\section{Odd gradings on simple associative superalgebras in terms of \texorpdfstring{$G$}{G}}\label{sec:assc-only-G}

In \cref{sec:grd-simple-salg}, our results about both odd graded-simple and odd simple $G$-graded superalgebras were in terms of the group $G^\#$. 
We will now present a classification in term of the group $G$. 
Throughout this section, $\FF$ will be assumed algebraically closed. 

\subsection{Odd graded-simple superalgebras}\label{ssec:odd-div-G-only}\label{ssec:in-terms-of-G}

Let $\D$ be an odd finite dimensional graded-division superalgebra associated to $(T, \beta, p)$. 
It is clear that $\D\even$ is a graded-division algebra associated to $(T^+, \beta^+)$. 
Also, given any $t_1 \in T^-$, then $t_1 = (h, \bar 1)$ for some $h\in G$ such that $h^2\in T^+$ and the map $\chi \from T^+ \to \FF^\times$ given by $\chi(t) \coloneqq \beta(t_1, t)$ is a character in $\widehat{T^+}$ such that $\chi(h^2) = 1$ and $\chi^2 = \beta^+ (h^2, \cdot)$. 

\begin{defi}\label{def:odd-parameters}
    We say that the odd graded-division superalgebra $\D$ is \emph{associated} to the quadruple $(T^+, \beta^+, h,\chi)$. 
    If $\U$ is a graded right $\D$-supermodule of finite rank associated to the map $\kappa\from G/T^+ \to \FF^\times$, we say that $(T^+, \beta^+, h, \chi, \kappa)$ are the \emph{$G$-parameters} of the pair $(\D, \U)$. 
\end{defi}

Any quadruple $(T^+, \beta^+, h,\chi)$ associated to $\D$ has enough information to recover $T$ and $\beta$, since $T^- = (h, \bar 1) T^+$ and
\[\label{eq:beta-from-h-chi}
    \forall s,t\in T^+,\, \forall i,j \in \ZZ, \quad \beta(s\, t_1^i,t \, t_1^j) = \beta^+(s,t)\, \chi (s)^{-j}\, \chi (t)^i,
\]
and, therefore, $(T^+, \beta^+, h,\chi)$ determines the isomorphism class of the graded-division superalgebra $\D$. 

\begin{defi}\label{def:O(T+-beta+)}
    Let $T^+$ be any finite subgroup of $G$ and let $\beta^+$ be an alternating bicharacter on $T^+$. 
    A pair $(h,\chi) \in G \times \widehat{T^+}$ is said to be \emph{$(T^+, \beta^+)$-admissible} if 
    $h^2 \in T^+$, $\chi(h^2) = 1$ and $\chi^2 = \beta^+(h^2, \cdot)$. 
    We will denote the set of all $(T^+, \beta^+)$-admissible pairs by $\mathbf {O} (T^+, \beta^+)$. 
\end{defi}

\phantomsection\label{T-beta-construction}

For each $(T^+, \beta^+)$-admissible pair $(h, \chi)$, we can construct a triple $(T, \beta, p)$ corresponding to a odd graded-division superalgebra. 
First, we set $t_1 \coloneqq (h, \bar 1)$ and define $T \coloneqq T^+ \cup t_1 T^-$.  
Since $h^2 \in T^+$, $T$ is a subgroup of $G^\#$. 
We take $\beta\from T\times T \to \FF^\times$ to be as in the following:

\begin{lemma}\label{lemma:existence-beta}
    There is a unique alternating bicharacter $\beta$ on $T$ such that $\beta\restriction_{T^+ \times T^+} = \beta^+$ and $\beta(t_1, t) = \chi(t)$, for all $t\in T^+$.
\end{lemma}

\begin{proof}
    Clearly, a bicharacter $\beta$ satisfies the conditions above if, and only if, \cref{eq:beta-from-h-chi} is satisfied. 
    It follows that there is at most one such bicharacter. 
    
    % One could also use \cref{eq:beta-from-h-chi} as a definition for $\beta$, but it is not clear if it is well defined. 
    
    Let $\widetilde T$ be the direct product of $T^+$ and the infinite cyclic group generated by a new symbol $\tau$, and let $\phi \from \widetilde T \to T$ be the unique group homomorphism such that $\phi(t) = t$ for all $t\in T^+$ and $\phi(\tau) = t_1$. 
    It is easy to see that $\ker \phi = \langle h^2 \tau^{-2} \rangle$ and that $\phi$ is surjective. 
    
    Let us define $b\from \widetilde T\times \widetilde T \rightarrow \FF^\times$ by $b(s\tau^i,t\tau^j) \coloneqq \beta^+(s,t)\, \chi (s)^{-j}\, \chi (t)^i$, for all $s,t\in T^+$ and $i,j \in \ZZ$. 
    Clearly, $b$ is an alternating bicharacter. 
    We claim that $h^2 \tau^{-2} \in \rad b$. 
    Indeed, for all $t \in T^+$ and $j \in \ZZ$,
    \[%begin{align}
        b(h^2 \tau^{-2},t\tau^j) = \beta^+(h^2,t)\, \chi (h^2)^{-j}\, \chi (t)^{-2} = \chi (t)^{2}\, \chi (h^2)^{-j}\, \chi (t)^{-2} = \chi (h^2)^{-j} = 1.
    \]%end{align}
    
    It follows that $\ker \phi \subseteq \rad b$ and, hence, $b$ induces an alternating bicharacter $\beta\from T\times T \to \FF$ such that $b = \beta \circ (\phi \times \phi)$. 
    From the definition of $b$, it follows that $\beta$ satisfies \cref{eq:beta-from-h-chi}.
\end{proof}

Combining this with \cref{lemma:colour-tensor-product}, we obtain:

\begin{prop}\label{prop:D-defined-by-quadruple}
    Let $(h, \chi) \in \mathbf{O}(T^+, \beta^+)$. 
    Then there exists an odd graded-division superalgebra $\D$ associated to the quadruple $(T^+, \beta^+, h,\chi)$. \qed
\end{prop}

We now have a parametrization of odd graded-division superalgebras in terms of the group $G$. 
It remains to see when different quadruples determine isomorphic graded-division superalgebras. 

% \begin{defi}\label{def:T^+-action}
    We define a $T^+$-action on $\mathbf{O} (T^+, \beta^+)$ by
    \[\label{def:T^+-action}
        \forall\, t\in T^+, \, \forall\, (h, \chi) \in \mathbf{O} (T^+, \beta^+), \quad
        %
        t \cdot (h, \chi) \coloneqq (th, \beta^+(t, \cdot) \, \chi)\,.
    \]
% \end{defi}
%
To see it is well defined, note that $(th)^2 = t^2h^2\in T^+$, $\beta^+(t, (t h)^2) \chi( (t h)^2) = \beta^+(t, h^2) \chi(t^2) \chi (h^2) = \chi^{-2}(t) \chi
^2 (t) = 1$ and $\beta^+((th)^2, \cdot) = \beta^+(t, \cdot) \chi$, so, indeed, $t \cdot (h, \chi) \in \mathbf {O} (T^+, \beta^+)$. 
It is straightforward that the axioms of action are satisfied. 

\begin{thm}\label{thm:iso-odd-D-only-G}
    Let $\D$ and $\D'$ be finite dimensional odd graded-division superalgebras associated to quadruples $(T^+, \beta^+, h, \chi)$ and $(T'^+, \beta'^+, h', \chi')$, respectively. 
    Then $\D \iso \D'$ as graded algebras if, and only if, $T^+ = T'^+$, $\beta^+ = \beta'^+$, and the pairs $(h, \chi)$ and $(h', \chi')$ are in the same $T^+$-orbit in $\mathbf {O} (T^+, \beta^+)$. 
\end{thm}

\begin{proof}
    Let $(T, \beta, p)$ and $(T', \beta', p')$ be the triples associated to $\D$ and $\D'$, respectively. 
    By \cref{prop:T-beta-determines-iso}, $\D \iso \D'$ if, and only if, $T= T'$ and $\beta = \beta'$. 
    
    Let $t_1 \coloneqq (h, \bar 1)$ and $t_1' \coloneqq (h', \bar 1)$.
    By definition, $T= T'$ if, and only if, $T^+ = T'^+$ and $t_1 T^+ = t_1' T^+$. 
    Clearly, the latter condition is equivalent to 
    % Hence $T= T'$ if, and only if, $T^+ = T'^+$ and 
    $h' = th$ for some $t\in T^+$. 
    
    Now suppose $T= T'$ and let $t\in T^+$ be such that $h' = th$. 
    By \cref{lemma:existence-beta}, $\beta = \beta'$ if, and only if, 
    $\beta^+ = \beta'^+$ and $\beta(t_1, \cdot) = \beta'(t_1, \cdot)$. 
    Since $t_1' = t t_1$, the latter condition is equivalent to $\chi' = \beta^+ (t, \cdot) \chi$. 
\end{proof}

Combining this with \cref{thm:iso-D-odd}, we obtain: 

\begin{cor}\label{cor:classification-odd-general}
    Let $(\D, \U)$ and $(\D', \U')$ be pairs as in  \cref{def:odd-parameters} and let $(T^+, \beta^+, h, \chi, \kappa)$ and $(T'^+, \beta'^+, h', \chi', \kappa)$ be the $G$-parameters of $(\D, \U)$ and $(\D', \U')$, respectively. 
	Then $\End_\D (\U) \iso \End_{\D'} (\U')$ if, and only if, $T^+=T'^+$, $\beta^+=\beta'^+$, the pairs $(h, \chi)$ and $(h', \chi')$ are in the same $T^+$-orbit in $\mathbf {O} (T^+, \beta^+)$, and there is $g\in G$ such that $\kappa' = g \cdot \kappa$. \qed
\end{cor}

\subsection{Odd \texorpdfstring{$G$}{G}-gradings on simple superalgebras}\label{ssec:grds-M(m-n)-only-G}
%  of type \texorpdfstring{$M$}{M} in terms of \texorpdfstring{$G$}{M}

For specific cases, the parametrization obtained in the previous subsection can be simplified using the following general observation about group actions, which will also be useful in the following chapters: 

\begin{lemma}\label{lemma:lemma-on-actions}
    Let $H$ be a group, let $X$ and $Y$ be $H$-sets, and let $\pi\from X \to Y$ be an $H$-equivariant map. 
    For every $y \in Y$, the $H$-action on $X$ restricts to a $\operatorname{Stab}_H (y)$-action on $\pi\inv(y)$ and, if the $H$-action on $Y$ is transitive, the inclusion map $\pi\inv(y) \hookrightarrow X$ induces a bijection between $\operatorname{Stab}_H (y)$-orbits in $\pi\inv(y)$ and $H$-orbits in $X$.  
\end{lemma}

\begin{proof}
    The first assertion is straightforward: if $x\in \pi\inv(y)$ and $g \in \operatorname{Stab}_H (y)$, then $g \cdot x \in \pi\inv(y)$. 
    
    Now suppose that the $H$-action on $Y$ is transitive. 
    It is clear that the $\operatorname{Stab}_H (y)$-orbit of any $x\in \pi\inv (y)$ is contained in the $H$-orbit of $x$. 
    Conversely, given $x\in X$, by transitivity, there is $g\in H$ such that $g \cdot \pi(x) = y$ and, hence, $g\cdot x \in \pi\inv (y)$. 
    We claim that the intersection of the $H$-orbit of $x$ with $\pi\inv (y)$ is precisely the  $\operatorname{Stab}_H (y)$-orbit of $g\cdot x$. 
    Indeed, if for some $g'\in H$ we have $g'\cdot x \in \pi\inv(y)$, then $y = \pi(g'\cdot x) = (g'g\inv)\cdot \pi(g\cdot x) = (g'g\inv) \cdot y$, so $g'g\inv \in \operatorname{Stab}_H (y)$.
\end{proof}

\phantomsection\label{odd-Q}

As an application of this lemma, we will revisit the classification of graded-division superalgebras of type $Q$. 
Recall that in this case $\beta^+$ is nondegenerate. 

Let $\pi\from \mathbf {O} (T^+, \beta^+) \to \widehat{T^+}$ be the projection on the second entry, which is $T^+$-equivariant if we define the action of $T^+$ on $\widehat{T^+}$ by $t\cdot \chi = \beta^+(t,\cdot) \chi$, for all $t\in T$ and $\chi \in \widehat{T^+}$. 
Since $\beta^+$ is nondegenerate, the map $T \to \widehat{T^+}$ sending $s \to \beta^+(s, \cdot)$ is an isomorphism of $T^+$-sets, hence this $T^+$-action on $\widehat{T^+}$ is simply transitive. 

By \cref{lemma:lemma-on-actions}, it follows that the $T^+$-orbits in $\mathbf {O} (T^+, \beta^+)$ are in bijection with points in $\pi\inv (1)$, where $1$ denotes the trivial character of $T^+$. 
By \cref{def:O(T+-beta+)}, $(h, 1) \in \mathbf {O} (T^+, \beta^+)$, $(h, 1)$ if, and only if, $h^2 \in T^+$ and $h^2 \in \ker \beta^+$, that is, \IFF $h^2 = e$. 

We note that, in this case, $(h, \bar 1) \in \ker \beta$, hence, in view of \cref{lemma:beta-deg-beta-tilde-nondeg}, we have $\ker \beta = \langle (h, \bar 1) \rangle$ and $\D$ is isomorphic to a standard realization of a graded-division superalgebra of type $Q$ associated to $(T^+, \beta^+, h)$ (see \cref{def:standard-realization-Q}). 
Thus, we recover \cref{cor:iso-Q} from \cref{cor:classification-odd-general}. 

% --- Type M:

We will now focus on the case of graded superalgebras of type $M$. 
Let us fix a finite dimensional odd graded-division superalgebra $\D$ associated to a triple $(T, \beta, p)$. 
Since $\D$ is odd, $T^-$ is a non-empty coset of $T^+$ and, hence, $|T| = |T^+| + |T^-| = 2|T^+|$. 

\begin{lemma}\label{prop:char-does-not-divide-T}
    Suppose $\Char \FF = p > 0$. 
    If $p$ divides $|T|$, then $\beta$ is degenerate.
\end{lemma}

\begin{proof}
    Let $t\in T$ be an element of order $p$. 
    For every $s\in T$, we have $1 = \beta(e, s) = \beta(t^p, s) = \beta(t, s)^p$, hence, since $\Char \FF = p$, $\beta(t, s) = 1$, \ie, $t\in \rad \beta$. 
\end{proof}

Since we are interested in the case when $\D$ is of type $M$, \ie, that $\beta$ is nondegenerate, from now on we will assume that $\Char \FF \neq 2$.

We start with a necessary condition on the pair $(T^+, \beta^+)$ for $\beta$ be nondegenerate:

\begin{prop}\label{prop:parity-element}
    If $\beta$ is nondegenerate, then there is an element $t_p \in T^+$ of order $2$ such that $\rad \beta^+ = \langle t_p \rangle$. 
    Moreover, $\beta(t_p, T^-) = -1$. 
\end{prop}

\begin{proof}
    Consider $\chi \in \widehat{T}$ given by $\chi(t) = (-1)^{p(t)}$. 
    Since $\beta$ is nondegenerate, there is $t_p\in T$ of order $2$ such that $\chi = \beta(t_p, \cdot)$. 
    Since $\beta(t_p, t_p) = 1 = (-1)^{p(t_p)}$, $t_p$ is even. 
    Hence $t_p \in \rad \beta^+$. 
    
    If $0 \neq t \in \rad \beta^+$, using again that $\beta$ is nondegenerate, there is $t_1 \in T^-$ such that $\beta(t, t_1) \neq 1$. 
    Since $t_1^2 \in T^+$, $\beta(t_p, t_1)^2 = \beta(t, t_1^2) = 1$. 
    It follows that $\beta(t, t_1) = -1$, and since $T^- = t_1 T^+$, $\beta(t, s) = -1$ for all $s\in T^-$. 
    Hence $\beta(t, s) = (-1)^{p(s)}$ and, therefore, $t = t_p$.
\end{proof}

We note that $t_p$ is the (unique) parity element of $(T, \beta, p)$ (see \cref{def:parity-element}). 

% -- Existence, necessary condition --

As we will see in \cref{ex:T+-but-no-T}, not every pair $(T^+, \beta^+)$ with $|\rad \beta^+| = 2$ is a restriction of a triple $(T, \beta, p)$ with $\beta$ nondegenerate (see \cref{ex:T+-but-no-T}). 
Roughly speaking, this is because some information about the \emph{squares} of elements in $T^-$ is encoded in $(T^+, \beta^+)$. 
To make this precise, we will need the following: 

\begin{defi}\label{defi:perp}
    Let $H$ be an abelian group and $b$ be a symmetric or skew-symmetric bicharacter on $H$. 
    For every subgroup $A \subseteq H$, we define the \emph{orthogonal complement to $A$ with respect to $b$} to be the subgroup
    \[
        A^\perp \coloneqq \{ h\in H \mid b(h, A) = 1 \}.
    \]
\end{defi}

\begin{lemma}\label{lemma:perp-perp}
    Let $H$ and $b$ be as in \cref{defi:perp}, and suppose that $H$ is finite and $b$ is nondegenerate. 
    Then for every subgroup $A \subseteq H$, we have that $|A^\perp| = [H : A]$ and $(A^\perp)^\perp = A$.
\end{lemma}

\begin{proof}
    It is easy to see that the map $A^\perp \to \widehat{\left( \frac{H}{A}\right)}$ given by $t \mapsto \beta(t, \cdot)$ is an isomorphism of groups. 
    Also, since $\beta$ is nondegenerate, by \cref{prop:char-does-not-divide-T},  $\Char \FF$ does not divide $[H : A]$. 
    In this case, it is well-known that $\widehat{\left( \frac{H}{A}\right)} \iso \frac{H}{A}$, proving the first assertion.

    Since $b$ is symmetric or skew-symmetric, it is clear that $A \subseteq (A^\perp)^\perp$. 
    Using the first assertion, we have that $|A| = |(A^\perp)^\perp|$ and, therefore, $A = (A^\perp)^\perp$.
\end{proof}

\begin{defi}\label{def:A_[m]}
    Let $A$ be an abelian group and $m \in \ZZ$. 
    We define $A^{[m]} \coloneqq \{a^m \mid a\in A\}$ and $A_{[m]} \coloneqq \{a\in A \mid a^m = e \}$.
\end{defi}

Note that $(T^+)^{[2]} \subseteq T^{[2]} \subseteq T^+$, but we can have $(T^+)^{[2]} \neq T^{[2]}$. 

\begin{lemma}\label{lemma:small-perp}
    Let $H$ and $b$ be as in \cref{defi:perp}, and suppose that $H$ is finite and $b$ is nondegenerate.
    Then, for every $m\in \ZZ$, $(H_{[m]})^\perp = H^{[m]}$.
\end{lemma}

\begin{proof}
    By \cref{lemma:perp-perp}, it suffices to prove that $(H^{[m]})^\perp = H_{[m]}$:
    %
	\begin{align}
		(H^{[m]})^\perp & = \{ h \in H \mid b (h, g^m) = 1 \text{ for all } g\in H \}\\ 
		& = \{ h \in H \mid b (h^m, g) = 1 \text{ for all } g\in H \}\\ 
		& = \{ h \in H \mid h^m = e \} \\
% 		\numberthis\label{4th-line-again} \\ 
		&= H_{[m]},
	\end{align}
	%
	where we are using that $b$ is nondegenerate in the third line. 
\end{proof}

Now suppose $\beta$ is nondegenerate, let $t_p$ be as in \cref{prop:parity-element}, set $\barr G \coloneqq G/\langle t_p \rangle$, let $\theta\from G\rightarrow \barr G$ be the natural homomorphism, set $\barr {T^+} \coloneqq \theta(T^+)$ and let $\barr{\beta^+}$ be the bicharacter on $\barr {T^+}$ induced by $\beta^+$. 
Note that $\barr{\beta^+}$ is nondegenerate. 
Next result explains what was meant by ``some information about the squares of elements in $T^-$'' above. 
It is similar to \cref{lemma:small-perp}, but does not follow from it.

\begin{prop}\label{prop:square-subgroup}
	Consider $\theta(T^{[2]})$ and $\theta(T^+_{[2]})$ as subgroups of $\barr {T^+}$. 
	We have that $\theta(T^{[2]})$ is the orthogonal complement of $\theta(T^+_{[2]})$ with respect to $\barr{\beta^+}$, \ie, $ \theta(T^+_{[2]})^\perp = \theta(T^{[2]})$. 
	In particular, $\theta(T^+_{[2]})^\perp \subseteq \barr G^{[2]}$.
\end{prop}

\begin{proof}
	By \cref{lemma:perp-perp}, it suffices to prove that $\theta(T^{[2]})^\perp = \theta(T^+_{[2]})$:
	%
	\begin{align}
		\theta(T^{[2]})^\perp & = \{ \theta(t) \mid t\in T^+ \AND \barr{\beta^+} (\theta (t), \theta (s^2)) = 1 \text{ for all }s\in T\}\\ 
		& = \{\theta(t) \mid t\in T^+ \AND \beta^+ (t, s^2) = 1 \text{ for all }s\in T\}\\ 
		& = \{ \theta(t) \mid t\in T^+ \AND \beta (t^2, s) =1 \text{ for all }s\in T\}\\ 
		& = \{ \theta(t) \mid t\in T^+ \AND t^2=e \} \\
% 		\numberthis\label{4th-line} \\ 
		&= \theta(T^+_{[2]}),
	\end{align}
	%
	where we are using that $\beta$ is nondegenerate in the fourth line. 
\end{proof}

\begin{example}\label{ex:T+-but-no-T}
    Take $G \coloneqq T^+ \coloneqq \ZZ_2 \times \ZZ_4$ and define $\beta^+\from T^+ \times T^+ \to \FF^\times$ by $\beta^+((i, j),(i', j')) \coloneqq (-1)^{ij' - i'j}$, for all $i,j, i',j' \in \ZZ$. 
    It is easy to see that $\beta^+$ is an alternating bicharacter and that $\rad \beta^+ = \langle (\bar 0, \bar 2) \rangle$. 
    We have that
    $T^+_{[2]} = \langle (\bar 1, \bar 0) , (\bar 0, \bar 2) \rangle$ and, hence, $\theta(T^+_{[2]}) = \langle \theta(\bar 1, \bar 0) \rangle$. 
    Since $\theta(T^+_{[2]})$ is cyclic, $\theta(\bar 1, \bar 0) \in \theta(T^+_{[2]})^\perp$. 
    But it is clear that $\theta(\bar 1, \bar 0) \not\in \barr G^{[2]}$, so the pair $(T^+, \beta^+)$ cannot be obtained from a triple $(T, \beta, p)$ with $\beta$ nondegenerate. 
\end{example}

From now on, let $T^+$ be a finite subgroup of $G$ and $\beta^+$ be an alternating bicharacter on $T^+$ such that $\rad \beta^+ = \langle t_p \rangle$, where $t_p\in T^+$ is an element of order $2$, and define $\barr G$, $\theta$, $\barr {T^+}$ and $\barr{\beta^+}$ as above. 
In \cref{prop:O_M-non-empty}, we will see that the condition $\theta(T^+_{[2]})^\perp \subseteq \barr G^{[2]}$ is sufficient to extend $(T^+, \beta^+)$ to a triple $(T, \beta, p)$ with $\beta$ nondegenerate. 
% But first, we will apply the results from the previous section to the present situation. 

\begin{lemma}\label{lemma:motivation-O_M}
    Let $(h, \chi) \in \mathbf{O}(T^+, \beta^+)$ and let $\D$ be a graded-division superalgebra associated to $(T^+, \beta^+, h, \chi)$. 
    Then $\D$ is of type $M$ if, and only if, $\chi(t_p) = -1$.
\end{lemma}

\begin{proof}
    Let $(T, \beta, p)$ be the triple constructed from $(T^+, \beta^+, h, \chi)$ and let $t_1 = (h, \bar 1)$. 
    
    If $\beta$ is nondegenerate, then $\chi(t_p) = \beta(t_1, t_p) = -1$ by \cref{prop:parity-element}. 
    
    Conversely, assume $\chi(t_p) = -1$. 
    Then $\beta(t_p, T^-) = \beta(t_p, t_1T^+) = \beta (t_p, t_1) = \chi(t_p)\inv = -1$. 
    We conclude that $(\rad \beta)\cap T^- = \emptyset$ and that $t_p \not\in \rad\beta$. 
    Also, it is clear that $(\rad \beta)\cap T^+ \subseteq \rad \beta^+ = \langle t_p \rangle$, hence $(\rad \beta)\cap T^+ = \{e\}$ and, therefore, $\rad \beta = \{e\}$.
\end{proof}

\phantomsection\label{def:O_M}

We define $\mathbf{O}_M(T^+, \beta^+) \coloneqq \{ (h, \chi) \in \mathbf{O}(T^+, \beta^+) \mid \chi(t_p) = -1 \}$. 
Since $t_p\in \rad \beta^+$, we see that the $T^+$-action on $\mathbf{O}(T^+, \beta^+)$ restricts to $\mathbf{O}_M(T^+, \beta^+)$. 

\begin{lemma}\label{lemma:Y-non-empty}
    The set $Y \coloneqq \{\chi \in \widehat{T^+} \mid \chi (t_p) = -1 \}$ is non-empty.
\end{lemma}

\begin{proof}
    Since $\barr{\beta^+}$ is a nondegenerate bicharacter, by \cref{prop:char-does-not-divide-T}, $\Char \FF$ does not divide $|\barr{T^+}|$. 
    Using that $|T^+| = 2 |\barr{T^+}|$ and $\Char \FF \neq 2$, it follows that $\Char \FF$ does not divide $|T^+|$. 
    It is well-known that, in this case, every character on a subgroup of $T^+$ can be extended to a character of $T^+$. 
    We can define a character $\chi$ on $\langle t_p \rangle$ by $\chi(t_p) = -1$, and, extending $\chi$, we conclude that $Y \neq \emptyset$. 
\end{proof}

\begin{lemma}\label{lemma:chi-defines-a}
    Given $\chi \in Y$, there is a unique element $a \in T^+$ such that $\chi^2 = \beta^+(a, \cdot)$ and $\chi(a) = 1$. 
    Further, an element $h\in G$ is such that $(h, \chi) \in \mathbf{O}_M(T^+, \beta^+)$ if, and only if, $h^2 = a$. 
\end{lemma}

\begin{proof}
    Since $\chi^2(t_p) = 1$, $\chi^2$ can be seen as a character on $\barr {T^+}$. 
    It follows that there is a unique element $\barr a\in \barr{T^+}$ such that $\chi^2(\barr t) = \barr\beta(\barr a, \barr t)$, for all $\barr t\in \barr {T^+}$. 
    We have that $\theta\inv(\barr a) = \{ a, at_p \}$ for some $a\in T^+$. 
    Since $\chi^2(a) = \chi^2(\barr a) = 1$, $\chi (a) = \pm 1$. 
    Relabeling if necessary, we can assume $\chi (a) = 1$ and $\chi(at_p) = -1$. 
    This shows existence and uniqueness.
    The ``further'' part follows directly from \cref{def:O(T+-beta+)}.
\end{proof}


\begin{prop}\label{prop:O_M-non-empty}
    % Let $R \coloneqq \frac{T^+_{[2]}}{\langle t_p \rangle}$. 
    The set $\mathbf{O}_M(T^+, \beta^+)$ is non-empty if, and only if, $\theta(T^+_{[2]})^\perp \subseteq \barr G^{[2]}$.
\end{prop}

\begin{proof}
    The ``only if'' part follows from \cref{prop:square-subgroup}. 
    For the ``if'' part, let us fix $\chi \in Y$, which exists by \cref{lemma:Y-non-empty}, and take $a\in T^+$ as in \cref{lemma:chi-defines-a}.
    We want to find $h\in G$ such that $(h, \chi) \in \mathbf{O}_M(T^+, \beta^+)$, \ie, $h^2 = a$. 
    
	By the definition of $a$, for any $b \in T^+_{[2]}$ we have that
	\[
	    \barr{\beta^+} ( \theta(a) , \theta(b) )
	    = \beta^+ (a , b) 
	    =  \chi^2 (b) 
	    = \chi (b^2) 
	    = \chi (e) 
	    = 1,
	\]
	so $ \theta (a) \in \theta(T^+_{[2]})^\perp$ and, hence, $\theta(a) \in \barr G^{[2]}$. 
	
	Let $h\in G$ be such that $\theta(a) = \theta(h)^2$, so either $a = h^2$ or $a = h^2t_p$. 
	If $t_p \in G^{[2]}$, we can change $h$ if necessary to make $a = h^2$. 
	If $t_p \not\in G^{[2]}$, it is straightforward that $\theta(T^+_{[2]}) = \theta(T^+)_{[2]}$, so, using \cref{lemma:small-perp}, we have
	\[
	    a \in \theta(T^+_{[2]})^\perp = (\theta(T^+)_{[2]})^\perp = \theta(T^+)^{[2]},
	\]
	and, hence, we can take $h\in T^+$. 
	In this case, $h^2$ satisfies the same conditions as $a$ in \cref{lemma:chi-defines-a}:
	\[
	    \forall t\in T^+, \quad
	    \chi^2(t) 
	    = \beta^+(a, t) 
	   % = \barr{\beta^+}( \theta(h)^2, \theta(t) ) 
	   % = \barr{\beta^+}( \theta(h^2), \theta(t) )
	    = \beta^+ (h^2, t)
	\]
	and
	\[
	    \chi(h^2) 
	    = \chi^2(h) 
	    = \beta^+ (a, h)
	    = \barr{\beta^+} (\theta(a), \theta(h)) 
	    = \barr{\beta^+} (\theta(h)^2, \theta(h)) 
	    = 1.
	\] 
	By the uniqueness of $a$, it follows that $h^2 = a$, concluding the proof. 
\end{proof}

Combining  \cref{cor:classification-odd-general} and \cref{lemma:motivation-O_M}, we can get a classification result for finite dimensional odd graded superalgebras of type $M$ in terms of orbits of the $T^+$-action on $\mathbf{O}_M(T^+, \beta^+)$. 
But, as we did for $Q$ in the end of \cref{odd-Q}, we can simplify this classification using \cref{lemma:lemma-on-actions}. 
To this end, define a $T^+$-action on $Y$ by $t\cdot \chi = \beta^+(t, \cdot) \chi$, which is well defined since $t_p \in \rad \beta^+$. 

\begin{lemma}
    The $T^+$-action on $Y$ is transitive.
\end{lemma}

\begin{proof}
    Let $\chi, \chi' \in Y$. 
    We have $(\chi' \chi\inv) (t_p) = 1$, hence $(\chi' \chi\inv)$ can be seen as a character on $\barr{T^+} = T^+/ \langle t_p \rangle$. 
    By nondegeneracy of $\barr {\beta^+}$, there is $t\in T^+$ such that $(\chi' \chi\inv) = \barr {\beta^+} (\bar t, \cdot)$ as a character on $\barr{T^+}$. 
    It follows that $(\chi' \chi\inv) = \beta^+(t, \cdot)$ as a character on $T^+$, so $\chi' = \beta(t, \cdot)\chi$. 
    We conclude that $\chi' = t \cdot \chi$, as desired. 
\end{proof} 

In the case of superalgebras of type $Q$, we were able to fix the character to be the trivial one. 
In the present case, we can also fix the character $\chi \in Y$, but there is no canonical choice for it.

\begin{defi}\label{defi:element-a}
    Given $\chi \in \widehat{T^+}$ such that $\chi(t_p) = -1$, let $a\in T^+$ be the unique element as in \cref{lemma:chi-defines-a}. 
    We define $\mathbf{O}_M(T^+, \beta^+)_{\chi} \coloneqq \{ h\in G \mid h^2 = a \}$.
\end{defi}

\phantomsection\label{fix-chi-odd-M}

The projection onto the second entry $\pi\from \mathbf{O}_M(T^+, \beta^+) \to Y$ is a $T^+$-equivariant map and, clearly, $\mathbf{O}_M(T^+, \beta^+)_{\chi}$ is in bijection with $\pi\inv (\chi)$. 
In what follows, for each pair $(T^+,\beta^+)$
we fix an arbitrary character $\chi \in Y$ and its corresponding element $a\in T^+$ as above.

\begin{defi}\label{def:Gamma_M-only-G}
    Given a finite subgroup $T^+ \subseteq G$, an alternating bicharacter $\beta^+\from T\times T \to \FF^\times$ such that $\rad \beta^+$ is generated by an order $2$ element $t_p \in T^+$, an element $h \in \mathbf{O}_M(T^+, \beta^+)_{\chi}$ and a map $\kappa\from G/T^+ \to \ZZ_{\geq 0}$ with finite support, we define $\Gamma_M(T^+, \beta^+, h, \kappa)$ to be the $G$-grading $\Gamma_M (T, \beta, p, \kappa)$ on $M(n,n)$ (see \cref{def:Gamma-T-beta-kappa-odd}), where $n \coloneqq |\kappa| \sqrt{2|T^+|}$ and $(T, \beta, p)$ is constructed from $T^+$, $\beta^+$, $h$ and $\chi$ as in \cref{T-beta-construction}. 
    The superalgebra $M(n,n)$ endowed with $\Gamma_M (T^+, \beta^+, h, \kappa)$ will be denoted by $M(T^+, \beta^+, h, \kappa)$. 
\end{defi}

\begin{thm}\label{cor:iso-odd-M-simplified}
    Every odd $G$-grading on $M(n,n)$ is isomorphic to $\Gamma_M (T^+, \beta^+, h, \kappa)$ as in \cref{def:Gamma_M-only-G}. 
    Two such gradings $\Gamma_M (T^+, \beta^+, h, \kappa)$ and $\Gamma_M (T'^+, \beta'^+, h', \kappa')$ are isomorphic if, and only if, $T^+ = T'^+$, $\beta^+ = \beta'^+$, $h' \in \{ h, h t_p \}$ and there is $g\in G$ such that $\kappa' = g\cdot \kappa$.
\end{thm}

\begin{proof}
    From \cref{cor:iso-M-odd}, every grading is isomorphic to one of this form. 
    The isomorphism condition follows from \cref{cor:classification-odd-general,lemma:lemma-on-actions}, by noting that, considering the action of $T^+$ on $Y$,  $\operatorname{Stab}_{T^+} (\chi) = \rad \beta^+ = \{ e, t_p \}$. 
\end{proof}

% ---



% -- Existence, sufficiency --

% As stated before, the pair $(T^+, \beta^+)$ might not correspond to any triple $(T, \beta, p)$ with $\beta$ nondegenerate, \ie, the set $\mathbf{O}_M(T^+, \beta^+)$ might be empty.



% -------------------




% \input{chapters/02_Associative-Grd-Simple/existence_t_p}



% % ---------
% \section{Odd gradings on simple associative superalgebras only in terms of \texorpdfstring{$G$}{G}}\label{sec:assc-supersimple-only-G}

% In this section we will present a classification, up to isomorphism, only in terms of $G$ of odd gradings on finite dimensional simple superalgebras over an algebraically closed field. 

% Note that there are no odd gradings if $\Char \FF =2$. 
% Indeed, in this case, there is no nondegenerate bicharacter on $T$ because the characteristic of the field divides $|T|=2|T^+|$. 
% From now on, we suppose $\Char \FF \neq 2$.

% As stated in \cref{ssec:wedderburn-super}, the only problem is to describe the odd graded-division superalgebras only in terms of $G$. 
% For what follows, let $\D$ be a finite dimensional odd graded-division superalgebra, associated to the triple $(T, \beta, p)$. 
% We will denote the restriction of $\beta$ to $T^+ \times T^+$. 

% In general terms, our strategy is to describe the isomorphism class of $\D$ in terms of $\D\even$ and and some additional data, \ie, describe $(T, \beta, p)$ in terms of $(T^+, \beta^+)$ and some additional data. 

% \subsection{Odd gradings on \texorpdfstring{$M(n,n)$}{M(n,n)} only in terms of \texorpdfstring{$G$}{G}}\label{ssec:second-odd}

% Assume that we have $(T, \beta, p)$ with $\beta$ nondegenerate. 

% Since $\beta$ is nondegenerate, we have an isomorphism $T\rightarrow \widehat T$ given by $t\mapsto \beta(t,\cdot)$. For a subgroup $A\subseteq T$, we denote by $A^\perp$ its orthogonal complement in $T$ with respect to $\beta$, i.e., $A^\perp = \{t\in T\mid \beta(t, A) =1\}$. In view of the above isomorphism, $|A^\perp| = [T:A]$.

% In particular, we have $(T^+)^\perp = \langle t_p \rangle$ where $t_p$ is an element of order 2. It follows that $\beta(t_p, t) = 1$ if $t\in T^+$ and $\beta(t_p, t) = -1$ if $t\in T^-$. For this reason, we call $t_p$ the \emph{parity element} of the odd grading $\Gamma$. Note that $\rad \beta^+ = T^+\cap (T^+)^\perp = \langle t_p \rangle$.

% Fix an element $0\neq d_0\in \D$  of degree $t_p$. By the definition of $\beta$, $d_0$ commutes with all elements of $\D\even$ and anticommutes with all elements of $\D\odd$. Since $d_0^2\in \D_e = \FF$, and $\FF$ is algebraically closed, we may rescale $d_0$ so that $d_0^2=1$. Then $\epsilon := \frac{1}{2}(1+d_0)$ is a central idempotent of $\D\even$. Take a homogeneous element $0\neq d_1\in\D\odd$. Then $d_1\epsilon d_1\inv = \frac{1}{2}(1-d_0)=1-\epsilon$, which is another central idempotent of $\D\even$ and must have the same rank as $\epsilon$. 
% Hence, $\D\even\iso \epsilon\D\even\oplus (1-\epsilon)\D\even$ (direct sum of ideals) and, consequently, $E\even \iso \End(\tilde U)\tensor \D\even = \End(\tilde U)\tensor \epsilon\D\even \oplus \End(\tilde U)\tensor (1-\epsilon)\D\even$, where the two summands have the same dimension. Therefore, odd gradings exist only if $m=n$. 
% Also note that we have 
% \begin{equation}\label{eq:D1eps}
% \D\odd \epsilon = (1-\epsilon) \D\odd.
% \end{equation}

% We are now going construct an even grading by coarsening a given odd grading. The reverse of this construction will be used in Subsection \ref{ssec:second-odd}.

% Let $H$ be a group and suppose we have an even grading $\Gamma'$ on $M(n,n)$ that is the coarsening of $\Gamma$ induced by a group homomorphism $\alpha: G\rightarrow H$. Since $\Gamma'$ is even, then the idempotent $\id_{\tilde U}\tensor\epsilon$ must be homogeneous with respect to $\Gamma'$. This means that $\alpha(t_p)=e$, so $\alpha$ factors through $\barr G := G/\langle t_p \rangle$. This motivates the following definition:

% \begin{defi}
% 	Let $\Gamma$ be an odd $G$-grading on $M(n,n)$ with parity element $t_p$. 
% 	The \emph{finest even coarsening of $\Gamma$} is the $\barr G$-grading ${}^\theta \Gamma$, where $\barr G := G/\langle t_p \rangle$ and $\theta: G \to \barr G$ is the natural homomorphism.
% \end{defi}

% % Thm: this is the finest even coarsening
% \begin{thm}
% 	Let $\Gamma = \Gamma(T, \beta, \gamma)$ be an odd grading on $M(n,n)$ with parity element $t_p$. Then its finest even coarsening is isomorphic to $\barr \Gamma = \Gamma(\barr T, \barr \beta, \barr \gamma, \barr u\barr \gamma)$, where $\barr T= \frac{T^+}{\langle t_p \rangle}$, $\barr\beta$ is the nondegenerate bicharacter on $\barr T$ induced by $\beta^+$, $\barr\gamma$ is the tuple whose entries are the images of the entries of $\gamma$ under $\theta$, and $u \in G$ is 
% 	any element such that $(u, \barr 1) \in T^-$.
% \end{thm}

% \begin{proof}
% 	% D now decomposes as left module
% 	Let us focus our attention on the $G$-graded division algebra $\D$. We now consider it as a $\barr G$-graded algebra, which has a decomposition $\D=\D\epsilon \oplus \D(1-\epsilon)$ as a graded left module over itself.

% 	% Claim 1: D\epsilon is simple
% 	\setcounter{claim}{0}
% 	\begin{claim}
% 		The $\D$-module $\D\epsilon$ is simple as a graded module.
% 	\end{claim}

% 	% Proof of Claim 1
% 	To see this, consider a nontrivial graded submodule $V\subseteq \D\epsilon$ and take a homogeneous element $0\neq v\in V$. Then we can write $v=d\epsilon$ where $d$ is a $\barr G$-homogeneous element of $\D$, so $d = d' + \lambda d' d_0$ where $d'$ is a $G$-homogeneous element and $\lambda\in \FF$. Hence, $v = d'\epsilon + \lambda d'd_0\epsilon = (1+\lambda)d'\epsilon$, where we have used $d_0\epsilon=\epsilon$. Clearly, $(1+\lambda)d'\neq 0$, so it has an inverse in $\D$. We conclude that $\epsilon\in V$, hence $V=\D\epsilon$.\qedclaim 

% 	Let $\barr \D := \epsilon \D \epsilon \iso \End_{\D}(\D\epsilon)$, where we are using the convention of writing endomorphisms of a left module on the right. By Claim 1 and the graded analog of Schur's Lemma (see \eg \cite[Lemma 2.4]{livromicha}), $\barr \D$ is a $\barr G$-graded division algebra.

% 	% Claim 2: parameters of \barr D
% 	\begin{claim}
% 		The support of $\barr \D$ is $\barr T= \frac{T^+}{\langle t_p \rangle}$ and the bicharacter $\barr \beta: \barr T\times \barr T\rightarrow \FF^\times$ is induced by $\beta^+: T^+\times T^+ \rightarrow \FF^\times$.
% 	\end{claim}

% 	% Proof of Claim 2
% 	We have $\barr \D = \epsilon \D\even \epsilon + \epsilon \D\odd \epsilon$ and $\epsilon \D\odd \epsilon = 0$ by Equation \eqref{eq:D1eps}, so $\supp \barr \D \subseteq \barr T$. On the other hand, for every $0\neq d\in \D\even$ with $G$-degree $t\in T^+$, we have that $\epsilon d\epsilon = d\epsilon = \frac{1}{2}(d+dd_0)\neq 0$, since the component of degree $t$ is different from zero. Hence $\supp \barr \D = \barr T$. Since $\epsilon$ is central in $\D\even$, we obtain $\barr\beta (\barr t,\barr s) = \beta (s, t) = \beta^+ (s, t)$ for all $t, s\in T^+$.\qedclaim 

% 	% a basis for D\epsilon
% 	We now consider $\D\epsilon$ as a graded right $\barr \D$-module. Then we have the decomposition $\D\epsilon = \epsilon \D\epsilon \oplus (1-\epsilon) \D\epsilon$. The set $\{\epsilon\}$ is clearly a basis of $\epsilon \D\epsilon$. To find a basis for $(1-\epsilon)\D\epsilon$, fix any $G$-homogeneous $0\neq d_1\in \D\odd$  with $\deg d_1 = t_1\in T^-$. Then we have $(1-\epsilon)\D\epsilon = (1-\epsilon)\D\even \epsilon + (1-\epsilon)\D\odd \epsilon = (1-\epsilon)\D\odd \epsilon = \D\odd \epsilon$ by Equation \eqref{eq:D1eps}. Since $d_1$ is invertible, $\{d_1\epsilon\}$ is a basis for $(1-\epsilon) \D\epsilon$. We conclude that $\{\epsilon, d_1\epsilon\}$ is a basis for $\D\epsilon$.

% 	% All parameters for D
% 	Using the graded analog of the Density Theorem (see e.g. \cite[Theorem 2.5]{livromicha}), we have $\D\iso \End_{\barr \D}(\D\epsilon)\iso \End(\FF\epsilon\oplus \FF d_1\epsilon)\tensor \barr\D$. Hence,
% 	%
% 	\[
% 	\begin{split}
% 	\End_\D(\mc U)&\iso\End (\tilde U) \tensor \D \iso \End (\tilde U) \tensor \End(\FF\epsilon \oplus \FF d_1\epsilon) \tensor \barr\D \\
% 	&\iso \End(\tilde U\tensor \epsilon \oplus \tilde U\tensor d_1\epsilon) \tensor \barr\D
% 	\end{split}
% 	\]
% 	%
% 	as $\barr G$-graded algebras. The result follows.
% \end{proof}

% In the next section, we will show how to recover $\Gamma$ from $\barr\Gamma$ and some extra data. The following definition and result will be used there.

% \begin{defi}
% 	For every abelian group $A$ we put $A^{[2]} = \{a^2 \mid a\in A\}$ and $A_{[2]} = \{a\in A \mid a^2 = e \}$.
% \end{defi}

% Note that $T^{[2]}\subseteq T^+$, but $T^{[2]}$ can be larger than $(T^+)^{[2]}$ since it also includes the squares of elements of $T^-$. Also, the subgroup $\barr S = \{\barr t \in \barr T \mid t \in T^{[2]}\}$ of $\barr T$ can be larger than $\barr T^{[2]}$, but we will show that, surprisingly, it does not depend on $T^-$.

% \begin{lemma}
% 	Let $\theta: T^+\rightarrow \barr T=\frac{T^+}{\langle t_p \rangle}$ be the natural homomorphism. 
% 	Consider the subgroups $\barr S = \theta(T^{[2]})$ and $\barr R=\theta(T^+_{[2]})$ of $\barr T$. 
% 	Then $\barr S$ is the orthogonal complement of $\barr R$ with respect to the nondegenerate bicharacter $\barr\beta$.
% \end{lemma}

% \begin{proof}
% 	We claim that $\barr S^\perp = \barr R$. Indeed,
% 	%
% 	\[
% 		\begin{split}
% 			\barr S^\perp & = \{ \theta(t) \mid t\in T^+ \AND \barr\beta(\theta (t), \theta (s^2)) =1 \text{ for all }s\in T\}\\ & = \{\theta(t) \mid t\in T^+ \AND \beta (t, s^2) =1 \text{ for all }s\in T\}\\ & = \{ \theta(t) \mid t\in T^+ \AND \beta (t^2, s) =1 \text{ for all }s\in T\}\\ & = \{ \theta(t) \mid t\in T^+ \AND t^2=e \}\\ & = \barr R\,.
% 		\end{split}
% 	\]
% 	Since $\bar{\beta}$ is nondegenerate, it follows that $\barr S = \barr R^\perp$.
% \end{proof}

% Our second description of an odd grading consists of its finest even coarsening and the data necessary to recover the odd grading from this coarsening. 
% % All parameters will be obtained in terms of $G$ rather than its extension $G^\#=G\times \ZZ_2$.

% Let $t_p\in G$ be an arbitrarily fixed element of order 2 and set $\barr G = \frac{G}{\langle t_p \rangle}$. Let $\barr T \subseteq \barr G$ be a finite subgroup and let $\barr \beta: \barr T \times \barr T \rightarrow \FF^\times$ be a nondegenerate alternating bicharacter. 
% We define $T^+\subseteq G$ to be the inverse image of $\barr T$ under the natural homomorphism $\theta: G\rightarrow \barr G$. Note that $\barr \beta$ gives rise to a bicharacter $\beta^+$ on $T^+$ whose radical is generated by the element $t_p$. 
% We wish to define $T^-\subseteq G\times \{\barr 1\}$ so that $T=T^+\cup T^-$ is a subgroup of $G^\#$ and $\beta^+$ extends to a nondegenerate alternating bicharacter on $T$.

% From Lemma \ref{lemma:square-subgroup}, we have a necessary condition for the existence of such $T^-$, namely, for $\barr R=\frac{T^+_{[2]}}{\langle t_p \rangle}$, we need $\barr R' \subseteq \barr G^{[2]}$ (indeed, $\barr S$ is a subgroup of $\overline {G^{[2]}} = \barr G^{[2]}$). 
% We will now prove that this condition is also sufficient.

% \begin{prop}\label{prop:square-subgroup-converse}
% 	If $\left( \frac{T^+_{[2]} }{\langle t_p \rangle}\right)^\perp \subseteq \barr G^{[2]}$, then there exists an element $t_1\in G\times \{\barr 1\} \subseteq G^\#$ such that $T= T^+ \cup t_1\, T^+$ is a subgroup of $G^\#$ and  $\beta^+$ extends to a nondegenerate alternating bicharacter $\beta:T\times T\rightarrow \FF^\times$.
% % \end{prop}

% \begin{proof}
% 	Let $\chi\in \widehat {T^+}$ be such that $\chi(t_p) = -1$. Since $\chi^2(t_0)=1$, we can consider $\chi^2$ as a character of the group $\barr T = \frac{T^+}{\langle t_0 \rangle}$, hence there is $a\in T^+$ such that $\chi^2(\barr t) = \barr\beta(\barr a, \barr t)$ for all $\barr t\in \barr T$. Note that $\chi (a) = \pm 1$ and hence, changing $a$ to $a t_0$ if necessary, we may assume $\chi (a) = 1$.
	
% 	\bigskip 

% 	\textit{(i) Existence of $t_1$}:
	
% 	\medskip 

% 	As before, let $\barr R = \frac{T^+_{[2]}}{\langle t_0 \rangle}$. Then $\barr a \in \barr R^\perp$. Indeed, if $b\in T^+_{[2]}$, then $\barr\beta(\barr a,\barr b) = \chi^2 (\barr b) = \chi (b^2) = \chi (e) =1$. By our assumption, we conclude that $\barr a\in \barr G^{[2]}$. We are going to prove that, actually, $a\in G^{[2]}$. Pick $u\in G$ such that $\barr u^2 = \barr a$. Then, either $a=u^2$ or $a=u^2t_0$. If $t_0 = c^2$ for some $c\in G$, then replacing $u$ by $uc$ if necessary, we can make $u^2 = a$. Otherwise, $t_0$ has no square root in $T^+$, which implies that $\barr R=\barr T_{[2]}$. Hence $\barr R^\perp = (\barr T_{[2]})^\perp = \barr T^{[2]} = \theta ((T^+)^{[2]})$. Thus, in this case, we can assume $u\in T^+$. Then $\chi(u^2) = \chi^2(u) = \barr \beta (\barr a, \barr u) = \barr \beta (\barr u^2, \barr u) =1$, hence $u^2 = a$. Finally, we set $t_1=(u,\barr 1) \in G^\#$.

% 	\bigskip 

% 	\textit{(ii) Existence of $\beta$}:
	
% 	\medskip 

% 	We wish to extend $\beta^+$ to $T=T^+ \cup t_1\, T^+$ by setting $\beta(t_1, t) = \chi (t)$ for all $t\in T^+$. It is clear that there is at most one alternating bicharacter on $T$ with this property that extends $\beta^+$. To show that it exists and is nondegenerate, we will first introduce an auxiliary group $\widetilde T$ and a bicharacter $\tilde\beta$.

% 	Let $\widetilde T$ be the direct product of $T^+$ and the infinite cyclic group generated by a new symbol $\tau$. We define $\tilde\beta:\widetilde T\times \widetilde T \rightarrow \FF^\times$ by $ \tilde\beta(s\tau^i,t\tau^j) = \beta^+(s,t)\, \chi (s)^{-j}\, \chi (t)^i$, where $s,t\in T^+$. It is clear that $\tilde\beta$ is an alternating bicharacter.

% 	\begin{claim*}
% 	$\langle a\tau^{-2} \rangle = \rad \tilde \beta\,$.
% 	\end{claim*}

% 	Let $t\in T^+$ and $\ell\in \ZZ$. Then
% 	\[
% 	\tilde \beta (a\tau^{-2},t\tau^\ell) =
% 	\beta^+(a, t)\,\, \chi(t)^{-2} \, \chi(a)^{-\ell} = 
% 	\barr\beta(\barr a, \barr t)\,\, \chi(t)^{-2} = \chi(t)^2 \, \chi(t)^{-2} = 1,
%     \]
%     hence, $\langle a\tau^{-2} \rangle \subseteq \rad \tilde \beta$.

%     Conversely, if $s\tau^k \in \rad \tilde\beta$, then, $1 = \tilde \beta (s\tau^k, t_0) = \beta^+(s,t_0)\, \chi(t_0)^k = (-1)^k$, hence $k$ is even. From the previous paragraph, we know that $a\tau^{-2} \in \rad \tilde\beta$, hence $a^\frac{k}{2} \tau^{-k} \in \rad \tilde\beta$ and $s a^\frac{k}{2} = (s \tau^k) (a^\frac{k}{2} \tau^{-k}) \in \rad \tilde\beta$. Since $s a^\frac{k}{2} \in T^+$, we get $s a^\frac{k}{2} \in \rad \beta^+ = \{ e, t_0 \}$. But, if $sa^\frac{k}{2} = t_0$, we have $1 = \tilde\beta (sa^\frac{k}{2}, \tau) = \tilde\beta (t_0, \tau) = \chi(t_0)\inv = -1$, a contradiction. It follows that $sa^\frac{k}{2} = e$ and, hence, $s\tau^k = a^{-\frac{k}{2}}\tau^k = (a\tau^{-2})^{\frac{k}{2}}$, concluding the proof of the claim.
%     \qedclaim 

%     We have a homomorphism $\vphi:\widetilde T\rightarrow T$ that is the identity on $T^+$ and sends $\tau$ to $t_1$. Clearly, $\ker \vphi = \langle a\tau^{-2} \rangle$. By the above claim, $\tilde\beta$ induces a nondegenerate alternating bicharacter on $\frac{\widetilde T}{\langle a\tau^{-2} \rangle}$, which can be transferred via $\vphi$ to a nondegenerate alternating bicharacter on $T$ that extends $\beta^+$.
% %
% \end{proof}

% Now fix $\chi\in \widehat {T^+}$ with $\chi(t_0)=-1$ and let $a$ be the unique element of $T^+$ such that $\chi(a)=1$ and $\chi^2(\barr t) = \barr\beta (\barr a, \barr t)$ for all $t\in T^+$. Suppose that the condition of Proposition \ref{prop:square-subgroup-converse} is satisfied. 
% Then part (i) of the proof shows that there exists $u\in G$ such that $u^2=a$. Moreover, part (ii) shows that there exists an extension of $\beta^+$ to 
% a nondegenerate alternating bicharacter $\beta$ on $T=T^+\cup t_1T^+$, where $t_1=(u,\bar 1)$, such that $\beta(t_1,t)=\chi(t)$ for all $t\in T^+$.
% Clearly, such an extension is unique. We will denote it by $\beta_u$ and its domain by $T_u$.

% \begin{prop}\label{prop:roots-of-a}
% For every $T\subseteq G^\#$ such that $T\subsetneq G$ and $T\cap G=T^+$ and for every extension of $\beta^+$ to a nondegenerate alternating bicharacter $\beta$
% on $T$, there exists $u\in G$ such that $u^2=a$, $T=T_u$ and $\beta=\beta_u$.
% Moreover, $\beta_u=\beta_{\tilde{u}}$ if, and only if, 
% $u^{-1} \tilde{u} \in \langle t_0 \rangle$.
% \end{prop}

% \begin{proof}

% We have $T=T^+ \cup T^-$ where $T^-\subseteq G\times \{\barr 1\}$ is a coset of $T^+$.
% We can extend $\chi$ to a character of $T$, which we still denote by $\chi$, and, since $\beta$ is nondegenerate, 
% there is $t_1\in T$ such that $\beta(t_1, t) = \chi(t)$ for all $t\in T$. We have $t_1\in T^-$ since $\beta(t_1,t_0)=\chi(t_0)=-1$, so $t_1=(u,\bar 1)$, 
% for some $u\in G$, and hence $T=T_u$. We claim that $t_1^2 = a = (a, \bar 0)$ and, hence, $u^2 = a$. Indeed, $\chi(t_1^2) = \beta(t_1,t_1^2)=1$ and, for every $t\in T^+$,
% \[
%  	\chi^2(\barr t) = \chi(t)^2 = \beta (t_1, t)^2 = \beta (t_1^2, t) = \barr\beta (\,\overline {(t_1^2)},\, \barr t)\,,
% \]
% so $t_1^2$ satisfies the definition of the element $a$. This completes the proof of the first assertion.

% Now suppose $\beta_u=\beta_{\tilde{u}}$, so in particular $t_1\,T^+=\tilde{t}_1\,T^+$ where $t_1 = (u, \barr 1)$ and $\tilde{t}_1 = (\tilde u, \barr 1)$.
% Then there is $r\in T^+$ such that $\tilde{t}_1 = t_1\,r$. Also, for every $t\in T^+$,
% \[
% \chi(t) = \beta_{\tilde{u}}(\tilde{t}_1,t) = \beta_u (t_1\,r, t)
% 		= \beta_u(t_1, t)\,\beta_u(r,t) = \chi(t) \beta^+(r, t)
% \]
% and, hence, $\beta^+(r, t)=1$ for all $t\in T^+$. This means that $r = u\inv \tilde{u} \in \langle t_0 \rangle$.

% Conversely, if $\tilde u = u r$ for some $r\in \langle t_0 \rangle$, then $t_1\, T^+ = \tilde t_1\, T^+$. Also, for all $t\in T^+$,
% \[
% \beta_u(t_1, t) = \chi(t) = \beta_{\tilde{u}}(\tilde{t}_1, t) = \beta_{\tilde{u}}(t_1r, t) = 
% \beta_{\tilde{u}}(t_1, t)\, \beta^+(r, t) = \beta_{\tilde{u}}(t_1, t).
% \]
% It follows that $\beta_u=\beta_{\tilde{u}}$.
% \end{proof}

% Note that, keeping the character $\chi \in \widehat {T^+}$ with $\chi(t_0) = -1$ fixed, we have a surjective map from the square roots of $a$ to all possible pairs $(T,\beta)$. If we had started with a different character above, we would have obtained a different surjective map. Hence, for parametrization purposes, $\chi$ (and, hence, $a$) will be fixed.

% We are now in a position to give a classification of odd graded-division superalgebras gradings in terms of $G$ only. 
% We already have the following parameters: an element $t_0\in G$ of order $2$ and a pair $(\barr T, \barr\beta)$. 
% For any such $t_0$ and $\barr T$, we fix a character $\chi\in \widehat {T^+}$ satisfying $\chi(t_0) = -1$. 
% The next parameter is an element $u\in G$ such that $u^2 = a$, where $a$ is the unique element of $T^+$ such that $\chi(a)=1$ and $\chi^2(\barr t) = \barr\beta (\barr a, \barr t)$ for all $t\in T^+$. 
% % Finally, let $\gamma = (g_1, \ldots, g_k)$ be a $k$-tuple of elements of $G$. With these data, we construct the grading $\Gamma (t_0, \barr T, \barr \beta, u, \gamma)$ as follows:

% \begin{defi}\label{def:odd-grd-on-Mmn-2}
% 	Let $\D$ be a standard realization of the $G^\#$-graded division algebra with parameters $(T_u,\beta_u)$. 
% 	As a superalgebra, $\D$ is isomorphic to $M(n,n)$. 
% 	We define $\Gamma (t_0, \barr T, \barr \beta, u)$ as the corresponding $G$-grading on $M(n,n)$.
% \end{defi}

% % Theorem \ref{thm:first-odd-iso} together with Proposition \ref{prop:roots-of-a} give the following result:

% \begin{thm}\label{thm:2nd-odd-iso}
% 	Every odd division $G$-grading on the superalgebra $M(n,n)$ is isomorphic to some $\Gamma (t_0, \barr T, \barr \beta, u)$ as in Definition \ref{def:odd-grd-on-Mmn-2}.
% 	Two odd gradings, $\Gamma (t_0, \barr T, \barr \beta, u)$ and $\Gamma (t_0', \barr T', \barr \beta', u')$, 
% 	are isomorphic if, and only if, $t_0=t_0'$, $\barr T = \barr T'$, $\barr\beta = \barr\beta'$ and $u^{-1} u' \in \langle t_0 \rangle$. \qed
% \end{thm}

% \subsection{Gradings on \texorpdfstring{$Q(n)$}{Q(n)} only in terms of \texorpdfstring{$G$}{G}}

% % In this subsection we will not only find a description of gradings on $Q(n)$ only in terms of $G$, but we

% Suppose $\D \iso Q(n)$ as a superalagebra. 
% Recall that, by \cref{prop:tilde-beta-nondeg}, we have that $\tilde\beta$ is nondegenerate but $\beta$ is degenerate, \ie, we are under the conditions of \cref{lemma:beta-deg-beta-tilde-nondeg}. 

% We will denote by $u \coloneqq
%     \begin{pmatrix}
%         0 & I\\
%         I & 0
%     \end{pmatrix}
%     \in Q(n)$. 
% Note that $Z(Q(n))\even = \FF 1$ and $Z(Q(n))\odd = \FF u$. 

% % Let $\Gamma$ be a division on $Q(n)$ and let $(T, \beta, p)$ be the triple associated to the graded-division superalgebra $\D \coloneqq (Q(n), \Gamma)$. 
% % Note that, by \cref{prop:tilde-beta-nondeg}, we are under the conditions of \cref{lemma:beta-deg-beta-tilde-nondeg}. 

% % Clearly, $(T^+, \beta^+)$ defines a division-grading on the algebra $Q(n)\even \iso M_n(\FF)$. 
% By \cref{lemma:beta-deg-beta-tilde-nondeg}\eqref{item:rad-beta=t_1}, we have that $\rad \beta = \langle t_1 \rangle$ for a order two element $t_1 \in T^-$. 
% Then $t_1 = (h, \bar 1)$ for some element $h\in G$ of order at most two. 
% Since $\rad \beta = \supp Z(Q(n))$, we must have that $\deg u = t_1$. 

% \begin{defi}
%     If $\D \iso Q(n)$ as a superalgebra, we define the $G$-parameters of $\D$ to be the triple $(T^+, \beta^+, h)$.
% \end{defi}

% Note that the triple $(T^+, \beta^+, h)$ has the same information as the pair $(\Gamma\even, h)$, where $\Gamma\even$ denote the grading on $\D\even$.

% Conversely, given a division-grading $\Gamma\even$ on the algebra $Q(n)\even$ and an order two element $h \in G$, let $(T^+, \beta^+)$ be the pair corresponding to the graded-division algebra $(Q(n)\even, \Gamma\even)$ and define $t_1 \coloneqq (h, \bar 1)$. 
% We can then define $T \coloneqq T^+ \times \langle t_1 \rangle$, and define $\beta\from T\times T \to \FF^\times$ by $\beta(s t_1^i, t t_1^j) \coloneqq \beta^+(s, t)$. 
% It is easy to see that $\beta$ is a alternating bicharacter on $T$ and $\rad \beta = \langle t_1 \rangle$, and that $(T, \beta, p)$ is the triple associated to the graded-division superalgebra $Q(1)$ where the grading on $Q(n)\even$ is extended to $Q(n)$ by declaring $\deg u \coloneqq t_1$.  

% % We conclude the following:

% % \begin{thm}\label{thm:grd-div-Q-only-G}
    
% % \end{thm}

% \begin{remark}
%     The description of gradings on $Q(n)$ we found here
%     % in \cref{thm:grd-div-Q-only-G} 
%     is essentially the same one as in \cite[Theorem 5.5]{paper-Qn}.
% \end{remark}

% \begin{itemize}
%     \item Add that every $G$-grading on $Q(n)$ is restriction of a $G\times \ZZ_2$-grading on $M(n,n)$.
% \end{itemize}

% % For every associative superalgebra $R = R\even \oplus R\odd$, it is easy to see that $R\odd$ is an $(R\even, R\even)$-bimodule. 
% % In the case of $R \iso Q(n)$, then it is clear that $R\even \iso M(n)$ as an algebra and $R\odd \iso M(n)$ as a $(M(n), M(n))$-bimodule. 


% % \begin{itemize}
% %     \item We have two parametrizations, one here and one in \cite{paper-Qn}.
% %     \item The one here is as follows:
% %     \begin{itemize}
% %         \item Every grading is odd, since it contains $Q(1)$ in the center, and hence in the center of $\D$.
% %         \item Hence we describe it by $(T, \beta, \kappa)$, where $T\subseteq G^\#$ but $T\not\subseteq G$. 
% %         \item Also, $\rad \beta$ is generated by an odd element of order $2$, say $t_0$.
% %         \item $t_0$ is the parity element according to $\tilde\beta$.
% %     \end{itemize}
% %     \item The old parametrization consisted of a grading on the even part and an element of order $2$ (in $G$) to shift it to the odd part.
% %     \item The old parametrization is only in terms of $G$.
% %     \item the connection must be, top down:
% %     \begin{itemize}
% %         \item The grading on the even part is $(T^+, \beta^+, \kappa)$.
% %         \item Note that $\beta^+$ is nondegenerate on $T^+$.
% %         \item If $t_0 = (h, \bar 1)$, then the shift on the odd part is by $h$, which clearly has order $2$.
% %     \end{itemize}
% %     \item the connection must be, bottom up:
% %     \begin{itemize}
% %         \item Define $t_0$ as $(h, \bar 1)$
% %         \item Define $T$ as $T^+ \cup t_0 T^+$
% %         \item Extend $\beta^+$ to $\beta$ by defining $t_0$ to be in the radical
% %     \end{itemize}
% %     \item we can see it not only on the level of parameters but also on the level of $\End_\D (\U)$:
% %     \item top down:
% %     \begin{itemize}
% %         \item Note that $\End_\D (\U) = \End_{\D\even} (\U\even) \oplus d_0 \End_{\D\even} (\U\even)$, where $d_0 \in Z(\D) \cap \D\odd$. 
% %         Why is that?
% %         \item Well, I guess it starts we getting an even basis for $\U$ and its corresponding $\FF$-form $\widetilde U$. 
% %         \item Then $\End_\D (\U) \equiv \End_\FF (\tilde U) \tensor \D$, hence the even part is $\End_\FF (\tilde U) \tensor \D\even$. 
% %         \item Since $\D\odd = d_0 \D\even$, we get that the odd part is $\End_\FF (\tilde U) \tensor \D\odd = d_0 \End_\FF (\tilde U) \tensor \D\even$
% %         \item The apparent problem here is that the choice of the shift on the odd part doesn't matter.
% %         \item Modulo $T^+$ they are clearly the same, but we don't need $T^+$ in the parametrization
% %         \item Oh, it should be the definition of the product in the down model! $(d_0 r) r' = r (d_0 r')$ and its version for only odd elements. So $d_0 \in Z(R)$.
% %         % \item Also, we could see that $\U\even = \tilde U \tensor \D\even$ and $\U\odd = \tilde U \tensor \D\odd$.
% %     \end{itemize}
% %     \item bottom up:
% %     \begin{itemize}
% %         \item The grading is determined be $\D\even$ and $\U\even$
% %         \item Let $R\even = \End_{\D\even} (\U\even)$ 
% %         \item define $t_0 = (h, \bar 1)$ and introduce a symbol $d_0$ of degree $t_0$, such that $d_0^2 = 1$ and it commutes with every element. This defines $R$.
% %         \item one should check the parameters for $R$. What is the new $\D$?
% %         \item By uniqueness of $\D$ up to iso, we may be able to use the top down part to prove it is what is asked. But we then have to show an isomorphism. Luckily, this is obvious by the definition of the product. 
% %         \item Wait, we have to define $\D$ as $\D\even \oplus d_0\D\odd$, and check it is a graded-division algebra (obvious).
% %     \end{itemize}
% % \end{itemize}
