\section[Graded-division superalgebras of types \texorpdfstring{$M \times M\sop$}{MxMsop} and \texorpdfstring{$Q \times Q\sop$}{QxQsop}]{Graded-division superalgebras of types \\ $M \times M\sop$ and $Q \times Q\sop$}

In the next section, we will classify all group gradings on the superinvolution-simple superalgebras of types $M \times M\sop$ and $Q \times Q\sop$. 
To this end, we will first construct division gradings on those. 

We will assume $\FF$ is algebraically closed and $\Char \FF \neq 2$. 
Fix $i\in \FF$ a primitive fourth-root of unity, \ie, $i^2 = -1$. 

Next subsection presents some well-known concepts and results from the theory of group extensions (see, for example, ?? and ??). 
We put it here for completeness and for fixing notation. 

\subsection{Abelian group extensions}

\begin{defi}
	Let $H, K$ be groups.
	A \emph{group extension of $H$ by $K$} is a group $E$ together with homomorphisms $\iota\from K \to E$ and $\pi\from E \to H$ such that
	%
	\begin{equation}\label{eq:short-exact-sequence}
		0 \rightarrow K \xrightarrow{\iota} E \xrightarrow{\pi} H \rightarrow 0
	\end{equation}
	%
	is a short exact sequence, \ie,
	$\iota$ is injective, $\pi$ is surjective and $\operatorname{im} \iota = \ker \pi$ (and, hence, $H \iso \frac{E}{\iota(K)}$).
	% For brevity, we may refer to the short exact sequence \eqref{eq:short-exact-sequence} as the extension. 
	An \emph{equivalence} between two extensions $K \xrightarrow{\iota} E \xrightarrow{\pi} H$ and $K \xrightarrow{\iota'} E' \xrightarrow{\pi'} H$ is a homomorphism $\alpha\from E \to E'$ such that the diagram
	%     \begin{center}
	% 		\begin{tikzcd}
	% 			&& |[alias=E]|E \arrow[to=E', "\alpha"] \arrow[to = H, "\pi"]&&\\
	% 			K \arrow[to=E, "\iota"] \arrow[to=E', "\iota'"]&&&& |[alias=H]|H\\
	% 			&&|[alias=E']|E' \arrow[to=H, "\pi'"]&&
	% 		\end{tikzcd}
	% 	\end{center}
	%%%%%%%%%%
	\begin{center}
		\begin{tikzcd}
			&& |[alias=E]|E \arrow[to=E', "\alpha"] \arrow[to = H, "\pi"]&&\\
			% 			0 \arrow[to=K]
			& |[alias=K]|K \arrow[to=E, "\iota"] \arrow[to=E', "\iota'"]&& |[alias=H]|H & \\ %\arrow[to=0] & |[alias=0]|0\\
			&&|[alias=E']|E' \arrow[to=H, "\pi'"]&&
		\end{tikzcd}
	\end{center}
	commutes.
	It is easy to see that $\alpha$ is necessarily an isomorphism.
	An equivalence from an extension to itself will be referred as a \emph{self-equivalence}.
\end{defi}

\begin{ex}\label{ex:main-extension}
    Let $T$ be an abelian group and consider $E \coloneqq \big(\pmone \times T^+\big) \cup \big(\{\pm i\} \times T^-\big)$ as a subgroup of $\{ \pm 1, \pm i \} \times T$, and let $\iota\from \pmone \to E$ and $\pi\from E \to T$ be the homomorphisms given by $\iota(\delta) = (\delta, e)$ and $\pi (\delta, t) = t$ for all $\delta \in \pmone$ and $t\in T$.
	Then $\pmone \xrightarrow{\iota} E \xrightarrow{\pi} T$ is an extension of $T$ by $\pmone$.
\end{ex}

Let us fix the abelian groups $H$ and $K$ for the remainder of the section.

\begin{defi}
	A map $\sigma\from H\times H \to K$ is said to be a \emph{$2$-cocycle} if, for all $a,b,c \in H$, we have $\sigma(a,b) \sigma(ab, c) = \sigma(a, bc) \sigma(b,c)$.
	If, further, we have that $\sigma(a,b) = \sigma(b,a)$, we say that $\sigma$ is \emph{symmetric}, and if we have $\sigma(a, e) = \sigma(e, a) = e$, we say that $\sigma$ is \emph{normalized}.
	In the case $\sigma(h_1, h_2) = e$ for all $h_1, h_2 \in H$, we say that $\sigma$ is \emph{trivial}.
\end{defi}

% In this work, we are only going to deal with normalized symmetric $2$-cocycles, so we may refer to them simply as \emph{cocycles}.  

\begin{ex}\label{ex:coboundary-is-cocycle}
	Let $f\from H \to K$ be any map. 
	Recall (\cref{def:coboundary}) that its $2$-coboundary is the map $\mathrm{d} f\from H\times H \to K$ defined by $\mathrm{d} f\, (a,b) = f(ab)f(a)\inv f(b)\inv$ for all $a,b \in H$. 
	It is easy to see that $\mathrm{d} f$ is a $2$-cocycle, which is symmetric since both $H$ and $K$ are abelian. 
	If $f(e) = e$, $\mathrm{d} f$ is also normalized. 
\end{ex}

\begin{ex}\label{ex:bicharacter-is-cocycle}
    Let $T$ be a abelian group and let $b\from T\times T \to \FF^\times$ be a symmetric bicharacter. 
    It is also easy to see that $b$ is a normalized symmetric $2$-cocycle. 
\end{ex}

\begin{ex}\label{ex:beta-is-cocycle}
    Let $\D$ be a finite dimensional graded-division superalgebra associated to $(T, \beta, p)$. 
    If $\beta$ and $\tilde\beta$ only takes values in $\pmone$, then both are symmetric and, hence, normalized symmetric $2$-cocycles. 
    This is not only a particular case of \cref{ex:bicharacter-is-cocycle}, but also of \cref{ex:coboundary-is-cocycle} (by \cref{prop:superpolarization}). 
\end{ex}

% It is easy to check that every symmetric bicharacter is a normalized symmetric $2$-cocycle, and those are the only ones that we will need in this work. 

Given a normalized symmetric $2$-cocycle $\sigma$, we define the abelian group $K \times_\sigma H$ to be the set $K\times H$ with product $*_\sigma$ given by:
\[
	(k_1, h_1)*_\sigma(k_2, h_2) = (\sigma(h_1, h_2) k_1 k_2, h_1 h_2),
\]
for all $k_1, k_2 \in K$ and $h_1, h_2 \in H$.
The condition of $\sigma$ being a symmetric $2$-cocycle is precisely what is needed for the associativity and commutativity of $*_\sigma$.
The identity element is $(e, e)$ and the inverse is given by $(k, h)\inv = (k\inv \sigma(h,h\inv)\inv, h\inv)$.
Note that the usual product on $K\times H$ is recovered as the particular case when $\sigma$ is trivial.

\begin{defi}
	The \emph{(abelian) group extension corresponding to $K \times_\sigma H$} is the group $K \times_\sigma H$ together the group homomorphisms $\iota \from K \to K \times_\sigma H$ and $\pi \from K \times_\sigma H \to H$ defined by $\iota (k) = (k , e)$ and $\pi (k, h) = h$, for all $k\in K$ and $h\in H$.
	If $\sigma$ is trivial, we say that the extension is \emph{trivial}.
\end{defi}

The next result tells us that, essentially, these are all abelian group extensions:

\begin{prop}\label{prop:all-ext-are-cocycle}
	Every abelian group extension $K \xrightarrow{\iota} E \xrightarrow{\pi} H$ is equivalent to the abelian group extension corresponding to $K\times_\sigma H$ for some normalized symmetric $2$-cocycle $\sigma\from H \to K$.
\end{prop}

\begin{proof}
	Fix $\tau\from H \to E$ a (set theoretical) map such that $\pi\tau = id_H$ and $\tau(e) = e$.
	For every $x \in E$, we have that $x (\tau(\pi(x)))\inv$ is in $\ker \pi$ and, hence, it equal to $\iota(k)$ for a unique $k_x\in K$.
	It follows that $x = \iota(k_x) \tau(\pi(x))$.
	Define $f\from E \to K\times H$ by $f(x) = (k_x, \tau(\pi(x)) )$.
	Clearly, $f$ is bijective, so we can make it an isomorphism by using it to define a product on $K\times H$.
	It is easy to check that this product is the one on $K \times_\sigma H$ where $\sigma\from H\times H \to K$ is given by $\sigma(h_1, h_2) = \tau(h_1) \tau(h_2) \tau(h_1 h_2)\inv$ and $f$ is the desired equivalence.
\end{proof}

We will now see to know when two extensions determined by different normalized symmetric $2$-cocycles are equivalent. 

\begin{prop}\label{prop:coboundary}
	Let $\sigma, \sigma' \from H\times H \to K$ be normalized symmetric $2$-cocycles.
	A map $\alpha\from K \times_{\sigma} H \to K \times_{\sigma'} H$ is an equivalence between the corresponding group extensions if, and only if, there is a map $f\from H \to K$ such that $\alpha(k,h) = (f(h) k, h)$, for all $k\in K$ and $h\in H$, and $\sigma' \sigma\inv = \mathrm{d} f$.
\end{prop}

\begin{proof}
	The result follows from the following claims:
	\newclaims
	\begin{claim}
		Suppose $\alpha$ is an isomorphism.
		Then $\alpha$ is an equivalence if, and only if, there is a map $f\from H \to K$ such that $\alpha(k,h) = (f(h)k, h)$, for all $k\in K$ and $h\in H$.
	\end{claim}

	Suppose $\alpha(k,h) = (f(h)k, h)$.
	First, it is clear that $\pi \alpha = \pi$.
	Also, since $\alpha(e,e) = (e,e)$, it follows that $f(e) = e$ and, hence, $\alpha \iota = \iota$.

	Now suppose $\alpha$ is an equivalence.
	Since for all $h\in H$ $(\pi \alpha) (e, h) = \pi (e, h) = h$, we have that $\alpha (e, h) = (f(h), h)$ for some map $f\from H\to K$.
	Also, since for all $k\in K$ $(\alpha \iota) (k) = \iota(k)$, we have that $\alpha(k, e) = (k,e)$.
	It follows that $\alpha (k,h) = \alpha((k,e) *_\sigma (e, h)) = \alpha(k, e) *_{\sigma'} (e, h) = (f(h)k, h)$.

	\begin{claim}
		Suppose there is a map $f\from H \to K$ such that $\alpha(k,h) = (f(h)k, h)$, for all $k\in K$ and $h\in H$.
		Then $\alpha$ is an isomorphism if, and only if, $\sigma'\sigma\inv = \mathrm{d}f$.
	\end{claim}

	First, it is easy to check that the map $K \times_{\sigma'} H \to K \times_{\sigma} H$ given by $(k,h)\mapsto (f(h)\inv k, h)$ is the inverse of $\alpha$, so $\alpha$ is bijective.

	If $h_1, h_2 \in H$ and $t_1, t_2 \in T$, then, on the one hand,
	\begin{align*}
		\alpha ((h_1, t_1)*_{\sigma}(h_2, t_2) ) & = \alpha (\sigma(t_1, t_2) h_1 h_2, t_1 t_2) =
		( f(t_1 t_2)\sigma(t_1, t_2) h_1 h_2, t_1 t_2)
	\end{align*}
	and, on the other hand,
	\begin{align*}
		\alpha ((h_1, t_1)) *_{\sigma'} \alpha ((h_2, t_2) ) & = ( f(t_1) h_1, t_1) *_{\sigma'} ( f(t_2) h_2, t_2) \\&=
		(\sigma'(t_1, t_2) f(t_1) f(t_2) h_1 h_2, t_1 t_2).
	\end{align*}
	Comparing both, we conclude that $\alpha$ is an homomorphism if, and only if, $\mathrm{d}f = \sigma' \sigma\inv$.
\end{proof}

\begin{cor}\label{cor:self-equivalences-are-homomorphisms}
	The set of self-equivalences of an abelian group extension $K \xrightarrow{\iota} E \xrightarrow{\pi} H$ is in bijection with the set of homomorphisms from $H$ to $K$.
\end{cor}

\begin{proof}
	By Proposition \ref{prop:all-ext-are-cocycle}, we can assume our extension is the one corresponding to $K \times_\sigma H$, for some normalized symmetric $2$-cocycle $\sigma$.
	The result follows from Proposition \ref{prop:coboundary} and the observation that $\mathrm{d}f = 0$ if, and only if, $f$ is a homomorphism.
\end{proof}

\subsection{Quadratic maps and (super-)anti-automorphisms}

Let $\D$ be a finite dimensional graded-division superalgebra associated to $(T, \beta, p)$ and choose elements $0\neq X_t \in \D_t$ for all $t\in T$. 
Recall from \cref{prop:superpolarization} that super-anti-automorphisms of $\D$ are in bijection with maps $\eta\from T \to \FF^\times$ such that $\mathrm{d}\eta = \tilde\beta$. 
The same computation with $p$ trivial shows that anti-automorphisms of $\D$ are in bijection with maps $\eta\from T \to \FF^\times$ such that $\mathrm{d}\eta = \beta$ (see also \cite{livromicha}). 

Even though we are mainly interested in superinvolutions, some super-anti-automorphisms which are not involutive, and even some anti-automorphisms, will useful in what follows and also in \cref{chap:Lie}. 
We will need the ones that correspond to quadratic maps.

\begin{defi}
	Let $\mu\from T \to \FF^\times$ be a map.
	We say that $\mu$ is a \emph{(multiplicative) quadratic map} if $\mu(t\inv) = \mu (t)$ for all $t\in T$ and the map $\mathrm{d}\mu\from T\times T \to \FF^\times$ 
	is a bicharacter, which is referred to as the \emph{polarization} of $\mu$.
\end{defi}

\begin{remark}
	In the literature, the additive notation is usually used in the context of quadratic maps.
	In general, for a given commutative ring $\mathbb K$ and $\mathbb K$-modules $A$ and $B$, a quadratic map $q\from A \to B$ is a map satisfying that $q(kx) = k^2 x$, for all $k\in \mathbb K$ and $x \in A$, and that the map $A \times A \to B$ defined by $(x,y) \mapsto q(x+y) - q(x) - q(y)$ is bilinear.
	In the case of abelian groups (\ie, $\mathbb K = \ZZ$), the first condition is equivalent to $q(-x) = q(x)$, justifying our nomenclature. 
\end{remark}

In next example, a quadratic map is used to construct a anti-isomorphism between different graded-division superalgebras:

\begin{ex}\label{ex:quadratic-form-polarization-parity}
	Let $\mu_0\from T \to \FF^\times$ be given by $\mu_0(t) = 1$ for all $t\in T^+$ and $\mu_0(t) = i$ for all $t\in T^-$.
	It is clear that $\mu_0(t\inv) = \mu_0(t)$.
	Also, we have that $\mathrm{d}\mu_0 \, (a,b) = \mu_0(ab) \mu_0(a)\inv \mu_0(b)\inv = (-1)^{p(a)p(b)}$, which is a symmetric bicharacter. 
	This quadratic map determines an anti-isomorphism $\D \to \D\sop$, $X_t\mapsto \mu_0(t)\overline{X_t}$. 
	Note that, in particular, $\D\sop$ is isomorphic to $\D^{\mathrm{op}}$.
\end{ex}

\begin{lemma}\label{lemma:quadratic-form-involutions}
	Let $\mu\from T \to \FF^\times$ be a map and let $\psi\from \D \to \D$ be the linear map defined by
	$\psi(X_t) = \mu(t) X_t$ for every $t\in T$ and $X_t \in \D_t$.
	Then:
	\begin{enumerate}[(i)]
		\item If $\mathrm{d}\mu = \tilde\beta$, then: \\
		      $\mu$ is a quadratic map $\iff$ $\mu(t)\in \{ \pm 1 \}$ for all $t \in T^+$ and $\mu(t)\in \{ \pm i \}$ for all $t \in T^-$ $\iff$ $\psi$ is a super-anti-automorphism such that $\psi^2$ is the parity automorphism on $\D$; \label{item:super-anti-auto-quadratic}
		\item If $\mathrm{d}\mu = \beta$, then:\\
		      $\mu$ is a quadratic map $\iff$ $\mu(t) \in \{\pm 1\}$ for all $t\in T$ $\iff$ $\psi$ is
		      an involution on $\D$. \label{item:anti-auto-quadratic}
	\end{enumerate}
\end{lemma}

\begin{proof}
	From Equation \eqref{eq:superpolarization}, we have $\tilde\beta (t, t\inv) = \mu (tt\inv) \mu(t)\inv \mu(t\inv)\inv$, which simplifies to $(-1)^{p(t)} = \mu(t)\mu(t\inv)$.
	Therefore $\mu(t\inv) = \mu(t)$ if, and only if, $\mu(t)^2 = (-1)^{p(t)}$, proving \eqref{item:super-anti-auto-quadratic}.

	Item \eqref{item:anti-auto-quadratic} follows from \eqref{item:super-anti-auto-quadratic} once we consider $\D$ as an algebra, \ie, if we consider $p$ to be the trivial homomorphism.
	% First note that, as a particular case of Proposition \ref{prop:superpolarization}, $\psi$ is an antiautomorphism if, and only, if 
	% %
	% \begin{equation}\label{eq:polarization}
	%     \forall a,b\in T, \quad \beta(a,b) = \mu(ab) \mu(a)\inv \mu(b)\inv.
	% \end{equation}
	% %
	% Then $1 = \beta(t, t\inv) = \mu (tt\inv) \mu(t)\inv \mu(t\inv)\inv$, hence $\mu(t\inv) = \mu(t)\inv$. 
	% Therefore we have that $\mu(t\inv) = \mu(t)$ if, and only if, $\mu(t)^2 = 1$, proving (i).
\end{proof}

We will now refine the statement about existence of $\eta$ in \cref{prop:superpolarization}:

\begin{prop}\label{prop:existence-involution}
	If $\beta$ takes values in $\{ \pm 1 \}$, then there are quadratic maps on $T$ whose polarizations are $\beta$ and $\tilde \beta$.
\end{prop}

\begin{proof}
	To show there is a quadratic map whose polarization is $\beta$,
	consider the group $\barr T \coloneqq \frac{T}{\rad \beta}$ and let $t \mapsto \bar t$ be the natural projection on the quotient.
	Also, we denote by $\barr \beta\from \barr T \times \barr T \to \FF^\times$ the bicharacter induced by $\beta$.

	Since $\barr \beta$ is nondegenerate and takes values $\pm 1$, $\barr T$ is an elementary $2$-group. 
	Choose a standard realization $\barr \D$ associated to $(\barr T, \barr \beta)$. 
	By \cref{lemma:transp-std-realization}, the transposition is a degree-preserving involution of $\barr \D$, so it is determined by a map $\bar \mu\from T \to \FF^\times$ be the map determining the transposition on $\barr \D$. 
	By \cref{lemma:quadratic-form-involutions}, $\bar\mu$ is a quadratic map taking values in  $\{ \pm 1 \}$ whose polarization is $\bar\beta$. 
	Define $\mu\from T\to \FF^\times$ by $\mu (t) = \barr \mu (\bar t)$ for all $t\in T$.
	Then $\mu$ takes values in $\{ \pm 1 \}$ and $\beta = \mathrm{d} \mu$. 
	
	To get a quadratic map with polarization $\tilde \beta$, simply multiply $\mu$ by the quadratic map $\mu_0$ of Example \ref{ex:quadratic-form-polarization-parity}.
\end{proof}

\subsection{Division gradings on $\D \times \D\sop$}

We are now in position to apply these concepts and results to our original problem. 

\begin{lemma}\label{lemma:tildeT-finally}
	Suppose $\beta$ takes values in $\pmone$ and let $\sigma\from T\times T \to \pmone$ be the $2$-cocycle given by $\sigma(a,b) \coloneqq (-1)^{p(a)p(b)}$.
	The group extensions corresponding to $\pmone \times_{\tilde\beta} T$ and $\pmone \times_\sigma T$ are both equivalent to the extension of Example
	\ref{ex:main-extension}.
	% Further, $\pmone \times_\sigma T$ is isomorphic to the subgroup of $\{\pm 1, \pm i\} \times T$ given by $\big(\pmone \times T^+\big) \cup \big(\{\pm i\} \times T^-\big)$.
\end{lemma}

\begin{proof}
	By Proposition \ref{prop:existence-involution}, there is a map $\mu\from T \to \{\pm 1\}$ such that $\beta = \mathrm{d}\mu$, hence, using Proposition \ref{prop:coboundary}, the group extensions corresponding to $\pmone \times_{\tilde\beta} T$ and $\pmone \times_\sigma T$ are equivalent.

	We can consider the $2$-cocycle $\sigma$ as admitting values in $\{\pm 1, \pm i\}$.
	We then have $\pmone \times_\sigma T \subseteq \{\pm 1, \pm i\} \times_\sigma T$.
	But then we can use the quadratic map $\mu_0$ from Example \ref{ex:quadratic-form-polarization-parity} to conclude that, since $\sigma = \mathrm{d} \mu_0$, the extension $\{\pm 1, \pm i\} \to \{\pm 1, \pm i\} \times_\sigma T \to T$ is equivalent to the trivial extension $\{\pm 1, \pm i\} \to \{\pm 1, \pm i\} \times T \to T$ via the isomorphism $\alpha\from \{\pm 1, \pm i\} \times_\sigma T \to \{\pm 1, \pm i\} \times T$ given by $\alpha(\lambda, t) = (\mu_0(t) \lambda, t)$.
	Following this isomorphism, we see that the image of $\pmone \times_\sigma T$ is precisely the group extension of Example \ref{ex:main-extension} and we get an equivalence if we restrict $\alpha$ accordingly.
\end{proof}

% The next result show us Our strategy consists in start with a graded division superalgebra $\D$ with $\beta$ taking values in $\{ \pm 1 \}$. 
% By Proposition \ref{prop:refinement-DxDsop} below, we can, then, refine the grading on $\D \times \D\sop$ to a division grading such that the exchange superinvolution preserves degree. 
% The refinement 

% If $\D$ is a graded division superalgebra with $\beta$ taking values in $\{ \pm 1 \}$, we can refine the 
% Then the grading on $\D \times \D\sop$ can be refined to a division grading such that the exchange superinvolution $\vphi$ preserves degree.

% \begin{prop}\label{prop:refinement-DxDsop}
%     Let $\D$ be a graded division superalgebra with support $T$ and $\beta$ taking values in $\{ \pm 1 \}$. 
%     Consider $\mc E \coloneqq \D \times \D\sop$ with its natural $T$-grading $\Gamma\colon \mc E = \bigoplus_{t\in T} \D_t \times \overline{\D_t}$ and let $\vphi$ be the exchange superinvolution on $\mc E$. 
%     Then there is a division grading $\widetilde \Gamma$ on $(\mc E, \vphi)$ by $\widetilde T$ such that $\Gamma = {}^\pi\widetilde \Gamma$, \ie, $\Gamma$ is the coarsening of $\widetilde \Gamma$ by $\pi$. 
%     Moreover, if $\Gamma'$ is another division grading on $(\mc E, \vphi)$ by an abelian group $T'$ such that $\Gamma = {}^{\pi'}\Gamma'$ for some homomorphism $\pi'\from T' \to T$, then there is a unique isomorphism $\alpha\from T \to  T'$ such that $\pi = \pi' \alpha$ and $\Gamma' = {}^\alpha \widetilde \Gamma$.

%     % , let $\mc E \coloneqq \D \times \D\sop$ and $\vphi$ be the exchange superinvolution on $\mc E$. 
%     % The grading on $\mc E$ can be refined to a division grading such that $\vphi$ preserves degrees if, and only if, $\beta$ takes values $\pm 1$. 
%     % % If $\beta$ takes values $\pm 1$, the grading on $\D \times \D\sop$ can be refined to a division grading such that the exchange superinvolution preserves degree. 
%     % % if, and only if, $\beta$ takes values $\pm 1$
%     % Every such refinement has support isomorphic to $\widetilde T \coloneqq \{ \pm 1 \}\times T$ with product
%     % % and suppose there is a super-anti-automorphism $\psi$ on $\D$ preserving degrees. 
%     % % Then the grading on $\D \times \D\sop$ can be refined to a division grading such that the exchange superinvolution $\vphi$ preserves degree.
% \end{prop}

% \begin{prop}\label{prop:refinement-DxDsop}
%     Let $\D$ be a graded division superalgebra associated to $(T, \beta, p)$.  
%     Consider $\mc E \coloneqq \D \times \D\sop$ with its natural $T$-grading $\Gamma\colon \mc E = \bigoplus_{t\in T} \D_t \times \overline{\D_t}$ and let $\vphi$ be the exchange superinvolution on $\mc E$. 
%     There is a division grading on $(\mc E, \vphi)$ refining $\Gamma$ if, and only if, $\beta$ takes values in $\{ \pm 1 \}$. 
%     If $\widetilde \Gamma$ is a such grading and $\widetilde T$ is its support, then there are group homomorphisms $\tilde \pi\from \widetilde T \to T$ and $\alpha\from \widetilde T \to \{ \pm 1\} \times_\sigma T$, where $\sigma$ is the bicharater defined by $\sigma(a,b) = (-1)^{p(a)p(b)}$, such that $\Gamma = {}^{\tilde\pi}\widetilde \Gamma$ and $\pi_\sigma \alpha = \tilde \pi$.
% \end{prop}

% \begin{thm}\label{thm:refinement-DxDsop}
%     Let $\D$ be a graded division superalgebra associated to $(T, \beta, p)$.  
%     Consider $\mc E \coloneqq \D \times \D\sop$ with its natural $T$-grading $\Gamma\colon \mc E = \bigoplus_{t\in T} \D_t \times \overline{\D_t}$ and let $\vphi$ be the exchange superinvolution on $\mc E$. 
%     There is a division grading on $(\mc E, \vphi)$ refining $\Gamma$ if, and only if, $\beta$ takes values in $\{ \pm 1 \}$. 
%     If this is the case, we have the following:
%     % and $\widetilde T$ is its support, then:

%     % Then:
%     \begin{enumerate}[(i)]
%         % \item There is a division grading on $(\mc E, \vphi)$ refining $\Gamma$ if, and only if, $\beta$ takes values in $\{ \pm 1 \}$; \label{item:refinement-iff-pmone} 

%         \item %$\widetilde T$ fits into
%         If $\Delta$ is such a refinement, then there is a unique group extension $\{ \pm 1 \} \xrightarrow{\iota} E \xrightarrow{\pi} T$ such that $\supp \Delta = E$ and ${}^{\pi} \Delta = \Gamma$; \label{item:there-is-extension}

%         \item This group extension is equivalent to the one of Example \ref{ex:main-extension}; \label{item:equivalent-extension-example}
%         %determined by the $2$-cocycle $\sigma(a,b) \coloneqq (-1)^{p(a) p(b)}$, for all $a,b\in T$; 

%         \item The set of all refinements $\Delta$ such that $\supp \Delta = E$ and ${}^\pi \Delta = \Gamma$ is in bijection with the group homomorphisms from $T$ to $\{ \pm 1 \}$. \label{item:number-of-extensions}
%     \end{enumerate}
%     % There is a division grading on $(\mc E, \vphi)$ refining $\Gamma$ if, and only if, $\beta$ takes values in $\{ \pm 1 \}$. 
%     % If $\widetilde \Gamma$ is a such grading and $\widetilde T$ is its support, then there is a unique group extension $0 \to \{ \pm 1 \} \xrightarrow{\iota} \widetilde T \xrightarrow{\pi} T \to 0$ such that ${}^\pi \widetilde \Gamma = \Gamma$, and this extension is equivalent to the one given by the $2$-cocycle $\sigma$ given by $\sigma(a,b) = (-1)^{p(a) p(b)}$. 
%     % Moreover, the set of all gradings corresponding to $0 \to \{ \pm 1 \} \xrightarrow{\iota} \widetilde T \xrightarrow{\pi} T \to 0$ is in bijection with its self-equivalences.
% \end{thm}

\begin{thm}\label{thm:refinement-DxDsop}
	Let $\D$ be a graded division superalgebra associated to $(T, \beta, p)$.
	Consider $\mc E \coloneqq \D \times \D\sop$ with its natural $T$-grading $\Gamma\colon \mc E = \bigoplus_{t\in T} \D_t \times \overline{\D_t}$ and let $\vphi$ be the exchange superinvolution on $\mc E$.
	There is a division grading on $(\mc E, \vphi)$ refining $\Gamma$ if, and only if, $\beta$ takes values in $\{ \pm 1 \}$.
	If this is the case, let $\Delta$ be such a refinement, associated to $(T_\Delta, \beta_\Delta, p_\Delta, \eta_\Delta)$.
	Then: % we have the following:
	% and $\widetilde T$ is its support, then:
	%
	\begin{enumerate}[(i)]
		% \item There is a division grading on $(\mc E, \vphi)$ refining $\Gamma$ if, and only if, $\beta$ takes values in $\{ \pm 1 \}$; \label{item:refinement-iff-pmone} 

		\item %$\widetilde T$ fits into
		      $T_\Delta$ fits into a unique group extension $\{ \pm 1 \} \xrightarrow{\iota} T_\Delta \xrightarrow{\pi} T$ such that ${}^{\pi} \Delta = \Gamma$; \label{item:there-is-extension}

		\item This group extension is equivalent to the one of Example \ref{ex:main-extension}; \label{item:equivalent-extension-example}
		      %determined by the $2$-cocycle $\sigma(a,b) \coloneqq (-1)^{p(a) p(b)}$, for all $a,b\in T$; 
		\item $\beta_\Delta = \beta \circ (\pi \times \pi)$ and $p_\Delta = p \circ \pi$; \label{item:beta-and-p-delta}
		\item If $\tilde \Delta$ is another refinement with $\supp \tilde \Delta = T_\Delta$ and ${}^\pi \tilde \Delta = \Gamma$, then there is a unique self-equivalence $\alpha$ of $\{ \pm 1 \} \xrightarrow{\iota} T_\Delta \xrightarrow{\pi} T$ such that $\tilde \Delta = {}^\alpha \Delta$.
		Moreover, $\eta_{\tilde \Delta} = \eta_\Delta \circ \alpha$. \label{item:number-of-extensions}
	\end{enumerate}

	% There is a division grading on $(\mc E, \vphi)$ refining $\Gamma$ if, and only if, $\beta$ takes values in $\{ \pm 1 \}$. 
	% If $\widetilde \Gamma$ is a such grading and $\widetilde T$ is its support, then there is a unique group extension $0 \to \{ \pm 1 \} \xrightarrow{\iota} \widetilde T \xrightarrow{\pi} T \to 0$ such that ${}^\pi \widetilde \Gamma = \Gamma$, and this extension is equivalent to the one given by the $2$-cocycle $\sigma$ given by $\sigma(a,b) = (-1)^{p(a) p(b)}$. 
	% Moreover, the set of all gradings corresponding to $0 \to \{ \pm 1 \} \xrightarrow{\iota} \widetilde T \xrightarrow{\pi} T \to 0$ is in bijection with its self-equivalences.
\end{thm}

\begin{proof}
	We claim that all division gradings on $(\mc E, \vphi)$ refining $\Gamma$ must have the same set of subspaces of $\mc E$ as their homogeneous components.
	Indeed, for each $t\in T$, let $\mc E_t$ denote the homogeneous component of degree $t$ of $\Gamma$.
	Clearly, $\mc E_t$ is $2$-dimensional and $(X_t, \overline{X_t})$ and $(X_t, -\overline{X_t})$ are eigenvectors of $\vphi$, associated to the eigenvalues $1$ and $-1$, respectively.
	It follows that the eigenspaces of $\vphi \restriction_{\mc E_t}$ are $1$-dimensional and, hence, $(X_t, \overline{X_t})$ and $(X_t, -\overline{X_t})$ must be homogeneous in any grading $\Delta$ on $(\mc E, \vphi)$ refining $\Gamma$.
	If $\Delta$ is a division grading, all the components are $1$-dimensional, so the components must be $\mc E_{(\delta, t)} \coloneqq \FF (X_t, \delta \overline{X_t})$, for $t\in T$ and $\delta \in \pmone$.

	% the eigenspaces of $\vphi \restriction_{\mc E_t}$ associated to $1$ and $-1$ are both one dimensional, spanned by $(X_t, \overline{X_t})$ and $(X_t, -\overline{X_t})$, respectively. 
	% It follows that $(X_t, \overline{X_t})$ and $(X_t, -\overline{X_t})$ must be homogeneous in any grading on $(\mc E, \vphi)$ refining $\Gamma$. 
	% If such refinement is a division grading, the components must be $1$-dimensional, so the components must be the 

	% Hence on any division grading on $(\mc E, \vphi)$ refining the natural $T$-grading on $\mc E$, these eigenspaces have to be the homogeneous components. 
	% We will denote the subspace generated by $(X_t, \delta\overline{X_t})$, for $\delta \in \{ \pm 1 \}$, by $\mc E_{(\delta, t)}$. 
	% Clearly, $\mc E$ is the direct sum of all subspaces of this form. 

	Now, for all $a, b \in T$ and $\delta_1, \delta_2 \in \{ \pm 1 \}$, we have:
	%
	\begin{align*}
		(X_{a}, \delta_1 \overline{X_{a}})(X_{b}, \delta_2 \overline{X_{b}}) & = (X_{a} X_{b}, \delta_1 \delta_2 \overline{X_{a}} \,\overline{X_{b}})               \\
		                                                                     & = (X_{a} X_{b}, \delta_1 \delta_2 (-1)^{p(a)p(b)} \overline{X_{b}X_{a}})             \\
		                                                                     & =(X_{a} X_{b}, \delta_1 \delta_2 (-1)^{p(a)p(b)} \beta(a, b) \overline{X_{a} X_{b}}) \\
		                                                                     & = (X_{a} X_{b}, \delta_1 \delta_2 \tilde\beta (a,b) \overline{X_{a} X_{b}}).
	\end{align*}
	%
	On the one hand, if $\beta(a, b) \neq \pm 1$ for some $a,b \in T$, the direct sum decomposition $\mc E = \bigoplus \mc E_{(\delta, t)}$ not a grading of $\mc E$ as a superalgebra.
	On the other hand, if $\beta$ takes values in $\{ \pm 1 \}$, it follows that $\mc E_{(\delta_1, a)} \mc E_{(\delta_2, b)} = \mc E_{(\delta_1 \delta_2 \tilde\beta (a,b), ab)}$.
	Therefore we have a grading by the group $\{ \pm 1\} \times_{\tilde\beta} T$.
	Let us denote this grading by $\Delta_0$.
	% If $\pmone \xrightarrow{\tilde\iota} \{ \pm 1\} \times_{\tilde\beta} T \xrightarrow{\tilde\pi} T$ is the extension correponding to $\{ \pm 1\} \times_{\tilde\beta} T$, then it is clear that ${}^{\tilde\pi}\Delta_0 = \Gamma$. 
	% Note that, by Lemma ??, this group extension is equivalent to the one in Example \ref{ex:main-extension}.

	We will now proceed to prove \eqref{item:there-is-extension}.
	Recall that, for a division grading, its support is its universal group (Lemma \ref{lemma:div-grd-unvrsl-grp}).
	Since $\Gamma$ is a coarsening of $\Delta$, by the universal property of the universal group, there is a unique map $\pi\from E\to T$ such that ${}^{\pi}\widetilde \Gamma = \Gamma$.
	Also, since $|\widetilde T| = 2 |T|$, we must have $|\ker \pi| = 2$, and therefore there is a unique monomorphism $\iota\from \pmone \to \widetilde T$ with $\iota(\pmone) = \ker \pi$.
	Note that in the particular case $\Delta = \Delta_0$, we get the extension associated to $\pmone \times_{\tilde\beta} T$.

	We will also use the universal property of the universal group to prove items \eqref{item:equivalent-extension-example} and \eqref{item:number-of-extensions}.
	Let $\Delta$ and $\Delta'$ be division gradings on $(\mc E, \vphi)$ refining $\Gamma$, with the correponding extensions being $\{ \pm 1 \} \xrightarrow{\iota} E \xrightarrow{\pi} T$ and $\{ \pm 1 \} \xrightarrow{\iota'} E' \xrightarrow{\pi'} T$, respectively.
	Since they have the same components, $\Delta$ is a (improper) refinement of $\Delta'$, so there is a unique group homomorphism $\alpha\from E \to E'$ such that ${}^\alpha \Delta = \Delta'$.
	% Exchanging the roles of $\Delta$ and $\Delta'$ we have that $\alpha$ is an isomorphism. 
	Also, by the uniqueness of $\pi$, we have $\pi = \pi' \alpha$ and, by the uniqueness of $\iota'$, we have $\iota' = \alpha \iota$.
	We conclude not only that the extensions are equivalent, but also that $\alpha$ is the unique equivalence between them such that ${}^\alpha \Delta = \Delta'$.

	Putting $\Delta' = \Delta_0$, we obtain item \eqref{item:equivalent-extension-example} follows from Lemma \ref{lemma:tildeT-finally}.

	To prove \eqref{item:number-of-extensions},
	suppose $\Delta$ and $\Delta'$ correspond to the same group extension.
	Then there is a unique self-equivalence $\alpha$ of $\{ \pm 1 \} \xrightarrow{\iota} E \xrightarrow{\pi} T$ such that ${}^\alpha \Delta = \Delta'$.
	Conversely,
	note that for every self-equivalence $\alpha$ of $\{ \pm 1 \} \xrightarrow{\iota} E \xrightarrow{\pi} T$, we have that the grading ${}^\alpha \Delta$ also corresponds to this extension, since $\pi\alpha = \pi$.
	So the gradings corresponding to the extension $\{ \pm 1 \} \xrightarrow{\iota} E \xrightarrow{\pi} T$ are in bijection with its self-equivalences.
	% Now Corollary \ref{cor:self-equivalences-are-homomorphisms} concludes the proof.
\end{proof}

\begin{prop}\label{lemma:undoubling-D}
    Let $(\mc E, \vphi_0)$ be a finite dimensional graded-division superalgebra with superinvolution associated to a quadruple $(T, \beta, p, \eta)$. 
    Suppose there is an order 
\end{prop}


% Since this extension is equivalent to the one corresponding to $\pmone \times_{\tilde\beta} T$, we can apply Corollary \ref{cor:self-equivalences-are-homomorphisms} to conclude that the self-equivalences are in bijection with group homomorphisms from $T$ to $\pmone$, concluding the proof.
% 
% 
% 
% Since the direct sum decomposition of $\widetilde \Gamma$ must be the same of $\Delta$, let $\alpha\from \widetilde T \to \pmone \times_{\tilde\beta} T$ be the bijection such that the component of degree $\tilde t$ with respect to $\widetilde T$ is the component of degree $\alpha(\tilde t)$ with respect to $\Delta$. 
% In other
% 
% the identity map on $\mc E$ an equivalence between 
% Recall that the support of a division grading is its universal group (Lemma ??). 
% For each $\tilde t\in \widetilde T$, there are unique $\delta \in \pmone$ and $t\in T$ such that the component of $\tilde t$ with respect to $\widetilde \Gamma$ is $\mc E_{(\delta, t)}$. 
% Let us define 

% Let $\pi\from \widetilde T \to T$ be defined by $\pi(\tilde t) = t$ and $\alpha\from \widetilde T \to \pmone \times_{\tilde\beta} T$  be defined by $\alpha(\tilde t) = (\delta, t)$. 

% We claim that $\pi$ is a group homomorphism. 
% Indeed, given $\tilde t_1, \tilde t_2 \in \widetilde T$, since the component of $\tilde t_1, \tilde t_2$ is nonzero, there is a $t\in T$ such that $\pi(\tilde t_1, \tilde t_2) = t$ and, since $\Gamma$ is a grading, $t = \pi(\tilde t_1) \pi(\tilde t_2)$. 
% Clearly, ${}^{\pi}\widetilde \Gamma = \Gamma$. 
% On the one hand, if there is a group homomorphism $\pi'\from \widetilde T \to T$ such that ${}^{\pi'}\widetilde \Gamma = \Gamma$, then, clearly, we need $\pi'(\tilde t) = t$, so $\pi' = \pi$. 
% % On the other hand, defining $\pi$ this formula , we have that, since $\widetilde T$ is the support of $\widetilde \Gamma$, $\pi$ is, indeed, a group homomorphism
% Also, since $|\widetilde T| = 2 |T|$, we must have $|\ker \pi| = 2$, so there is a unique monomorphism $\iota\from \pmone \to \widetilde T$ with $\iota(\pmone) = \ker \pi$. 
% This proves \eqref{item:there-is-extension}. 
% Note that, for the particular case $\widetilde \Gamma = \Delta$, we have that this produces the group extension associated to $\tilde \beta$.

% We now claim that $\alpha\from \widetilde T \to \pmone \times_{\tilde\beta} T$ is a group isomorphism. 
% The proof it is a homomorphism is analogous to the proof $\pi$ is a homomorphism. 
% Also, $\alpha$ is necessarily a bijection, since every component $\mc E_{(\delta, t)}$ also corresponds to a unique component of the grading $\widetilde \Gamma$. 
% By definition, it is the only map such ${}^\alpha \widetilde\Gamma = \Delta$. 
% The isomorphism $\alpha$ is an equivalence between the corresponding group extensions. 
% In particular, given two gradings, there is a unique equivalence between the corresponding group extensions. 

% % From this and the assumption that $\beta$ takes values in $\{ \pm 1 \}$, it follows that we can grade $\mc E$ by the group $\{ \pm 1\} \times_{\tilde\beta} T$ by defining the degree of $(X_t, \delta\overline{X_t})$ to be $(\delta, t)$, for all $t \in T$ and $\delta \in \{ \pm 1 \}$.

% Using again that $\beta$ takes values in $\{ \pm 1 \}$, by Proposition ?? there is a quadratic map $\mu$ on $T$ whose polarization is $\beta$. 
% Since $\mu$ takes values in $\{ \pm 1 \}$, it follows that $\beta$ is a $2$-coboundary, so by Proposition ??, there is an isomorphism from $\{ \pm 1 \} \times_{\tilde\beta} T$ to $\{ \pm 1 \} \times_{\sigma} T$ preserving the projection on $T$.

% % Consider the automorphism $\theta\from \D \times \D\sop \to \D \times \D\sop$ given by $\theta (x, \bar y) = (\psi(y), \overline{\psi(x)})$. 
% % Clearly, $\theta$ is preserves degrees and commutes with the exchange superinvolution. 
% % Hence, by ??, it corresponds to a refinement of the grading on $(\D \times \D\sop, \psi)$. 
% % Also, if $\eta\from T \to \FF^\times$ is the map corresponding to $\psi$, then $\theta(X_t, \overline{X_t}) = \eta(t) (X_t, \overline{X_t})$ and $\theta(X_t, -\overline{X_t}) = -\eta(t) (X_t, \overline{X_t})$, hence $(X_t, \overline{X_t})$ and $(X_t, -\overline{X_t})$ lie in different components. 
% % Therefore each component have dimension at most $1$, completing the proof.
% \end{proof}

\begin{cor}\label{cor:old-item-iv}
	Under the conditions of Theorem \ref{thm:refinement-DxDsop}, the set of all refinements $\Delta$ such that $\supp \Delta = T_\Delta$ and ${}^\pi \Delta = \Gamma$ is in bijection with the group homomorphisms from $T$ to $\{ \pm 1 \}$.
\end{cor}

\begin{proof}
	It follows from item \eqref{item:number-of-extensions} and Corollary \ref{cor:self-equivalences-are-homomorphisms}.
\end{proof}

It is worth emphasizing that all these refinements are nonisomorphic as graded superalgebras with superinvolution, but they are isomorphic as graded superalgebras.
% The parameters are $(T_\Delta, \beta_\Delta, p_\Delta, \eta_\Delta \circ \alpha)$.
% This can be seen by looking on the parameters defining their equivalence class. 

% \begin{remark}
%     Note that quadratic maps could have been avoided if we decided to keep working with the group $\pmone \times_{\tilde\beta} T$. 
%     Nevertheless, the quadratic maps allowed us to to find a more explicit model for the extension, not depending on $\beta$.
% \end{remark}

% \begin{remark}
%     The refinement above could have been construct using the eigenspace decomposition of an automorphism on $\mc E$. 
%     Since $\beta$ takes values in $\{ \pm 1 \}$, there is a super-anti-automorphism $\psi\from \D \to \D$ of order form. 
%     Then the map $\Psi\from \mc E \to \mc E$ defined by $\Psi(x, \bar y) = (\psi (y), \overline{\psi(x)})$ is an automorphism of order $4$ commuting with the exchange superinvolution.
% \end{remark}

We will now present an example of such a refinement, which will play an important role in the next section. 
Let $\D$ be $M(1,1)$ with the division grading by $T \coloneqq \ZZ_2 \times \ZZ_2$ determined by:
\begin{align*}
	\deg \begin{pmatrix}
		\phantom{.}1 & \phantom{-}0\phantom{.} \\
		\phantom{.}0 & \phantom{-}1\phantom{.}
	\end{pmatrix} = (\bar 0, \bar 0),\quad & \deg \begin{pmatrix}
		\phantom{.}0 & \phantom{-}1\phantom{.} \\
		\phantom{.}1 & \phantom{-}0\phantom{.}
	\end{pmatrix} = (\bar 0, \bar 1), \\
	\deg \begin{pmatrix}
		\phantom{.}1 & \phantom{-}0\phantom{.} \\
		\phantom{.}0 & -1\phantom{.}
	\end{pmatrix} = (\bar 1, \bar 0),\quad &
	\deg \begin{pmatrix}
		\phantom{.}0 & -1\phantom{.}           \\
		\phantom{.}1 & \phantom{-}0\phantom{.}
	\end{pmatrix} = (\bar 1, \bar 1).
\end{align*}
%
%
% \begin{center}
%     \begin{tabular}{ c c }
%         $\deg \begin{pmatrix}
%         \phantom{.}1 & \phantom{-}0\phantom{.}\\
%         \phantom{.}0 & \phantom{-}1\phantom{.}
%         \end{pmatrix} = (\bar 0, \bar 0)$, & $\deg \begin{pmatrix}
%         \phantom{.}0 & \phantom{-}1\phantom{.} \\
%         \phantom{.}1 & \phantom{-}0\phantom{.}
%         \end{pmatrix} = (\bar 0, \bar 1)$,\\
%         \rule{0pt}{4ex}   
%         $\deg \begin{pmatrix}
%         \phantom{.}1 & \phantom{-}0\phantom{.}\\
%         \phantom{.}0 & -1\phantom{.}
%         \end{pmatrix} = (\bar 1, \bar 0)$, &
%         $\deg \begin{pmatrix}
%         \phantom{.}0 & -1\phantom{.} \\
%         \phantom{.}1 & \phantom{-}0\phantom{.}
%         \end{pmatrix} = (\bar 1, \bar 1)$.
%     \end{tabular}
% \end{center}
%
From Theorem \ref{thm:refinement-DxDsop}, we get a grading by the subgroup $E \coloneqq \big( \pmone \times \ZZ_2 \times \{ \bar 0 \} \big) \cup \big( \{ \pm i \} \times \ZZ_2 \times \{ \bar 1 \} \big)$ of $\{\pm 1, \pm i\} \times \ZZ_2 \times \ZZ_2$.
Note that this group is isomorphic to $\ZZ_2 \times \ZZ_4$ via the homomorphism determined by $(1, \bar 1, \bar 0) \mapsto (\bar 1, \bar 0)$ and $(i, \bar 0, \bar 1) \mapsto (\bar 0, \bar 1)$.

To construct this grading explicitly, we follow the proof of Theorem \ref{thm:refinement-DxDsop}.
First, we get a grading by $\pmone \times_{\tilde\beta} T$ on $\D\times \D\sop$ given by $\deg (X_t, \delta \overline{X_t}) = (\delta, t)$, for all $\delta \in \pmone$ and $t\in T$.
Then, to get a simpler model for the group, we follow the proof of Lemma \ref{lemma:tildeT-finally}, where we need to choose a quadratic map $\mu$ on $T$ whose polarization is $\beta$, which is equivalent to choosing an involution on $\D$ as a graded algebra.
We can choose the involution to be the transposition, \ie, $\mu(\bar 0, \bar 0) = 1$, $\mu(\bar 0, \bar 1) = 1$, $\mu(\bar 1, \bar 0) = 1$ and $\mu(\bar 1, \bar 1) = -1$.
We then get a grading by $\pmone \times_\sigma T$, where $\sigma(a,b) \coloneqq (-1)^{p(a)p(b)}$, given by $\deg (X_t, \delta \overline{X_t}) = (\mu(t) \delta, t)$, for all $\delta \in \pmone$ and $t\in T$.
This can be transplanted to the groups $\big(\pmone \times T^+\big) \cup \big(\{\pm i\} \times T^-\big)$ and $\ZZ_2\times \ZZ_4$ via the explicit isomorphisms given in the proof of Lemma \ref{lemma:tildeT-finally} and above.
To summarize:

\begin{ex}\label{ex:superalgebra-O}
	Let $\mc O$ denote the superalgebra $M(1,1) \times M(1,1)\sop$ endowed with the $\ZZ_2\times \ZZ_4$-grading determined by:
	%
	% We can refine the algebra the natural grading on $\D\times \D\sop$ by the division grading determined by:
	%
	\begin{align*}
		% -- 1st row --
		\deg \left(\begin{pmatrix}
			\phantom{.}1 & \phantom{-}0\phantom{.} \\
			\phantom{.}0 & \phantom{-}1\phantom{.}
		\end{pmatrix}, \overline{\begin{pmatrix}
				\phantom{.}1 & \phantom{-}0\phantom{.} \\
				\phantom{.}0 & \phantom{-}1\phantom{.}
			\end{pmatrix}}\right) = (\bar 0, \bar 0),\, &
		\deg \left(\begin{pmatrix}
			\phantom{.}1 & \phantom{-}0\phantom{.} \\
			\phantom{.}0 & \phantom{-}1\phantom{.}
		\end{pmatrix}, -\overline{\begin{pmatrix}
				\phantom{.}1 & \phantom{-}0\phantom{.} \\
				\phantom{.}0 & \phantom{-}1\phantom{.}
			\end{pmatrix}}\right) = (\bar 0, \bar 2),    \\
		% -- 2nd row --
		\deg \left(\begin{pmatrix}
			\phantom{.}1 & \phantom{-}0\phantom{.} \\
			\phantom{.}0 & -1\phantom{.}
		\end{pmatrix}, \overline{\begin{pmatrix}
				\phantom{.}1 & \phantom{-}0\phantom{.} \\
				\phantom{.}0 & -1\phantom{.}
			\end{pmatrix}}\right) = (\bar 1, \bar 0),\, &
		\deg \left(\begin{pmatrix}
			\phantom{.}1 & \phantom{-}0\phantom{.} \\
			\phantom{.}0 & -1\phantom{.}
		\end{pmatrix}, -\overline{\begin{pmatrix}
				\phantom{.}1 & \phantom{-}0\phantom{.} \\
				\phantom{.}0 & -1\phantom{.}
			\end{pmatrix}}\right) = (\bar 1, \bar 2),    \\
		% -- 3rd row --
		\deg \left(\begin{pmatrix}
			\phantom{.}0 & \phantom{-}1\phantom{.} \\
			\phantom{.}1 & \phantom{-}0\phantom{.}
		\end{pmatrix}, \overline{\begin{pmatrix}
				\phantom{.}0 & \phantom{-}1\phantom{.} \\
				\phantom{.}1 & \phantom{-}0\phantom{.}
			\end{pmatrix}}\right) = (\bar 0, \bar 1),\, &
		\deg \left(\begin{pmatrix}
			\phantom{.}0 & \phantom{-}1\phantom{.} \\
			\phantom{.}1 & \phantom{-}0\phantom{.}
		\end{pmatrix}, -\overline{\begin{pmatrix}
				\phantom{.}0 & \phantom{-}1\phantom{.} \\
				\phantom{.}1 & \phantom{-}0\phantom{.}
			\end{pmatrix}}\right) = (\bar 0, \bar 3),    \\
		% -- 4th row --
		\deg \left(\begin{pmatrix}
			\phantom{.}0 & -1\phantom{.}           \\
			\phantom{.}1 & \phantom{-}0\phantom{.}
		\end{pmatrix}, \overline{\begin{pmatrix}
				\phantom{.}0 & -1\phantom{.}           \\
				\phantom{.}1 & \phantom{-}0\phantom{.}
			\end{pmatrix}}\right) = (\bar 1, \bar 3),\, &
		\deg \left(\begin{pmatrix}
			\phantom{.}0 & -1\phantom{.}           \\
			\phantom{.}1 & \phantom{-}0\phantom{.}
		\end{pmatrix}, -\overline{\begin{pmatrix}
				\phantom{.}0 & -1\phantom{.}           \\
				\phantom{.}1 & \phantom{-}0\phantom{.}
			\end{pmatrix}}\right) = (\bar 1, \bar 1).
	\end{align*}
	%
	%
	% \setlength\tabcolsep{2pt}
	%  \begin{center}
	%  \begin{tabular}{c c}
	%  % -- 1st row --
	%  $\deg \left(\begin{pmatrix}
	%   \phantom{.}1 & \phantom{-}0\phantom{.}\\
	%   \phantom{.}0 & \phantom{-}1\phantom{.}
	%  \end{pmatrix}, \overline{\begin{pmatrix}
	%   \phantom{.}1 & \phantom{-}0\phantom{.}\\
	%   \phantom{.}0 & \phantom{-}1\phantom{.}
	%  \end{pmatrix}}\right) = (\bar 0, \bar 0),$&
	%  $\deg \left(\begin{pmatrix}
	%   \phantom{.}1 & \phantom{-}0\phantom{.}\\
	%   \phantom{.}0 & \phantom{-}1\phantom{.}
	%  \end{pmatrix}, -\overline{\begin{pmatrix}
	%   \phantom{.}1 & \phantom{-}0\phantom{.}\\
	%   \phantom{.}0 & \phantom{-}1\phantom{.}
	%  \end{pmatrix}}\right) = (\bar 0, \bar 2)$\\
	%  % -- 2nd row --
	%  $\deg \left(\begin{pmatrix}
	%   \phantom{.}1 & \phantom{-}0\phantom{.}\\
	%   \phantom{.}0 & -1\phantom{.}
	%  \end{pmatrix}, \overline{\begin{pmatrix}
	%   \phantom{.}1 & \phantom{-}0\phantom{.}\\
	%   \phantom{.}0 & -1\phantom{.}
	%  \end{pmatrix}}\right) = (\bar 1, \bar 0),$&
	%  $\deg \left(\begin{pmatrix}
	%   \phantom{.}1 & \phantom{-}0\phantom{.}\\
	%   \phantom{.}0 & -1\phantom{.}
	%  \end{pmatrix}, -\overline{\begin{pmatrix}
	%   \phantom{.}1 & \phantom{-}0\phantom{.}\\
	%   \phantom{.}0 & -1\phantom{.}
	%  \end{pmatrix}}\right) = (\bar 1, \bar 2)$\\
	%  % -- 3rd row --
	%  $\deg \left(\begin{pmatrix}
	%   \phantom{.}0 & \phantom{-}1\phantom{.} \\
	%   \phantom{.}1 & \phantom{-}0\phantom{.}
	%  \end{pmatrix}, \overline{\begin{pmatrix}
	%   \phantom{.}0 & \phantom{-}1\phantom{.} \\
	%   \phantom{.}1 & \phantom{-}0\phantom{.}
	%  \end{pmatrix}}\right) = (\bar 0, \bar 1),$&
	%  $\deg \left(\begin{pmatrix}
	%   \phantom{.}0 & \phantom{-}1\phantom{.} \\
	%   \phantom{.}1 & \phantom{-}0\phantom{.}
	%  \end{pmatrix}, -\overline{\begin{pmatrix}
	%   \phantom{.}0 & \phantom{-}1\phantom{.} \\
	%   \phantom{.}1 & \phantom{-}0\phantom{.}
	%  \end{pmatrix}}\right) = (\bar 0, \bar 3)$\\
	%  % -- 4th row --
	%  $\deg \left(\begin{pmatrix}
	%   \phantom{.}0 & -1\phantom{.} \\
	%   \phantom{.}1 & \phantom{-}0\phantom{.}
	%  \end{pmatrix}, \overline{\begin{pmatrix}
	%   \phantom{.}0 & -1\phantom{.} \\
	%   \phantom{.}1 & \phantom{-}0\phantom{.}
	%  \end{pmatrix}}\right) = (\bar 1, \bar 3),$&
	%  $\deg \left(\begin{pmatrix}
	%   \phantom{.}0 & -1\phantom{.} \\
	%   \phantom{.}1 & \phantom{-}0\phantom{.}
	%  \end{pmatrix}, -\overline{\begin{pmatrix}
	%   \phantom{.}0 & -1\phantom{.} \\
	%   \phantom{.}1 & \phantom{-}0\phantom{.}
	%  \end{pmatrix}}\right) = (\bar 1, \bar 1)$
	%  \end{tabular}
	%  \end{center}
	%
	Then $\mc O$ is an odd graded division superalgebra and the exchange superinvolution on it preserves degrees. 
\end{ex}

As we are going to see, $\mc O$ is of special importance among the odd graded division superalgebras with superinvolution of type $M\times M\sop$.

Of course, the construction of $\mc O$ depend on the choice of the involution on $\D$.
By Corollary \ref{cor:old-item-iv}, there are $4$ different graded superalgebras with superinvolution we could end up with if we took different choices.
