\chapter{Generalities on gradings}\label{sec:generalities}

% ** Intro to Chapter



The purpose of this chapter is to introduce the basic notions and constructions involving gradings and also to fix notation and terminology.  
% We will consider $G$ to be fixed group. 

Let $G$ be a group. 
In \cref{sec:graded-bimodules}, we introduce the concepts of homogeneous linear maps, elementary $G$-gradings on matrix (super)algebras, $G$-graded modules, tensor product of $G$-graded vector spaces and (super)algebras, and supercenter of an associative superalgebra.
In \cref{sec:Omega-algebras}, we define universal algebra, so we can handle gradings on different structures (such as algebras, superalgebras and superalgebras with superinvolution) in a uniform manner. 
In \cref{sec:g-hat-action}, under the assumptions that $G$ is abelian, $\FF$ is algebraically closed and $\Char \FF = 0$, we present the duality between $G$-gradings and $\widehat G$-actions for universal algebras. 
This allows us to ``transfer'' $G$-gradings between universal algebras with different signatures (see  \cref{def:universal-algebra,thm:transfer-of-gradings}); we will use this in \cref{chap:Lie} to get a classification of gradings on classical Lie superalgebras from a classification of gradings on associative superinvolution-simple superalgebras. 
% In that section, we will assume that $G$ is abelian, $\FF$ is algebraically closed and $\Char \FF = 0$.
% In \cref{sec:g-hat-action}, we present the duality between $G$-gradings on universal algebras and $\widehat G$-actions by automorphisms (in the case $\FF$ is algebraically closed and $\Char \FF = 0$); the main result (\cref{thm:transfer-of-gradings}) will be used in \cref{chap:Lie} to transfer gradings between universal algebras with different signatures (see \cref{def:universal-algebra}): associative superalgebras with superinvolution and Lie superalgebras. 
Finally, \cref{ssec:universal_group} is devoted to concepts related to refinement, coarsening and fine gradings, where we cannot keep the grading group fixed. 
We introduce set gradings on universal algebras and define equivalence of gradings and universal grading group in this context. 
We warn the reader that some terms appearing in \cref{ssec:universal_group} are not used consistently in the literature (see discussion in \cite[Section 2.7]{GS}); here we follow \cite{livromicha}. 

% The notion of grading is introduced in a very general way, not only for (super)algebras, but also for vector (super)spaces, (super)modules (\cref{sec:graded-bimodules}) and universal algebras (\cref{sec:Omega-algebras}). 
% In \cref{sec:g-hat-action} we discuss the correspondence between gradings and actions, which gives us a tool to transfer gradings between different (universal) algebras. 
% Finally, in \cref{ssec:universal_group}, we discuss the different ways to classify gradings (up to isomorphism or up to equivalence), as well as the concepts of coarsening and refinement of a grading.  


% --------------------






% ** Sections: 
\input{chapters/01_Generalities/01_Grd-Vector-Spaces.tex}

\input{chapters/01_Generalities/02_Omega-Algebras.tex}

\input{chapters/01_Generalities/03_G-hat-Actions.tex}

\input{chapters/01_Generalities/04_Iso-and-Equivalences.tex}

