\chapter{Super-anti-automorphisms on Graded-Simple Associative Superalgebras}\label{chap:super-inv}

% ** Intro of the Chapter

In this and in the next chapter we will study associative graded superalgebras with superinvolution. 
Here we will focus on the graded-simple case, adapting the approach of \cite{Eld10} (see also \cite[Section 2.4]{livromicha}) to superalgebras. 
We also take inspiration from \cite{paper-adrian}, even though we do not use results from there. 
% More specifically, we want to study the gradings making them simple as graded superalgebras with superinvolution. 
% As we are going to see in \cref{grd-sinv-simple}, the hardest case is the focus of this chapter: when the associative superalgebra is simple as a graded superalgebra. 

We start in a very general setting, adding more assumptions as the chapter develops. 
In \cref{ssec:superdual}, we introduce the concept of superdual for graded supermodules over a graded-division superalgebra $\D$ and for $\D$-linear maps between them. 
In \cref{sec:super-anti-auto-and-sesquilinear,sec:iso-vphi-abstract,sec:matrix-super-anti-auto}, we deal with graded-simple superalgebras satisfying \dcc on graded left superideals, over an arbitrary field. 
\Cref{sec:super-anti-auto-and-sesquilinear,sec:iso-vphi-abstract} handle the problem more abstractly: in the former, we describe super-anti-automorphisms in terms of sesquilinear forms (see \cref{def:sesquilinear-form,thm:vphi-iff-vphi0-and-B}) and, in the latter,
we solve the isomorphism problem for graded superalgebras with super-anti-automorphism in terms of this description (see \cref{thm:iso-abstract-vphi,cor:iso-with-actions}). 
In \cref{sec:matrix-super-anti-auto}, we express super-anti-automorphisms in the language of matrices with entries in $\D$ (\cref{prop:matrix-vphi}). 
In \cref{sec:superinv-sesquilinear-forms}, we study necessary and sufficient conditions on the sesquilinear form for the super-anti-automorphism to be involutive, assuming that the homogeneous components of the graded-division superalgebra are 1-dimensional (\cref{thm:vphi-involution-iff-delta-pm-1}). 
% that is satisfied if it is finite dimensional and we are working over an algebraically closed field. 
Finally, \cref{sec:classification-grd-simple-with-sinv} is devoted to classification results (up to isomorphism) assuming the base field is algebraically closed with characteristic different from $2$. 
It is divided into three subsections: \cref{ssec:param-D-vphi} deals with graded-division superalgebras, \cref{ssec:parameters-(U-B)} with graded supermodules with sesquilinear forms and \cref{subsec:param-(R-phi)} with graded-simple superalgebras with superinvolution. 
The main classification result is \cref{thm:iso-(R-vphi)-with-parameters}. 

We will assume the grading group $G$ is abelian throughout this chapter. 
We can do this without loss of generality because of the next result, which is a generalization of \cite[Theorem 1]{BSZ05} (see also \cite[Proposition 2.49]{livromicha} and its proof, which works in this more general situation). 

\begin{prop}\label{prop:grd-simple-vphi-abelian}
    Let $(R, \vphi)$ be an associative $G$-graded superalgebra with super-anti-automorphism. 
    If $R$ does not have nonzero proper graded $\vphi$-invariant superideals, then the subgroup of $G$ generated by the support of $R$ is abelian. \qed 
\end{prop}

% ** Sections:

\input{./chapters/03_Associtive-Grd-Simple-with-Sinv/01_Super-Dual}

\input{./chapters/03_Associtive-Grd-Simple-with-Sinv/02_Sesquilinear}

\input{./chapters/03_Associtive-Grd-Simple-with-Sinv/03_Iso-Grd-Simple}

\input{./chapters/03_Associtive-Grd-Simple-with-Sinv/04_Matrix-Representation}

\input{./chapters/03_Associtive-Grd-Simple-with-Sinv/05_Superinvolutions}

\input{./chapters/03_Associtive-Grd-Simple-with-Sinv/06_Classification}