% \makeatletter
% \def\input@path{{../}}
% \makeatother
% %
% \documentclass[../00_Thesis.tex]{subfiles}
% %
% \overfullrule=2cm
% %
% %
% \begin{document}

%\setcounter{chapter}{3}

\chapter{Super-anti-automorphisms on Graded-simple Associative Superalgebras}\label{chap:super-inv}

The orthosymplectic and the paraplectic Lie superalgebras are defined using a nondegenerate bilinenar form on a superspace. 
More specifically, if $\vphi$ is the superadjunction corresponding to this form, then we consider the subsuperalgebra of the general linear Lie superalgebra consisting of the skew elements with respect to $\vphi$ (see Subsection {\tt ??}). 

\vspace{5mm}
{\tt (More intro to come...)}


{\tt Mention that we are developing the approach of Elduque (J. of \\Al\-ge\-bra 2010, see also Chapter 2 in Monograph) in the super setting.}

\begin{itemize}
    \item Cite Bahturin and Tvaladze; maybe Tvaladze and Tvaladze;
    \item Cite Bahturin and Shestakov;
    \item Also Carlos G\'omes Ambrose ``On the Lie Structure of the Skew Elements of a simple Superalgebra with Superinvolution''
    \item And Racine's paper on superinvolution simple superalgebras.
    \item Maybe Elduques's \cite{elduqueSuperinv};
    \item How what we are doing is different?
    \item Analogous to Lie over $\RR$ (Adri\'an); not literally using results, but using ideas.
\end{itemize}
% For the remainder of the chapter, $G$ is a fixed abelian group.

% In this chapter we are going to describe 

\section{Super-anti-automorphisms and ses\-qui\-li\-near\\ forms}\label{sec:super-anti-auto-and-sesquilinear}

Let $\D$ be a graded division superalgebra and let $\U$ be a nonzero graded right $\D$-supermodule of finite rank. 
Consider the graded superalgebra $R := \End_\D(\mc U)$. 
Then $\mc U$ is an $(R, \D)$-superbimodule. 
By Proposition \ref{prop:converse-density-thm}, $\mc U$ is a simple graded left supermodule over $R$ and we have a natural identification between $\D$ and $\End_R(\mc U)$.

Recall that for a superalgebra $S$, the superalgebra $S\sop$ is defined by $S\sop = S$ as superspaces, but with a different product. For every element $s\in S$, we denote it by $\bar s$ when regarded as an element of $S\sop$, and the product on $S\sop$ is defined by $\bar a \overline {B} = \sign{a}{b} \overline{ba}$ for all $a, b \in S$.
% \begin{notation}
%     Let  be . As sets, we have that $S = S\sop$, but given $s\in S$, we will it by $ \bar s$ when regarded as an element of $S\sop$.
% \end{notation}

As we saw on {\tt Section ??}, $\mc U\Star = \Hom_\D (\mc U, \D)$ is a graded left $\D$-supermodule through $(df)(u) = df(u)$, for all $d\in \D$, $f\in \U\Star$ and $u\in U$. 
We can, then, regard $\U\Star$ as a graded right $\D\sop$-supermodule, through $f \bar d = \sign{f}{d} df$. 
Also, we can make $\mc U\Star$ a graded right $R$-supermodule by defining $(f r) (u) := f(r u)$ for all $f\in \mc U\Star$, $r\in R$ and $u\in \mc U$ (i.e., $f r = f \circ r$, since $R = \End_\D(\mc U)$). 
Hence, we can consider $\mc U\Star$ as a graded left $R\sop$-supermodule via $\bar r f = (-1)^{|r||f|} f r$, % (i.e., $r\cdot f = r\Star (f)$)
and $\mc U\Star$ becomes a $(R\sop, \D\sop)$-superbimodule.

\begin{lemma}\label{lemma:U-star-R-sop}
    The left $R\sop$-supermodule $\mc U\Star$ is graded simple, and the action of $\D\sop$ gives an isomorphism $\D\sop \to \End_{R\sop}(\mc U\Star)$.
\end{lemma}

\begin{proof}
    By definition of superadjoint operator, the above $R\sop$-action corresponds to the representation $\rho\from R\sop \to \End_{\D\sop} (\mc U\Star)$ given by $ \rho(r) = r\Star$, which is an isomorphism since $\U$ is of finite rank. 
    If we use $\rho$ to identify $R\sop$ with $\End_{\D\sop} (\mc U\Star)$, the result follows from Proposition \ref{prop:converse-density-thm}.
\end{proof}

%Note that the $R\sop$-action correspond to the representation $\rho: R\sop \to \End_{\D\sop} (\mc U\Star)$ given by $ \rho(r) = r\Star$, which is an isomorphism. If we use it to identify $R\sop$ with $\End_{\D\sop} (\mc U\Star)$, we can then apply Proposition \ref{prop:converse-density-thm} again and conclude that $\mc U\Star$ is a graded simple left $R\sop$-module and that we naturally can identify $\D\sop$ with $\End_{R\sop}(\mc U\Star)$.

Now let $\vphi: R\to R$ be a super-anti-automorphism that preserves the $G$-degree (\ie, is homogeneous of degree $e$ with respect to the $G$-grading).
We can see it as an isomorphism $R\to R\sop$, $r \mapsto \overline{ \vphi(r)}$, and use it to identify $R$ with $R\sop$. 
In particular, we will make the left $R\sop$-action on $\U\Star$ into a left $R$-action via $r\cdot f = \overline{\vphi(r)}f$, for all $r\in R$ and all $f\in \U\Star$. 
In other words,
%
\begin{equation}\label{eq:R-action-back-on-the-right}
    r\cdot f = \sign{r}{f} f \circ \vphi(r) .
\end{equation}

We will now consider $\U\Star$ as an $(R,\D\sop)$-superbimodule. 
In particular, the superalgebra $\End_R(\U\Star)$ should be understood as the set of $R$-linear maps with respect to the $R$-action on the left (which is the same set as $\End_{R\sop} (\U\Star)$). 
Also, since the action is on the left, we will follow the convention of writing $R$-linear maps on the right.

From Lemma \ref{lemma:U-star-R-sop}, it follows that $\U\Star$ is a simple graded left $R$-supermodule and that we can identify $\D\sop$ with $\End_R (\U\Star) = \End_{R\sop} (\U\Star)$. 
But from Proposition {\tt ??}, $R$ has only one graded simple supermodule up to isomorphism and shift, hence there is an invertible $R$-linear map $\vphi_1: \mc U \to \mc U\Star$ which is homogeneous of some degree $(g_0, \alpha)\in G^\#$. 
Fix one such $\vphi_1$.
% This map is not unique, but we are going to fix one for now. 

\begin{lemma}\label{lemma:nonuniqueness-of-vphi1}
    A map $\vphi_1' : \U \to \U\Star$ is $R$-linear and homogeneous with respect the $G^\#$-grading if, and only if, there is an element $\bar d\in \D\sop = \End_R (\U\Star)$ homogeneous with the respect the $G^\#$-grading such that $ \vphi_1' = \vphi_1 \bar d$, where juxtaposition represents composition of maps written on the right.
\end{lemma}

\begin{proof}
    This follows from the fact that $ \vphi_1\inv \vphi' \in  \D\sop = \End_R(\U\Star)$ if, and only if, $\vphi' \in \Hom_R(\U, \U\Star)$.
\end{proof}

% \begin{proof}
%     Let $\vphi_1'$ be an homogeneous $R$-linear map. Clearly, $\vphi_1\inv \vphi_1' \in \End_R(\U\Star)$ $ = \D\sop$ (note that we are composing functions written on the right). Then $\vphi_1' = \vphi_1 d$, for some homogeneous $d\in \D\sop$, and hence, by the definitions of the right $\D\sop$-action and the left $\D$-action, $\vphi' (u) = \sign{\vphi_1}{d} d\vphi(u)$ for all $u\in \U$. The converse is a direct computation.
% \end{proof}

We will use 
the $R$-linear map 
$\vphi_1$ to construct a super-anti-automorphism $\vphi_0$ on $\D$ and a nondegenerate $\vphi_0$-sesquilinear form $B$ on $\U$. 

\begin{defi}\label{def:sesquilinear-form}
    We say that a map $B\colon \U \times \U \to \D$ is a \emph{sesquilinear form on $\U$} if it is $\FF$-bilinear, $G^\#$-homogeneous if considered as a linear map $\U\tensor \U \to \D$, and there is $\vphi_0\from \D \to \D$ a degree-preserving su\-per\--an\-ti\--auto\-mor\-phism such that, for all $u,v \in \U$ and $d\in \D$,
    %
    \begin{enumerate}[(i)]
        \item $B(u,vd) = B(u,v)d$; \label{enum:linear-on-the-second}
        \item $B(ud, v) = (-1)^ {(|B| + |u|)|d|}\vphi_0(d) B(u, v)$. \label{enum:vphi0-linear-on-the-first}
    \end{enumerate}
    When the super-anti-automorphism $\vphi_0$ is fixed, we say that $B$ is a \emph{$\vphi_0$-sesquilinear form}. 
    The \emph{(left) radical} of $B$ is the set $\rad B \coloneqq \{u\in \U \mid B(u, v) = 0 \text{ for all } v\in \U\}$. We say that the form $B$ is \emph{nondegenerate} if $\rad B = 0$.
\end{defi}



\begin{remark}\label{rmk:B-determines-vphi_0}
    Note that if $B$ is nondegenerate and $\U \neq 0$, then $\vphi_0$ is actually determined by $B$.
\end{remark}

Suppose for now that a degree-preserving su\-per\--an\-ti\--auto\-mor\-phism $\vphi_0: \D \to \D$ is given. 
We can use it to define a right $\D$-action on $\U\Star$ by interpreting it as an isomorphism from $\D$ to $\D\sop$ and putting 
%
\begin{equation}\label{eq:right-D-action}
    f\cdot d \coloneqq f \overline{\vphi_0(d)},
\end{equation}
%
for all $f \in \U\Star$ and $d\in \D$. 
Using this action, we have $\End_\D (\U\Star) = \End_{\D\sop} (\U\Star)$. We also have the following:

\begin{prop}\label{prop:sesquilinear-form-iff-D-linear-map}
    Fix a degree-preserving su\-per\--an\-ti\--auto\-mor\-phism $\vphi_0\from \D \to \D$. 
    The $\vphi_0$-sesquilinear forms $B:\U\times\U \to \D$ are in a one-to-one correspondence with the homogeneous $\D$-linear maps $\theta\from \U \to \U\Star$ via $B \mapsto \theta$ where $\theta(u) \coloneqq B(u, \cdot)$, for all $u \in \U$ or, inversely, $\theta \mapsto B$ where $B(u,v) \coloneqq \theta(u)(v)$, for all $u, v\in \U$. 
    Moreover, $B$ is nondegenerate if, and only if, $\theta$ is an isomorphism.
\end{prop}

\begin{proof}
    Suppose $B$ is given. Condition \eqref{enum:linear-on-the-second} of Definition \ref{def:sesquilinear-form} tells us that $\theta$ defined this way is, indeed, a map from $\U$ to $\U\Star$. 
    Also, it is easy to check that $\theta$ is homogeneous of the same parity and degree as $B$.
    
    Recalling the left $\D$-action on $\U\Star$, condition \eqref{enum:vphi0-linear-on-the-first} tells us that, for all $u\in \U$ and $d\in \D$,
    \[
        \theta (ud) = (-1)^{|d|(|\theta|+|u|)}\vphi_0 (d) \theta (u),
    \]
    which, by the definition of the right $\D\sop$-action on $\U\Star$, is equivalent to $\theta(ud) = \theta(u) \overline{\vphi_0(d)}$, \ie, $\theta$ is, indeed, $\D$-linear considering the left $\D$-action on $\U\Star$ given by Equation \eqref{eq:right-D-action}.
    
    To show that the correspondence is bijective, note that all the considerations above can be reversed when, given $\theta\from \U \to \U\Star$, we define  $B(u, v) \coloneqq \theta(u)(v)$.
    
    The ``moreover'' part follows from the fact that $\rad B = \ker \theta$, so the nondegeneracy of $B$ is equivalent to $\theta$ being injective. But $\U$ and $\U\Star$ have the same (finite) rank over $\D$, so by Proposition {\tt ??}, $\theta$ is injective if, and only if, it is bijective.
\end{proof}

% \begin{lemma}\label{lemma:sesquilinear-form-iff-D-linear-map}
%     Consider $\U\Star$ as a left $\D$-supermodule by using $\vphi_0$ as above. Then there is a bijection between the $\D$-linear maps $\theta\from \U \to \U\Star$ and the $\vphi_0$-sesquilinear forms $B:\U\times\U \to \D$ via $\theta \mapsto B$ where $B(u,v) \coloneqq \theta(u)(v)$. Moreover, $\theta$ is an isomorphism if, and only if, $B$ is nondegenerate.
% \end{lemma}

% Condition \eqref{enum:linear-on-the-second} on the Definition above allows us to use $B$ to define a map $\U \to \U\Star$ by $u \mapsto B(u, \cdot)$. If this is invertible, we say that the form $B$ is \emph{nondegenerate}.

% Note that a degree-preserving super-anti-automorphism $\vphi_0: \D \to \D$ can be seen as an isomorphism between $\D$ and $\D\sop$ and, hence, one can use it to define a right $\D$-action on $\U\Star$ by $v$

Coming back to our map $\vphi_1\from \U \to \U\Star$ and using the identifications $\D = \End_R(\U)$ and $\D\sop = \End_R(\U\Star)$ introduced above, consider the map $\D \to \D\sop$ sending $d \mapsto \sign{d}{\vphi_1}\vphi_1\inv d \,\vphi_1$, where juxtaposition denotes composition of maps on the right. 
It is straightforward to check that this map is an isomorphism and, hence, we can consider it as a super-anti-automorphism $\vphi_0 \from \D \to \D$. 
Then, for all $u\in \U$ and $d\in \D$, we have
%
\begin{equation}\label{eq:sesquilinear-before-B}
    (ud)\vphi_1 = u (d\vphi_1) =  u(\vphi_1\vphi_1\inv d \vphi_1) = \sign{d}{\vphi_1}(u\,\vphi_1 )\vphi_0(d).
\end{equation}

% The map $\vphi_0$ depends on the choice o f $\vphi_1$. Following Lemma \ref{lemma:all-possible-vphi1}, if we had started with $\vphi_1' \coloneqq d \vphi_1$ instead, we would have gotten the map $\vphi_0' \coloneqq \vphi_0 \circ \operatorname{sInt}_d$, where $\operatorname{sInt}_d: \D \to \D$ is defined by $\operatorname{sInt}_d(c) = \sign{d}{c} d\inv c d$.

\begin{defi}\label{def:change-map-to-the-left}
    Let $V$ and $V'$ be left $R$-supermodules and let $\psi: V \to V'$ be an $R$-linear map. We define $\psi^\circ: V \to  V'$ to be the following map, written on the left:
    \[
        \psi^\circ(v) = \sign{\psi}{v} v\psi.
    \]
\end{defi}

For example, using the identification $\D\sop = \End_R (\U\Star)$ as before, the left $\D$-action on $\U\Star$ is given by $df = \bar d^\circ (f)$, for all $d\in \D$ and $f\in \U\Star$.

\begin{lemma}\label{lemma:change-of-side-properties}
    Under the conditions of Definition \ref{def:change-map-to-the-left}, we have that, for all $r\in R$ and $v\in V$,  $\psi^\circ (rv) = \sign{\psi}{v} r \psi^\circ (v)$. 
    Further, given another $R$-linear map $\tau: V' \to V''$, we have $(\psi\tau)^\circ = \sign{\psi}{\tau} \tau^\circ\psi^\circ$. \qed
\end{lemma}

% \begin{remark}
%     The map $\psi^\circ$ defined above is not, in general, $R$-linear. Instead, it satisfies $\psi^\circ (rv) = \sign{\psi}{v} r \psi^\circ (v)$, for all $r\in R$ and $v\in V$. 
%     Also, given another $R$-linear map $\theta: \V' \to \V''$, we have that $(\psi\theta)^\circ = \sign{\psi}{\theta} \theta^\circ\psi^\circ$.


    % Let $\psi: \V \to \V'$ and $\theta: \V' \to \V''$ be $R$-linear maps between left $R$-supermodules. Then
    % \begin{enumerate}[(i)]
    %     \item $\psi^\circ (rv) = \sign{\psi}{v} r \psi^\circ (v)$, for all $r\in R$ and $v\in V$;
    %     \item $(\psi\theta)^\circ = \sign{\psi}{\theta} \theta^\circ\psi^\circ$.
    % \end{enumerate}
% \end{remark}

Using the notation just introduced, we can rewrite Equation \eqref{eq:sesquilinear-before-B} as follows:
%
\begin{equation}\label{eq:vphi1-circ-is-D-linear}
    \begin{split}
        \vphi_1^\circ (ud) &= (-1)^{|\vphi_1|(|u|+|d|)} (ud)\vphi_1 \\
        &=\sign{\vphi_1}{u}(u\,\vphi_1) \overline{\vphi_0(d)} = 
        \vphi_1^\circ (u) \overline{\vphi_0(d)},
    \end{split}
\end{equation}
%
which means, considering the right $\D$-action defined via Equation \eqref{eq:right-D-action},
% We can use $\vphi_0\colon \D \to \D\sop$ to define a right $\D$-module structure on $\U\Star$ via $f\cdot d \coloneqq f\vphi_0(d)$, for all $f\in \U\Star$ and $d\in \D$. 
% Considering this action, Equation \eqref{eq:vphi1-circ-is-D-linear} tells us 
that $\vphi_1^\circ$ is $\D$-linear. (Note, however, that Lemma \ref{lemma:change-of-side-properties} shows that $\vphi_1^\circ$ is not $R$-linear, in general.)


% Also, recalling the definition of the right $\D\sop$-action on $\U\Star$, note that Equation \eqref{eq:vphi1-circ-is-D-linear} can be rewritten using the left $\D$-action as
%
% \begin{equation}\label{eq:sesquilinear-with-vphi1-circ}
%     \vphi_1^\circ (ud) = (-1)^{|d|(|\vphi_1|+|u|)}\vphi_0 (d)\vphi_1^\circ (u).
% \end{equation}


% We define $\vphi_1 := \tilde\vphi_1^\circ$ and $\vphi_0: \D \to \D$ by $\vphi_0(d): \sign{\vphi_1}{d} \vphi_1 d^\circ \vphi_1\inv$. 
% Note that the left $\D$-action on $\U\Star$ is connected the right $\D\sop$-action by the formula $f\cdot d = d^\circ \cdot f$, hence $\vphi_0$ is an anti-super-automorphism of $\D$. Also, we have that $\vphi_1(ud) = \sign{u}{d} \vphi_1(d^\circ  $

% \begin{lemma}
%     Let $B: \U\times \U\Star$ be a nondegenerate $\vphi_0$-sesquilinear map. Then, given $r\in R$, there is a unique $s\in R$ such that \[
%         B(ru,v) = \sign{r}{u} B(u,sv).
%     \]
%     Further, the map $r\mapsto s$ is a super-anti-automorphism of $R$.
% \end{lemma}

% \begin{proof}
%     Consider $\theta: \U \to \U\Star$ as in Lemma \ref{lemma:sesquilinear-form-iff-D-linear-map}. 
%     We then have that
%     \begin{align*}
%         \theta(ru)(v) &= \sign{r}{u} \theta(u)(sv)\\
%         \theta (ru)(v) &= \sign{r}{u} (\theta (u)\circ s)(v)\\
%         \theta (ru) &= \sign{r}{u} \theta(u) \circ s\\
%         (\theta \circ r) (u) &= (-1)^{(|\theta| + |u|)|s|} s\Star (
%     \end{align*}
% \end{proof}

Now we define $B: \U\times \U \to \D$ by $B(u, v) = \vphi_1^\circ (u)(v)$. 
By Proposition \ref{prop:sesquilinear-form-iff-D-linear-map}, we have that $B$ is a nondegenerate $\vphi_0$-sesquilinear map. 
Using Lemma \ref{lemma:change-of-side-properties} and Equation \eqref{eq:R-action-back-on-the-right}, we have
%
\begin{equation*}
    \begin{split}
        B(ru,v) &= \vphi_1^\circ (ru)(v) = \sign{r}{\vphi_1} \big(r \cdot \vphi_1^\circ (u) \big) (v)\\ &= \sign{r}{\vphi_1} (-1)^{|r|(|\vphi_1| + |u|)} \big(\vphi_1^\circ (u) \circ \vphi(r) \big)(v) \\ &= \sign{r}{u} \vphi_1^\circ (u) \big( \vphi(r)v \big)= \sign{r}{u} B(u,\vphi(r)v).
    \end{split}
\end{equation*}
%\ie, we have that $\vphi$ is the \emph{superadjunction} with respect to $B$.
We have proved one direction of Theorem \ref{thm:vphi-iff-vphi0-and-B}, below. 

% \begin{lemma}\label{lemma:superadjoint}
%     Let $B$ be a nondegenerate $\vphi_0$-sesquilinear form on a graded right $\D$-module $\U$ and set $R \coloneqq \End_\D (\U)$. 
%     For each homogeneous $\D$-linear map $r\in \End_\D(\U)$, there is a unique homogeneous $\D$-linear map $\vphi(r) \in \End_\D(\U)$ such that
%     \begin{equation}\label{eq:superadjunction}
%         \forall r\in R\even \cup R\odd,\,\forall u, v \in \U\even \cup \U\odd,  \quad B(ru,v) = \sign{r}{u} B(u,\vphi(r)v).
%     \end{equation}
%     Further, extending $\vphi$ by linearity to all elements in $End_\D(\U)$, we have a super-anti-automorphism $\vphi\from \End_\D(\U) \to \End_\D(\U)$.
% \end{lemma}

% \begin{prop}
%     Let $\vphi_0\from \D \to \D$ be a super-anti-automorphism and let $B\from \U\times \U \to \D$ be a nonzero $\vphi_0$-sesquilinear form. 
%     We have that $B$ is nondegenerate if, and only if, there is a unique super-anti-automorphism $\vphi\from R \to R$ such that
%     %
%     \begin{equation}\label{eq:superadjunction}
%         \forall u, v \in \U, \forall r\in R, \quad B(ru,v) = \sign{r}{u} B(u,\vphi(r)v).
%     \end{equation}
%     %
%     Moreover, if $ $
% \end{prop}

To state the theorem, it is convenient to introduce the following notation. 
Recall that, any invertible element $d\in \D$ gives rise to the inner automorphism $\operatorname{Int}_d\from \D \to \D$ defined by $\operatorname{Int}_d (c) \coloneqq dcd\inv$, for all $c\in \D$. 
If we require $d$ to be homogeneous with respect to the $G^\#$-grading, then $\operatorname{Int}_d$ is an automorphism of $\D$ as a graded superalgebra (Definition \ref{def:inner-automorphism}).

\begin{defi}
    Let $d\in \D$ be a nonzero $G^\#$-homogeneous element. 
    We define the \emph{superinner automorphism} $\operatorname{sInt}_d\from \D \to \D$ by $\operatorname{sInt}_d (c) \coloneqq \sign{c}{d} dcd\inv$, for all $c\in \D$.
\end{defi}

% Considered as a $\FF$-linear map $B: \U\tensor \U \to \D$, it is homogeneous of same parity and degree of $\vphi_1$. It is $\vphi_0$-sesquilinear: since $\vphi_1^\circ (u) \in \U\Star$, we have that $\vphi_1^\circ(u)(vd) = \vphi_1^\circ(u)(v)d$, which give us condition \eqref{enum:linear-on-the-second} of Definition \ref{def:sesquilinear-form};
% condition \eqref{enum:vphi0-linear-on-the-first} is a restatement of \eqref{eq:sesquilinear-with-vphi1-circ}. It is nondegenerate since $\rad B = \ker \vphi_1^\circ$, and $\vphi_1^\circ$ is a bijective $\D$-linear map.



% \begin{lemma}
%     Let $\vphi_0\colon \D\to \D$ be a fixed degree-preserving su\-per\--an\-ti\--auto\-mor\-phism. 
%     Given re is a bijective correspondence between the $\vphi_0$-sesquilinear maps $B$ is in bijection with the set of homogeneous maps $\theta\colon \U \to \U\Star$ such that $\theta (ud) = \theta(u) \vphi_0(d)$.
% \end{lemma}

% \begin{proof}
%     Let $B\colon \U \times \U \to \D$ be a $\vphi_0$-sesquilinear form. Define $\theta(u)  \coloneqq B(u, \cdot)$. By condition \eqref{enum:linear-on-the-second} in Definition \ref{def:sesquilinear-form}, the map $\theta (u) \in \U\Star$ for all $u\in \U$. Note that $\theta$ have the same degree and parity of $B$. Hence, the condition \eqref{enum:vphi0-linear-on-the-first} tells us that $\theta(ud) = (-1)^ {(|\theta| + |u|)|d|} \vphi_0(d) \theta(u)$, which, by the Definition of the right $\D\sop$-action on $\U\Star$, becomes $\theta(ud) = \theta (u) \vphi_0 (d)$. 
% \end{proof}

% In particular, we can recover $\vphi$ from the pair $(\vphi_0, B)$.



% One should note that the $\vphi_0: \D \to \D\sop$ give $\U\Star$ a right $\D$-module structure by defining $f\cdot d = f\vphi_0(d)$, for all $f\in \U\Star$ and $d\in \D$. In this sense, from

% Clearly, the $\vphi_0$-sesquilinear form $B$ is \emph{nondegenerate} in the sense that the map $\U \to \U\Star$ given by $u \mapsto B(u, \cdot)$ is an isomorphism of right $\D$-modules. 

% \begin{thm}\label{thm:vphi-iff-vphi0-and-B}
%     Let $\D$ be a graded division superalgebra and let $\U$ be a nonzero right graded module of finite rank over $\D$. 
%     If $\vphi$ is degree-preserving super-anti-automorphism on $R \coloneqq \End_\D(\U)$, then there is a pair $(\vphi_0, B)$, where $\vphi_0$ is a degree-preserving super-anti-automorphism on $\D$ and $B\from \U \times \U \to \D$ is a nondegenerate $\vphi_0$-sesquilinear form, such that
%     %
%     \begin{equation}\label{eq:superadjunction}
%         \forall r\in R\even \cup R\odd,\,\forall u, v \in \U\even \cup \U\odd,  \quad B(ru,v) = \sign{r}{u} B(u,\vphi(r)v).
%     \end{equation}
%     %
%     Conversely, given a pair $(\vphi_0, B)$ as above, there is a unique degree-preserving super-anti-automorphism $\vphi$ on $R$ satisfying Equation \eqref{eq:superadjunction}. 
%     Moreover, another pair $(\vphi_0', B')$ determines the same super-anti-automorphism $\vphi$ if, and only if, there is a nonzero $G^\#$-homogeneous element $d\in \D$ such that $\vphi_0' = \mathrm{sInt}_d \circ \vphi_0$ and $B'(u, v) = dB (u, v)$ for all $u, v \in \U$.
% \end{thm}

\begin{thm}\label{thm:vphi-iff-vphi0-and-B}
    Let $\D$ be a graded division superalgebra and let $\U$ be a nonzero right graded module of finite rank over $\D$. 
    If $\vphi$ is degree-preserving super-anti-automorphism on $R \coloneqq \End_\D(\U)$, then there is a pair $(\vphi_0, B)$, where $\vphi_0$ is a degree-preserving super-anti-automorphism on $\D$ and $B\from \U \times \U \to \D$ is a nondegenerate $\vphi_0$-sesquilinear form, such that
    %
    \begin{equation}\label{eq:superadjunction}
        \forall r\in R\even \cup R\odd,\,\forall u, v \in \U\even \cup \U\odd,  \quad B(ru,v) = \sign{r}{u} B(u,\vphi(r)v).
    \end{equation}
    %
    Conversely, given a pair $(\vphi_0, B)$ as above, there is a unique degree-preserving super-anti-automorphism $\vphi$ on $R$ satisfying Equation \eqref{eq:superadjunction}. 
    Moreover, another pair $(\vphi_0', B')$ determines the same super-anti-automorphism $\vphi$ if, and only if, there is a nonzero $G^\#$-homogeneous element $d\in \D$ such that $B'(u, v) = dB (u, v)$ for all $u, v \in \U$, and, hence, $\vphi_0' = \mathrm{sInt}_d \circ \vphi_0$.
\end{thm}

\begin{proof}
    The first assertion is already proved. For the converse, let $\vphi_0$ be a degree-preserving super-anti-automorphism on $\D$, let $B\from \U \times \U \to \D$ be a nondegenerate $\vphi_0$-sesquilinear form and consider $\theta$ as in 
    Proposition \ref{prop:sesquilinear-form-iff-D-linear-map}. Then Equation \eqref{eq:superadjunction} is equivalent to:
    %
    \begin{alignat*}{2}
        \forall r\in R\even \cup R\odd,\,\forall u, v &\in \U\even \cup \U\odd,& \theta (ru)(v)&= \sign{r}{u} \theta(u)(\vphi(r)v)\\
        &&&= \sign{r}{u} \big(\theta (u)\circ \vphi(r)\big)(v)\\
        %
        \intertext{and, hence, equivalent to}
        %
        \forall r\in R\even \cup R\odd,\,&\forall u \in \U\even \cup  \U\odd,&   \theta (ru) &= \sign{r}{u} \theta(u) \circ \vphi(r).
        %
        \addtocounter{equation}{1}\tag{\theequation}\label{eq:theta-is-almost-R-superlinear}\\
        %
        \intertext{Recalling the definition of superadjoint operator, Equation \eqref{eq:theta-is-almost-R-superlinear} becomes}
        %
        \forall r\in R\even \cup R\odd,\,\forall u &\in \U\even \cup \U\odd, & (\theta \circ r) (u) &= \sign{r}{u} (-1)^{(|\theta| + |u|)|r|} \big(\vphi(r)\big)\Star \big(\theta(u)\big) \\
        &&&=  \sign{r}{\theta} \big(\big(\vphi(r)\big)\Star \circ \theta \big) (u),
        %
        \intertext{which is the same as}
        %
        \forall r&\in R\even \cup R\odd, &\theta \circ r &= \sign{r}{\theta}  \big(\vphi(r)\big)\Star \circ \theta.
        \intertext{In other words, we have}
        \forall r&\in R\even \cup R\odd, & \big(\vphi(r)\big)\Star &= \sign{r}{\theta}\, \theta \circ r \circ \theta\inv.
        %
        \addtocounter{equation}{1}\tag{\theequation}\label{eq:vphi-r-Star-is-a-superconjugation}
    \end{alignat*}
    %
    % We have shown that
    % %
    % \begin{equation}
    %   \big(\vphi(r)\big)\Star = \sign{r}{\theta}\, \theta \circ r \circ \theta\inv.
    % \end{equation}
    %
    Since $\U$ has finite rank over $\D$, the superadjunction map $\End_\D (\U) \to \End_{\D\sop} (\U\Star)$ is invertible and, hence, $\vphi$ is uniquely determined.
    Also, the properties of superadjunction imply that $\vphi$ is, indeed, a super-anti-automorphism of $R$.
    
    For the ``moreover'' part, let $d$ be a nonzero $G^\#$-homogeneous element of $\D$ and consider $\vphi_0' = \operatorname{sInt}_d \circ \, \vphi_0$ and $B' = dB$. 
    We have that $B'$ is $\vphi_0'$-sesquilinear since, for all $c\in \D\even \cup \D\odd$ and $u,v \in \U\even \cup \U\odd$,
    %
    \begin{align*}
        B' (uc, v) &= dB (uc, v) = (-1)^{(|B| + |u| ) |c|} d\vphi_0(c) B(u,v) \addtocounter{equation}{1}\tag{\theequation}\label{eq:dB-is-sesquilinear}\\
        &= (-1)^{(|B| + |u| ) |c|} d\vphi_0(c) d\inv d B(u,v) \\
        &=  (-1)^{(|B| + |u| ) |c|} \sign{c}{d} (\operatorname{sInt}_d \circ\, \vphi_0) (c)\, dB(u,v)\\
        &= (-1)^{(|B'| + |u|) |c|} (\operatorname{sInt}_d \circ\, \vphi_0) (c)\, B'(u,v).
    \end{align*}
    %
    To show $B'$ that is nondegenerate, note that $dB(u,v) = 0$ implies $B(u,v) =0$, hence  $\rad B' \subseteq \rad B$. 
    Finally, it is straightforward that Equation \eqref{eq:superadjunction} is still true if we replace $B$ by $B'$. 
    
    %and let $\vphi_0'$ be a super-anti-automorphism on $\D$. 
    % we will first check that $B'$ is, indeed, $\vphi_0'$-sesquilinear.
    
    To prove the other direction, we consider, again, the left $R$-supermodule structure on $\U\Star$ given by Equation \eqref{eq:R-action-back-on-the-right} and let $\theta\from \U \to \U\Star$ be as above, \ie, $\theta(u) = B(u, \cdot)$. Similarly, let $\theta'\from \U \to \U\Star$ be defined by $\theta' \coloneqq B'(u, \cdot)$.
    
    Combining Equations \eqref{eq:R-action-back-on-the-right} and  \eqref{eq:theta-is-almost-R-superlinear}, we have that
    %
    \begin{equation}\label{eq:theta-is-R-superlinear}
        \theta(ru) = \sign{\theta}{r} r\cdot \theta(u).
    \end{equation}
    %
    Define the map $\tilde \theta\from \U \to \U\Star$, written on the right, by $u\, \tilde\theta = \sign{u}{\theta} \theta(u)$, for all $u\in \U$ (compare with Definition \ref{def:change-map-to-the-left} and note that $\theta = (\tilde \theta)^\circ$). 
    Then Equation \eqref{eq:theta-is-R-superlinear} becomes $(ru)\tilde\theta = r \cdot (u\,\tilde\theta)$, \ie, $\tilde\theta$ is $R$-linear.
    
    % Now, given a pair $(\vphi_0', B')$, we have the corresponding map $\theta'(u) \coloneqq B'(u, \cdot)$, for all $u\in \U$. 
    All these considerations about $\theta$ are also valid for $\theta'$, so we define $\tilde\theta'\from \U \to \U\Star$ by $u\,\tilde\theta' \coloneqq \sign{u}{\theta'} \theta'(u)$ and we get another $R$-linear map from $\U$ to $\U\Star$.
    By Lemma~\ref{lemma:nonuniqueness-of-vphi1}, there is $\bar d\in \D\sop$ such that $\tilde\theta' = \tilde\theta \bar d$.
    Applying Lemma \ref{lemma:change-of-side-properties}, this implies \[\theta' = \sign{\theta}{\bar d} \bar d^\circ \theta.\]
    But $\bar d^\circ \theta (u) = d\theta(u)$, where in the last term we use the left $\D$-action on $\U\Star$. 
    Therefore $B'(u,v) = \theta'(u)(v) = d\theta(u)(v) = \sign{\theta}{d} dB(u, v)$, for all $u,v \in \U$. 
    Replacing $d$ by $\sign{\theta}{d} d$, we get $B' = dB$. 
    
    It remains to check that $\vphi_0' = \operatorname{sInt}_d \circ\, \vphi_0$. 
    Since $B' = dB$, Equation \eqref{eq:dB-is-sesquilinear} is valid, hence $B'$ is $(\operatorname{sInt}_d \circ \vphi_0)$-sesquilinenar.
    We then have, for all $c\in \D\even \cup \D\odd$ and $u,v \in \U\even \cup \U\odd$,
    \[
        \vphi_0'(c)\, B'(u,v) = (-1)^{(|B'| + |u|) |c|} B'(uc,v) = (\operatorname{sInt_d} \circ\, \vphi_0) (c)\, B'(u,v).
    \]
    The form $B'$ is nondegenerate, so we can choose $G^\#$-homogeneous $u,v\in \U$ with $B'(u,v)\neq 0$. Then $B'(u,v)$ is invertible, hence $\vphi_0' (c) = (\operatorname{sInt}_d \circ\, \vphi_0) (c)$, concluding the proof.
\end{proof}

The "conversely" part of Theorem \ref{thm:vphi-iff-vphi0-and-B} motivates the following:

\begin{defi}\label{def:superadjunction}
    Let $\D$ be a graded-division superalgebra, $\U$ a graded right $\D$-module of finite rank and $B$ a nondegenerate sesquilinear form on $\U$. 
    The unique super-anti-automorphism $\vphi$ on $\End_\D(\U)$ defined by Equation \eqref{eq:superadjunction} is called the \emph{superadjunction with respect to $B$} and, for every $r\in \End_\D(\U)$, the $\D$-linear map $\vphi(r)$ is called the \emph{superadjoint of $r$}.
    % Under the conditions of Lemma \ref{lemma:superadjoint}, the $\D$-linear map $\vphi(r)$ is called the \emph{superadjoint of $r$}, for every $r\in R$, and the super-anti-automorphism $\vphi \from R \to R$ is called the \emph{superadjunction with respect to $B$}.
\end{defi}

\begin{remark}\label{conv:pick-even-form}
    Under the conditions of Theorem \ref{thm:vphi-iff-vphi0-and-B}, if $\D$ is an odd graded division superalgebra (\ie, $\D\odd \neq 0$), then we can choose the form $B$ to be even. 
    This is possible since, by the ``moreover'' part, we can substitute an odd form $B$ by $dB$, for some $d\in \D\odd$.
\end{remark}

\section{Isomorphism of graded-simple superalgebras\\ with super-anti-automorphism}\label{sec:iso-vphi-abstract}

In this section, we are going to describe isomorphisms between $G$-graded superalgebras with super-anti-automorphism that are graded-simple and satisfy d.c.c on graded left ideals. 
As we have seen, such superalgebras are, up to isomorphism, of the form $\End_\D (\U)$ where the super-anti-automorphism is given by the superadjunction with respect to a nondegenerate sesquilinear form $B\from \U \times \U \to \D$.

Even though, as superalgebras, $\End_\D( \U )$ is the same as $\End_\D( \U^{[g]} )$ for every $g \in G^\#$, an extra care should be taken when considering super-anti-automorphisms. 
If $g\in G^\#$ is odd, a $\vphi_0$-sesquilinear form $B$ on the $\D$-module $\U$ is not $\vphi_0$-sesquilinear if considered on the $\D$-module $\U^{[g]}$, and Equation \eqref{eq:superadjunction} does not determine the same super-anti-automorphism $\vphi$. 
This motivates the following:

\begin{defi}
    Let $\U$ be a graded right $\D$-module and $\vphi_0\from \D \to \D$ be a super-anti-automorphism. 
    Given a homogeneous $\vphi_0$-sesquilinear form $B$ on $\U$ and $g\in G^\#$, we define the $\vphi_0$-sesquilinear form  $B^{[g]}$ on $\U^{[g]}$ by $B^{[g]}(u,v) \coloneqq \sign{u}{g} B(u,v)$, for all $u,v \in \U$. 
\end{defi}

\begin{remark}\label{rmk:deg-B^[g]}
    Note that $\deg B^{[g]} = g^{-2} \deg B$ and, in particular, $|B^{[g]}| = |B|$.
\end{remark}

\begin{lemma}\label{lemma:B^[b]-does-the-job}
    % Let $\U$ be a graded $\D$-module, $\vphi_0$ be a super-anti-automorphism on $\D$ and $B$ be a $\vphi_0$-sesquilinear form on $\U$. 
    For every $g\in G^\#$, $B^{[g]}$ is a homogeneous $\vphi_0$-sesquilinear form on $\U^{[g]}$. 
    Further, if $B$ is nondegenerate and the pair $(\vphi_0, B)$ determines the super-anti-automorphism $\vphi$ on $R \coloneqq \End_\D(\U) = \End_\D(\U^{[g]})$, then $B^{[g]}$ is nondegenerate and $(\vphi_0, B^{[g]})$ also determines $\vphi$.
\end{lemma}

\begin{proof}
    Let $u, v \in \U$. 
    To avoid confusion, we will denote $u$ and $v$ by $u^{[g]}$ and $v^{[g]}$, respectively, when regarded as elements of $\U^{[g]}$. 
    For all $d\in D$, we have:
    \begin{align*}
        B^{[g]}(u^{[g]}, v^{[g]}d) &= \sign{g}{u} B(u, vd) = \sign{g}{u} B(u, v)d =  B^{[g]}(u^{[g]}, v^{[g]})d
        \intertext{and}
        B^{[g]}(u^{[g]}d, v^{[g]}) &= \sign{g}{ud} B(ud, v) = (-1)^{|g|( |u| + |d| )} (-1)^{|d|( |B| + |u| )} \vphi_0(d) B(u, v)\\
        &= (-1)^{|d| ( |B| + |u| + |g| )} \vphi_0(d) \sign{g}{u} B(u, v) \\ 
        &= (-1)^{|d| ( |B| + |u^{[g]}| )} \vphi_0(d) B^{[g]}(u^{[g]}, v^{[g]})d .
        \intertext{Also, for all $r\in R$, we have:}
        B^{[g]}(ru^{[g]}, v^{[g]}) &= \sign{g}{ru} B(ru, v) = (-1)^{|g|( |r| + |u| )} (-1)^{|r||u|} B(u, \vphi(r) v)\\
        &= (-1)^{|r| ( |g| + |u|)} \sign{u}{g} B(u, \vphi(r) v)\\ 
        &= \sign{r}{u^{[g]}} B^{[g]}(u, \vphi(r) v).
    \end{align*}
\end{proof}

Recall the concept of a module induced by a homomorphism of algebras (Definition \ref{def:twist}).

\begin{lemma}\label{lemma:twist-on-(U,B)}
    Let $(\D, \vphi_0)$ and $(\D', \vphi_0')$ be graded-division superalgebras with super-anti-automorphisms and let $\psi_0 \from (\D, \vphi_0) \to (\D', \vphi_0')$ be an isomorphism. 
    If $\U'$ is a $\D'$-supermodule and $B'$ is a homogeneous $\vphi_0'$-sesquilinear form on it, then $\psi_0\inv \circ B'$ is a homogeneous $\vphi_0$-sesquilinear form on $(\U')^{\psi_0}$. \qed
\end{lemma}

\begin{defi}\label{def:iso-(U,B)}
    Let $\U$ and $\U'$ be graded right $\D$-supermodules, and let $B$ and $B'$ be homogeneous sesquilinear forms on $\U$ and $\U'$, respectively. 
    A \emph{isomorphism from $(\U, B)$ to $(\U', B')$} is an isomorphism of graded modules $\theta\from \U \to \U'$ such that $B'( \theta(u), \theta(v) ) = B(u, v)$, for all $u,v \in \U$.
\end{defi}

Note that if $(\U, B)$ and $(\U', B')$ are isomorphic, then $B$ and $B'$ have the same degree in $G^\#$ and are sesquilinear with respect to the same $\vphi_0$. 

% \begin{remark}
%     odd iso and $B^{[g]}$
% \end{remark}

\begin{thm}\label{thm:iso-abstract-vphi}
    Let $R \coloneqq \End_\D(\U)$ and $R' \coloneqq \End_{\D'}(\U')$, where $\D$ and $\D'$ are graded division superalgebras, and $\U$ and $\U'$ are nonzero right graded supermodules of finite rank over $\D$ and $\D'$, respectively. 
    Let $\vphi$ and $\vphi'$ be degree preserving super-anti-automorphisms on $R$ and $R'$ determined, as in Theorem \ref{thm:vphi-iff-vphi0-and-B}, by pairs $(\vphi_0, B)$ and $(\vphi_0', B')$, respectively. 
    If $\psi\from (R, \vphi) \to (R', \vphi')$ is an isomorphism, then there are $g\in G^\#$, a homogeneous element $0\neq d\in \D$, an isomorphism $\psi_0\from \D \to \D'$, and an isomorphism
    \begin{equation}\label{eq:iso-B-implies-vphi}
        \psi_1 \from (\U^{[g]}, dB^{[g]}) \to ( (\U')^{\psi_0}, \psi_0\inv \circ B' ) 
    \end{equation}
    such that 
    \begin{equation}\label{eq:iso-super-anti-auto}
        \forall r\in R, \quad \psi(r) = \psi_1 \circ r \circ \psi_1\inv.
    \end{equation}
    % $\psi(r) = \psi_1 \circ r \circ \psi_1\inv$, for all $r\in R$. 
    Conversely, for any $g$, $d$, $\psi_0$ and $\psi_1$ as above, 
    % the formula $\psi(r) \coloneqq \psi_1 \circ r \circ \psi_1\inv$ 
    Equation \eqref{eq:iso-super-anti-auto}
    defines an isomorphism $\psi \from (R, \vphi) \to (R', \vphi')$.
\end{thm}

\begin{proof}
    Given an isomorphism of graded superalgebras $\psi\from R \to R'$, define $\vphi'' \coloneqq \psi\inv \circ \vphi' \circ \psi$. 
    Then $\psi$ is an isomorphism $(R, \vphi) \to (R', \vphi')$ if, and only if, $\vphi = \vphi''$. 

    Since $\psi$ is an isomorphism of $G^\#$-graded algebras, we can apply Theorem \ref{thm:iso-abstract} to conclude that there are $g\in G^\#$, an isomorphism of graded superalgebras $\psi_0\from \D \to \D'$, and an isomorphism of graded modules $\psi_1\from \U^{[g]} \to (\U')^{\psi_0}$ such that $\psi(r) = \psi_1 \circ r \circ \psi_1\inv$, for all $r\in R$. 
    
    Consider $\vphi_0'' \coloneqq \psi_0\inv \circ \vphi_0' \circ \psi_0$ and $B''\from \U^{[g]} \times \U^{[g]} \to \D$ defined by \[ B''(u, v) \coloneqq \psi_0\inv \Big( B' \big( \psi_1(u), \psi_1(v) \big) \Big)\] for all $u, v \in \U^{[g]}$. 
    We claim that $B''$ is $\vphi_0''$-sesquilinear. 
    Indeed,
    \begin{align*}
        B''(u, vd) &= \psi_0\inv \Big( B'\big( \psi_1(u), \psi_1(vd) \big) \Big) 
        = \psi_0\inv \Big( B'\big( \psi_1(u), \psi_1(v) \big) \psi_0(d) \Big) = B''(u, v)d
        \intertext{and}
        B''(ud, v) &= \psi_0\inv \Big( B' \big( \psi_1(ud), \psi_1(v) \big) \Big) = \psi_0\inv \Big( B' \big( \psi_1(u) \psi_0(d), \psi_1(v) \big) \Big)\\
        &= \psi_0\inv \Big( (-1)^{(|B'| + |u|) |d|} \vphi_0' \big( \psi_0(d) \big) B' \big( \psi_1(u), \psi_1(v) \big) \Big) \\
        &= (-1)^{(|B''| + |u|) |d|} \psi_0\inv \Big( \vphi_0' \big( \psi_0 (d) \big) \Big) B''(u, v)\\
        &= (-1)^{(|B''| + |u|) |d|} \vphi_0''(d) B''(u, v).
        \intertext{Also, $\vphi''$ is the superadjunction with respect to $B''$:}
        % \end{align*}
        % Also, $\vphi''$ is the superadjunction with respect to $B''$:
        % \begin{align*}
        B''(ru, v) &= \psi_0\inv \Big( B' \big( \psi_1(ru), \psi_1(v) \big) \Big) 
        = \psi_0\inv \Big( B' \big( (\psi_1 \circ r \circ \psi_1\inv) \psi_1(u), \psi_1(v) \big) \Big) \\
        &= \psi_0\inv \Big( B' \big( \psi(r) \psi_1(u), \psi_1(v) \big) \Big) \\
        &= \psi_0\inv \Big( \sign{\psi(r)}{\psi_1(u)} B' \big( \psi_1(u), \vphi'( \psi(r) ) \psi_1(v) \big) \Big) \\
        % &= \sign{r}{u} \psi_0 \inv \Big( B' \big( \psi_1(u), (\vphi'\circ \psi)(r)\psi_1(v) \big) \Big)\\
        % &= \sign{r}{u} \psi_0\inv \Big( B' \big( \psi_1(u), (\psi\circ \vphi'')(r) \psi_1(v) \big) \Big)\\
        &= \sign{r}{u} \psi_0\inv \Big( B' \big( \psi_1(u), \psi (\vphi''(r)) \psi_1(v) \big) \Big)\\
        &= \sign{r}{u} \psi_0\inv \Big( B' \big( \psi_1(u), (\psi_1 \circ \vphi''(r) \circ \psi_1\inv) \psi_1(v) \big) \Big)\\
        &= \sign{r}{u} \psi_0\inv \Big( B' \big( \psi_1(u), \psi_1 (\vphi''(r) v) \big) \Big)\\
        &= \sign{r}{u} B'' \big( u, \vphi''(r) v\big).
    \end{align*}
    Hence, applying Theorem \ref{thm:vphi-iff-vphi0-and-B} for $\U^{[g]}$ and Lemma \ref{lemma:B^[b]-does-the-job}, we conclude that $\vphi = \vphi''$ if, and only if, there is a homogeneous $0 \neq d \in \D$ such that $B'' = dB^{[g]}$. 
    The result follows. 
\end{proof}

We can interpret Theorem \ref{thm:iso-abstract-vphi} in terms of group actions. 
For that, let us first assume that $\D$ is a fixed graded-division superalgebra. 
We will define three (left) group actions on the class of pairs $(\U, B)$, where $\U \neq 0$ is a graded $\D$-supermodule and $B$ is a nondegenerate homogeneous $\vphi_0$-sesquilinear form, for some super-anti-automorphism $\vphi_0$ on $\D$. 
Recall that, since $\U \neq 0$ and $B$ is nondegenerate, $\vphi_0$ is determined by $B$ (see Remark \ref{rmk:B-determines-vphi_0}).

Let $\D^\times_{\mathrm{gr}} \coloneqq \big( \cup_{g \in G^\#} \D_g \big)\backslash \{ 0 \}$, the group of nonzero homogeneous elements of $\D$. 
Given $d\in \D^\times_{\mathrm{gr}}$, we define 
\begin{equation}\label{eq:Dx_gr-action}
    d\cdot (\U, B) \coloneqq (\U, dB).
\end{equation}
Note that $dB$ is $(\mathrm{sInt}_d \circ \vphi_0)$-sesquilinear by Theorem \ref{thm:vphi-iff-vphi0-and-B}.

Let $A \coloneqq \Aut (\D)$, the group of automorphisms of $\D$ as a graded superalgebra. 
Given $\psi_0 \in A$, we define
\begin{equation}\label{eq:Aut(D)-action}
    \psi_0 \cdot (\U, B) \coloneqq (\U^{\psi_0\inv}, \psi_0 \circ B).
\end{equation}
Note that $\psi_0 \circ B$ is $(\psi_0 \circ \vphi_0 \circ \psi_0\inv)$-sesquilinear by Lemma \ref{lemma:twist-on-(U,B)}.

Finally, consider the group $G^\#$. 
Given $g \in G^\#$, we define
\begin{equation}\label{eq:G-action}
    g \cdot (\U, B) \coloneqq (\U^{[g]}, B^{[g]}).
\end{equation}
Note that $B^{[g]}$ is $\vphi_0$-sesquilinear by Lemma \ref{lemma:B^[b]-does-the-job}.

\begin{lemma}\label{lemma:action-on-(U,B)}
    The three actions defined above give rise to a $(\D^\times_{\mathrm{gr}} \rtimes A) \times G^\#$-action, where $A$ acts on $\D^\times_{\mathrm{gr}}$ by evaluation. 
\end{lemma}

\begin{proof}
    Let $d\in \D^\times_{\mathrm{gr}}$, $\psi_0 \in A$, $g \in G^\#$ and $u, v \in \U$. 
    First note that the action of $d$ does not change $\U$, so we only have to consider its effect on $B$. 
    Since 
    \begin{align*}
        (\psi_0 \circ dB)(u,v) &= \psi_0 \big( (d B(u,v) \big) = \psi_0 (d) \psi_0 \big( B(u,v) \big) = \big( \psi_0(d) (\psi_0 \circ B) \big) (u,v),
    \end{align*}
    the $\D^\times_{\mathrm{gr}}$-action combined with the $A$-action gives us a $(\D^\times_{\mathrm{gr}} \rtimes A)$-action. 
    The $G^\#$-action commutes with the $\D^\times_{\mathrm{gr}}$-action since 
    \begin{align*}
        (dB)^{[g]} (u, v) = \sign{g}{u} dB(u,v) = d B^{[g]}(u,v).
    \end{align*}
    Finally, the $G^\#$-action also commutes with the $A$-action since $(\U^{\psi_0\inv})^{[g]} = (\U^{[g]})^{\psi_0\inv}$ and 
    \begin{align*}
        \psi_0 \big(B^{[g]} (u,v) \big) 
        &= \psi_0 \big( \sign{g}{u} B(u,v) \big)
        &= \sign{g}{u} (\psi_0 \circ B) (u,v) = (\psi_0 \circ B)^{[g]} (u,v).
    \end{align*}
\end{proof}

% These 3 actions can be combined into a $(\D^\times_{\mathrm{gr}} \rtimes A) \times G^\#$-action, where $A$ acts on $\D^\times_{\mathrm{gr}}$ by evaluation. 
% To see that, let $d\in \D^\times_{\mathrm{gr}}$, $\psi_0 \in A$ and $g \in G^\#$. 
% The action of $d$ does not change $\U$, hence commutes in the first entry with the other actions. 
% On the other hand, $(\psi_0 \circ dB)(u,v) = \psi_0 \big( (d B(u,v) ) \big) = \psi_0 (d) \psi_0 (B(u,v)) = (\psi_0(d) \circ \psi_0(B) ) (u,v)$, for all $u,v \in \U$.

\begin{cor}\label{cor:iso-with-actions}
    Under the assumptions of Theorem \ref{thm:iso-abstract-vphi}, if $\D \not \iso \D'$, then $(R, \vphi) \not \iso (R', \vphi')$. 
    Otherwise, fix an isomorphism $\psi_0\from \D \to \D'$. 
    Then $(R, \vphi) \iso (R', \vphi')$ if, and only if, $\big( (\U')^{\psi_0}, \psi_0\inv \circ B' \big)$ is isomorphic to an object in the $(\D^\times_{\mathrm{gr}} \rtimes A) \times G^\#$-orbit of $(\U, B)$. 
    % and lie in the same orbit of the $(\D^\times_{\mathrm{gr}} \rtimes A) \times G^\#$-action. \qed
\end{cor}

% ----- 

\section{Matrix representation of a su\-per\--anti\--auto\-mor\-phism}

In this section, we are going to express the super-anti-automorphism (not necessarily involutive) $\vphi$ in terms of matrices with entries in $\D$. 
One could do that by following Equation \eqref{eq:vphi-r-Star-is-a-superconjugation}, but we will take a different path. 

As before, we suppose $\D$ is a graded division superalgebra, $\U$ is a nonzero right graded module of finite rank over $\D$, $R = \End_\D (\U)$ and $\vphi$ is a degree-preserving super-anti-automorphism on $R$. 
Also, let $\vphi_0$ be a super-anti-automorphism on $\D$ and $B$ be a nondegenerate $\vphi_0$-sesquilinear form on $\U$ determinig $\vphi$ as in Theorem \ref{thm:vphi-iff-vphi0-and-B}.

\begin{defi}\label{def:matrix-representing-B}
    Given a homogeneous $\D$-basis $\{e_1, \ldots, e_k\}$ of $\U$, the \emph{matrix representing the form B} is defined to be $\Phi = (\Phi_{ij}) \in M_k(\D)$, where $\Phi_{ij} = B(e_i, e_j)$.
\end{defi}

From now on, let $\mc B = \{e_1, \ldots, e_k\}$ be a fixed homogeneous $\D$-basis of $\U$, following Convention \ref{conv:pick-even-basis} (\ie, if $\D$ is odd, we take $\mc B$ with only even elements). 
We will use $\mc B$ to identify $R = \End_\D (\U)$ with $M_k (\D)$. 
Also, we will denote $|e_i|$ simply by $|i|$ for all $i \in \{1, \ldots, k\}$. 

% We will assume that the even elements precede the odd ones. 

% We will also follow Convention \ref{conv:pick-even-basis}, \ie, if $\D$ is odd, we will choose the $\D$-basis $\mc B$ to be one having only even elements.

\begin{convention}\label{conv:pick-even-basis}
    If $\D$ is odd (\ie, $\D\odd \neq 0$), we will choose the $\D$-basis $\mc B$ to be one having only even elements. 
    This is possible because, given any homogeneous $\D$-basis, we can multiply its odd elements by a nonzero homogeneous odd element in $\D$. 
\end{convention}

\begin{remark}\label{rmk:M(D)=M(FF)-tensor-D}
    It is well know that we a natural isomorphism between $M_k(\D)$ and $M_k(\FF)\tensor \D$, where we use the usual tensor product of algebras. 
    For superalgebras, though, we usually use a different product on the space $M_k(\FF)\tensor \D$, given by \[(r_1 \tensor s_1) (r_2 \tensor s_2) = \sign{r_2}{s_1} (r_1 r_2) \tensor (s_1 s_2).\] 
    If we are following Convention \ref{conv:pick-even-basis}, either $M_k(\FF)$ or $\D$ have trivial canonical $\ZZ_2$-grading, hence both tensor products coincide.
\end{remark}

\begin{defi}
    Let $X = (x_{ij})$ be a matrix in $M_k (\D)$. 
    We define $\vphi_0 (X)$ to be the matrix obtained by applying $\vphi_0$ in each entry, \ie, $\vphi_0 (X) \coloneqq (\vphi_0(x_{ij}))$. 
    We also extend the definition \emph{supertranspose} {(\tt see ??)} to matrices over $\D$ by putting $X\stransp \coloneqq \big((-1)^{(|i| + |j|) |i|} x_{ji} \big)$. 
    Note that, with our choice of $\mc B$ in the case of odd $\D$, we have that $X\stransp = X\transp$, the ordinary transpose.
\end{defi}

\begin{prop}\label{prop:matrix-vphi}
    Let $\Phi$ be the matrix representing $B$. 
    For every $r\in  R\even \cup R\odd$, let $X \in M_k(\D)$ be the matrix representing $r$ and let $Y \in M_k(\D)$ be the matrix representing $\vphi(r)$.
    Then, following Conventions \ref{conv:pick-even-form} and \ref{conv:pick-even-basis}, we have that
    %
    \begin{align}
        Y &= \Phi\inv\, \vphi_0( X\stransp )\, \Phi. \addtocounter{equation}{1}\tag{\theequation}\label{eq:matrix-vphi-D-even}
        \intertext{and, if $\D$ is odd, we have}
        Y &= \sign{B}{r}\,\Phi\inv\, \vphi_0( X\stransp )\, \Phi.\addtocounter{equation}{1}\tag{\theequation}\label{eq:matrix-vphi-D-odd}
    \end{align}
\end{prop}

\begin{proof}
    First of all, note that Equation \eqref{eq:superadjunction} is equivalent to the following:
    %
    \begin{alignat*}{2}
        \forall e_i, e_j \in \mc B, && B(re_i, e_j) &= \sign{r}{i} B(e_i, \vphi(r) e_j),
    \intertext{which, by the definitions of $X$, $Y$ and $\Phi$, becomes}
        \forall e_i, e_j \in \mc B, && \quad B\bigg(\sum_{\ell=1}^k e_\ell x_{\ell i}, e_j\bigg) &= \sign{r}{i} B\bigg(e_i, \sum_{\ell=1}^k e_\ell y_{\ell j}\bigg) \addtocounter{equation}{1}\tag{\theequation}\label{eq:superadjunction-matrix}.
    \end{alignat*}
    %
    
    Fix arbitrary $p,q \in \{1, \ldots, k\}$ and suppose that the $(p,q)$-entry of $X$ is a nonzero $G^\#$-homogeneous element of $\D$ and $x_{ij} = 0$ elsewhere, \ie, $X$ represents the map $r \in \End_\D(\U)$ defined by $r e_i = \delta_{iq} e_p x_{pq}$. 
    By the $\FF$-linearity of Equation \eqref{eq:matrix-vphi-D-even} %and \eqref{eq:matrix-vphi-D-odd}
    , it suffices to consider such $X$. 
    Note that $|r| = |e_p| + |x_{pq}| - |e_q| = |p| + |q| + |x_{pq}|$. 
    Then, on the one hand,
    %
    \begin{align*}
        B\bigg(\sum_{\ell=1}^k e_\ell x_{\ell i}, e_j\bigg) = B (e_p x_{pi}, e_j) &= (-1)^{ (|B| + |p|) |x_{pi}|} \vphi_0(x_{pi}) B(e_p, e_j)
        \\&= (-1)^{ (|B| + |p|) |x_{pi}|} \vphi_0(x_{pi}) \Phi_{pj},
    %\end{align*}
    %
    \intertext{which is only nonzero if $i = q$. On the other hand,}
    %
    %\begin{align*}
        \sign{r}{i} B\bigg(e_i, \sum_{\ell=1}^k e_\ell y_{\ell j}\bigg)
        &= \sign{r}{i} \sum_{\ell=1}^k B(e_i, e_\ell) y_{\ell j}\\
        &= (-1)^{ (|p| + |q| + |x_{pq}|) |i| } \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j}. 
    %\end{align*}
    %
    \intertext{Therefore, Equation \eqref{eq:superadjunction-matrix} is equivalent to, for all $i,j \in \{1, \ldots, k\}$,}
    %
    %\begin{align*}
        (-1)^{ (|B| + |p|) |x_{pi}|} \vphi_0(x_{pi}) \Phi_{pj} %&= \sign{r}{i} \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j}\\
        &= (-1)^{ (|p| + |q| + |x_{pq}|) |i| } \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j}. \addtocounter{equation}{1}\tag{\theequation}\label{eq:expression}
    \end{align*}
    %

    If $\D$ is even, then $|x_{pi}| = \bar 0$ and this equation reduces to
    \[              \vphi_0(x_{pi}) \Phi_{pj} = (-1)^{ (|p| + |q|) |i| } \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j}
    \]
    or, equivalently, 
    \[
        \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j} = (-1)^{ (|p| + |q|) |i| } \vphi_0(x_{pi}) \Phi_{pj}.
    \]
    The left-hand side is the $(i,j)$-entry of $\Phi\, Y$. 
    The right-hand side is only nonzero if $i = q$, so it can be rewritten as 
    $(-1)^{ (|p| + |i|) |i| } \vphi_0(x_{pi}) \Phi_{pj}$. 
    Recalling our choice of $X$, this is equal to $\sum_{\ell =1}^k (-1)^{ (|\ell| + |i|) |i| } \vphi_0(x_{\ell i}) \Phi_{\ell j}$, since $x_{\ell i}$ is only nonzero if $\ell = p$. 
    Hence the right-hand side is the $(i,j)$-entry of $\vphi_0 (X\stransp) \Phi$, and Equation \eqref{eq:matrix-vphi-D-even} follows. 
    
    If $\D$ is odd, by our choice of basis, Equation \eqref{eq:expression} reduces to
    \[
        (-1)^{|B| |x_{pi}|} \vphi_0(x_{pi}) \Phi_{pj} =  \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j},
    \]
    which, by the same reasoning as above, implies $(-1)^{|B||r|} \vphi_0(X\stransp) \Phi = \Phi Y$. 
    But we are following Convention \ref{conv:pick-even-form}, hence $|B| = \bar 0$ and, therefore, we have the desired result.
\end{proof}

% \begin{proof}
%     First of all, note that Equation \ref{eq:superadjunction} is equivalent to, for all $e_i, e_j \in \mc B$,
%     %
%     \[
%         B(re_i, e_j) = \sign{r}{i} B(e_i, \vphi(r) e_j).
%     \]
%     By the definitions of $X$, $Y$ and $\Phi$, we have that
%     %
%     \begin{align*}
%         B\bigg(\sum_{\ell=1}^k e_\ell x_{\ell i}, e_j\bigg) &= \sum_{\ell=1}^k (-1)^{( |B| + |\ell|) |x_{\ell i}|} \vphi_0( x_{\ell i} ) B (e_\ell x_{\ell i}, e_j)\\ &= \sum_{\ell=1}^k (-1)^{( |B| + |\ell|) |x_{\ell i}|} \vphi_0( x_{\ell i} ) \Phi_{\ell j}
%         \intertext{and}
%         \sign{r}{i} B\bigg(e_i, \sum_{\ell=1}^k e_\ell y_{\ell j}\bigg) 
%         &= \sign{r}{i} \sum_{\ell=1}^k B(e_i, e_\ell) y_{\ell j}\\
%         &= \sign{r}{i} \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j}. 
%     \end{align*}
%     %
    
%     Let $p,q \in \{1, \ldots, k\}$, and suppose $X$ is such that $x_{pq}$ is a nonzero $G^\#$-homogeneous element of $\D$ and $x_{ij} = 0$ elsewhere, \ie, $X$ represents the map $r \in \End_\D(\U)$ defined by $r e_i = \delta_{iq} e_p x_{pq}$. 
%     By the $\FF$-linearity of Equations \eqref{eq:matrix-vphi-D-even} and \eqref{eq:matrix-vphi-D-odd}, it suffices to consider such $X$. 
%     Note that $|r| = |e_q| + |x_{pq}| - |e_p| = |p| + |q| + |x_{pq}|$. 
%     Then
%     %
%     \begin{align*}
%         B\bigg(\sum_{\ell=1}^k e_\ell x_{\ell i}, e_j\bigg) = B (e_p x_{pi}, e_j) &= (-1)^{ (|B| + |p|) |x_{pi}|} \vphi_0(x_{pi}) B(e_p, e_j)
%         \\&= (-1)^{ (|B| + |p|) |x_{pi}|} \vphi_0(x_{pi}) \Phi_{pj},
%     \end{align*}
%     %
%     which is only nonzero if $i = q$. 
%     Combining this with Equation \eqref{eq:superadjunction-matrix}, we get
%     %
%     \begin{align*}
%         (-1)^{ (|B| + |p|) |x_{pi}|} \vphi_0(x_{pi}) \Phi_{pj} &= \sign{r}{i} \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j}\\
%         &= (-1)^{ (|p| + |q| + |x_{pq}|) |i| } \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j}. \addtocounter{equation}{1}\tag{\theequation}\label{eq:expression}
%     \end{align*}
%     %
%     If $\D$ is even, then $|x_{pi}| = 0$ and this expression reduces to
%     \[              \vphi_0(x_{pi}) \Phi_{pj} = (-1)^{ (|p| + |q|) |i| } \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j}
%     \]
%     or, reordering it, 
%     \[
%         \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j} = (-1)^{ (|p| + |q|) |i| } \vphi_0(x_{pi}) \Phi_{pj}.
%     \]
%     The left-hand side is the entry $ij$ of $\Phi\, Y$. 
%     The right-hand side is only nonzero if $i = q$, so it can be rewritten as 
%     $(-1)^{ (|p| + |i|) |i| } \vphi_0(x_{pi}) \Phi_{pj}$. 
%     Also, recalling our choice of $X$, it is equal to $\sum_{\ell =1}^k (-1)^{ (|\ell| + |i|) |i| } \vphi_0(x_{\ell i}) \Phi_{\ell j}$, since $x_{\ell i}$ is only nonzero if $\ell = p$. Hence the right-hand side is the $ij$ entry of $\vphi_0 (X\stransp) \Phi$, and Equation \eqref{eq:matrix-vphi-D-even} follows. 
    
%     If $\D$ is odd, by our choice of basis, Equation \eqref{eq:expression} reduces to
%     \[
%         (-1)^{|B| |x_{pi}|} \vphi_0(x_{pi}) \Phi_{pj} =  \sum_{\ell=1}^k \Phi_{i \ell} y_{\ell j},
%     \]
%     which implies $(-1)^{|B||r|} \phi_0(X\stransp) \Phi = \Phi Y$.
% \end{proof}

% \begin{remark}
%     Note that if $\D$ is odd, replacing $B$ by $dB$ with an odd $d$ if necessary, we can guarantee that $B$ is even. 
%     In this case, Equation \eqref{eq:matrix-vphi-D-odd} reduces to \eqref{eq:matrix-vphi-D-even}.
% \end{remark}

% \begin{cor}[of the proof]
%     Let $\vphi_0$ be a super-anti-automorphism on $\D$ and let $B$ be a nonzero $\vphi_0$-sesquilinear form on $\U$. If $\vphi\from R \to R$ be a parity preserving map satisfying Equation \eqref{eq:superadjunction}. 
%     Then $B$ is nondegenerate if, and only if, $\vphi$ is a super-anti-automorphism.
% \end{cor}

\section{Superinvolutions and sesquilinear forms}

Our goal now is to specialize the results of Section \ref{sec:super-anti-auto-and-sesquilinear} to the case where $\vphi$ is a superinvolution. 
To this end, let us investigate what super-anti-automorphism of $\D$ and what sesquilinear form on $\U$ determine the super-anti-automorphism $\vphi\inv$. 
Again, we suppose $\D$ is a graded division superalgebra, $\U$ is a nonzero right graded module of finite rank over $\D$ and put $R = \End_\D (\U)$.

\begin{defi}\label{def:barB}
    Given a super-anti-automorphism $\vphi_0$ on $\D$ and a $\vphi_0$-sesqui\-li\-near form $B$ on $\U$,  we define $\overline {B}\from \U\times \U \to \D$ by $\overline {B} (u,v) \coloneqq \sign{u}{v} \vphi_0\inv (B(v, u))$ for all $u, v \in \U$.
\end{defi}

% \begin{lemma}
%     Let $B\from \U\times \U\Star \to \D$ be a $\vphi_0$-sesquilinear form. Suppose there is a super-anti-automorphism $\vphi$ on $R = \End_\D(U)$ such that Equation \eqref{eq:superadjunction} holds. If $B$ is nonzero, then it is nondegenerate.
% \end{lemma}

\begin{prop}\label{prop:barB-determines-vphi-inv}
    Under the conditions of Definition \ref{def:barB}, we have that $\overline {B}$ is a $\vphi_0\inv$-sesquilinear form of the same degree and parity as $B$. 
    Further, if $B$ is nondegenerate and $\vphi$ is the super-anti-automorphism on $R$ determined by $(\vphi_0, B)$ as in Theorem \ref{thm:vphi-iff-vphi0-and-B}, then $\overline{B}$ is nondegenerate and $\vphi\inv$ is determined by $(\vphi_0\inv, \overline B)$, \ie, 
    %
    \begin{equation}\label{eq:barB-superadjunction}
        \forall r\in R\even \cup R\odd ,\,\forall u, v \in \U\even \cup \U\odd,  \quad \overline {B}(ru,v) = \sign{r}{u} \overline {B}(u,\vphi\inv (r)v).
    \end{equation}
    %
\end{prop}

\begin{proof}
    Since $B$ is $\FF$-bilinear, so is $\overline {B}$. 
    Also, since $\vphi_0$ preserves degree and parity, $\overline {B}$ is homogeneous of the same degree and parity as $B$. 
    Let us check the conditions of Definition \ref{def:sesquilinear-form} and Equation \eqref{eq:barB-superadjunction}.
    \vspace{2mm}
    \begin{align*}
       \intertext{ Condition \eqref{enum:linear-on-the-second}:}
        \overline {B} (u,vd) &= (-1)^{|u|( |v| + |d|)} \vphi_0\inv (B(vd, u))  \\
        & = (-1)^{|u|( |v| + |d|)} (-1)^{|d| (|B| + |v|)} \vphi_0\inv \big( \vphi_0(d) B(v, u) \big) \\
        & = (-1)^{|u||v| + |u||d| + |d||B| + |d||v|} (-1)^{|d| (|B| + |v| + |u|) }  \vphi_0\inv \big(B(v, u)) d \\ &= \sign{u}{v} \vphi_0\inv \big(B(v, u)) d = \overline {B}(u, v) d .
    \intertext{Condition \eqref{enum:vphi0-linear-on-the-first}:}
        \overline {B}(ud, v) &= (-1)^{(|u| + |d|) |v|} \vphi_0\inv \big( B(v, ud) \big) \\ &= (-1)^{(|u| + |d|) |v|} \vphi_0\inv \big( B(v, u)d \big) \\ &= (-1)^{(|u| + |d|) |v|} (-1)^{|d| (|B| + |v| + |u|)} \vphi_0\inv (d) \vphi_0\inv\big( B(v, u) \big) \\ &= (-1)^{|u||v| + |d| |B| + |d||u|} \vphi_0\inv (d) \vphi_0\inv\big( B(v, u) \big) \\ &= (-1)^{(|B| + |u|) |d|} \vphi_0\inv (d) \overline {B}(u, v).
      \intertext{For Equation \eqref{eq:barB-superadjunction}, note that replacing $r$ for $\vphi\inv(r)$, Equation \eqref{eq:superadjunction} can be rewritten as}
        B(v, ru) &= \sign{r}{v} B(\vphi\inv(r)v,u).
      \intertext{Hence, we have that}
        \overline {B}(ru, v) &= (-1)^{(|r| + |u|) |v|} \vphi_0\inv \big( B(v, ru) \big)\\ &= (-1)^{(|r| + |u|) |v|} (-1)^{|r||v|} \vphi_0\inv \big( B(\vphi\inv (r)v, u) \big) \\ &= (-1)^{|u||v|} \vphi_0\inv \big( B(\vphi\inv (r)v, u) \big) \\ &= (-1)^{|u||v|} (-1)^{(|r| + |v|) |u|} \overline {B}(u, \vphi\inv (r)v) \\ &= \sign{r}{u} \overline {B}(u, \vphi\inv (r)v).
    \end{align*}
    
    Finally, Equation \eqref{eq:barB-superadjunction} together with $B$ being nondegenerate implies that $\overline{B}$ is nondegenerate. 
    To see that, let $u$ be a nonzero homogeneous element in $\rad \overline{B}$. 
    Then for for every $r\in R\even \cup R\odd$ and $v\in \U\even \cup \U\odd$, we have that $\overline{B}(u, \vphi\inv (r) v) = 0$, hence $\overline{B}(ru, v) = 0$. 
    Since $r \in R\even \cup R\odd$ and $v\in \U\even \cup \U\odd$ were arbitrary, this implies $\overline{B} (Ru, \U) = 0$. 
    But $\U$ is simple as a graded $R$-supermodule, so we would have $\overline{B}(\U, \U) = 0$ and then, using that $\vphi_0$ is bijective, $B (\U, \U) = 0$, a contradiction.
\end{proof}

\begin{lemma}\label{lemma:bar-dB}
    Under the conditions of Definition \ref{def:barB}, let $d$ be a nonzero $G^\#$-homogeneous element of $\D$ and consider $\vphi_0' \coloneqq \operatorname{sInt}_d\circ\, \vphi_0$ and $B' \coloneqq d B$. 
    Then $\overline {B'} = (-1)^{|d|} \vphi_0\inv (d) \overline B$.
\end{lemma}

\begin{proof}
    Note that $(\vphi_0')\inv = \vphi_0\inv \circ \operatorname{sInt}_{d}\inv = \vphi_0\inv \circ \operatorname{sInt}_{d\inv}$. 
    Hence, for all $u, v \in \U\even \cup \U\odd$,
    %
    \begin{align*}
        \overline {B'} (u,v) &= \sign{u}{v} (\vphi_0\inv \circ \operatorname{sInt}_{d\inv})  (d B(v, u) ) \\
        &= \sign{u}{v} \vphi_0\inv \big( (-1)^{|d| (|d| + |B| + |u| + |v|)}\,  d\inv d B (v, u) d \big) \\ &= \sign{u}{v} (-1)^{|d|}\, \vphi_0\inv (d) \vphi_0\inv(B(v, u)) =  (-1)^{|d|}\,\vphi_0\inv (d) \overline {B} (u, v).
    \end{align*}
\end{proof}

We are primarily interested in the case $\FF$ is an algebraically closed field and $\D$ is finite dimensional. 
In this case, we have that $\D\even_e = \FF 1$, so we are under the hypothesis of the following theorem, which is a graded version of \cite[Theorem 7]{racine}:

\begin{thm}\label{thm:vphi-involution-iff-delta-pm-1}
    % Suppose $\FF$ is an  algebraically closed field. 
    Let $\D$ be a graded division superalgebra such that $\D\even_e = \FF 1$, let $\U$ be a nonzero right graded module of finite rank over $\D$ and let $\vphi$ be a degree-preserving super-anti-automorphism on $R \coloneqq \End_\D (\U)$. 
    Consider a super-anti-automorphism $\vphi_0$ on $\D$ and a nondegenerate $\vphi_0$-sesqui\-li\-near form $B$ on $\U$ determining $\vphi$ as in Theorem \ref{thm:vphi-iff-vphi0-and-B}.
    Then $\vphi$ is a superinvolution if, and only if, $\vphi_0$ is a superinvolution and $\overline B = \pm B$. 
\end{thm}

\begin{proof}
    Using Proposition \ref{prop:barB-determines-vphi-inv} and Theorem \ref{thm:vphi-iff-vphi0-and-B}, we conclude that $\vphi = \vphi\inv$ if, and only if, there is $\delta \in \D$ such that (i) $\vphi_0\inv = \operatorname{sInt}_\delta \circ \,\vphi_0$ and (ii) $\overline {B} = \delta B$. 
    % If $\vphi_0^2 =\id_\D$ and $B = \pm \overline{B}$, we have conditions (i) and (ii) sati
    % To prove the ``if'' part of the statement, we take $\delta \in \{\pm 1\}$, since then (i) becomes $\vphi_0 = \vphi_0\inv$ and (ii), $B = \pm \overline{B}$.
    
    If $\vphi_0^2 =\id_\D$ and $\overline{B} = \delta B$ with $\delta \in \{\pm 1\}$, conditions (i) and (ii) are satisfied, proving the ``if'' part of the statement. 

    For the ``only if'' part, since both parity and degree of $B$ and $\overline {B}$ coincide, (ii) implies $\delta \in \D\even_e$. 
    We are assuming $\D\even_e = \FF 1$, so $\operatorname{sInt}_\delta = \id_\D$ and (i) becomes $\vphi_0 = \vphi_0\inv$, \ie, $\vphi_0$ is a superinvolution. 
    Also from $\delta \in \FF 1$, $\vphi_0\inv(\delta) = \delta$ and, hence, using Lemma \ref{lemma:bar-dB}, we have that
    \[
        B = \overline {\overline B} = \overline {\delta B} = (-1)^{|\delta|} \vphi_0\inv(\delta) \overline B= \delta \overline B = \delta^2 B.
    \]
    This implies $\delta^2 = 1$. 
    Therefore $\delta \in \{ \pm 1 \}$, so $\overline B = \pm B$, concluding the proof. 
\end{proof}



% it is clear that $B(u,vd) = B(u,v)d$. By Equation \eqref{eq:sesquilinear-before-B}, the map $B: \U \times \U \to \D$ is a \emph{$\vphi_0$-sesquilinear form}, \ie,
% \[
%     B(ud, v) = (-1)^ {(|B| + |u|)|d|}
% \]

% Consider the map $\vphi_0: \D \to \D$ given by 

% Consider the map $\vphi_0(d) := \sign{\vphi_1}{d}\vphi_1\inv d \vphi_1$ (where juxtaposition denotes composition of maps on the right).
% Then
% \begin{equation}\label{eq:sesquilinear-before-B}
%     (ud)\vphi_1 = (u) (d\vphi_1) =  (u)(\vphi_1\vphi_1\inv d \vphi_1) = \sign{d}{\vphi_1}(u)\vphi_1 \,\vphi_0(d).
% \end{equation}
% It is straightforward to check that $\vphi_0: \D = \End_R(\mc U) \to \End_R(\mc U\Star) = \D\sop$ is an isomorphism of superalgebras.
% We will consider $\vphi_0$ as a super-anti-automorphism on $\D$.

%Recall (Subsection \ref{ssec:superlinear-maps}) that $\vphi_1^\circ$ is an $R$-superlinear map on the left. Using it, the Equation \eqref{eq:sesquilinear-before-B} becomes
% \begin{equation}\label{eq:sesquilinear-with-vphi1-circ}
%     \vphi_1^\circ (ud) = \vphi_1^\circ (u) \vphi_0 (d)
% \end{equation}

%For each $u\in \U$, $\vphi_1(u)$ is an $\D$-linear map on the left. We, then, can define \[B(u,v) = \sign{\vphi_1}{u} ((u)\vphi_1)(v),\]
%or, using the notation introduced in Subsection \ref{ssec:superlinear-maps},
% \[
%     B(u,v) = \vphi_1^\circ (u) (v),
% \]
% for all $u,v \in U$.


%We will consider $\vphi_0$ as a super-anti-automorphism on $\D$.

%Recall (Subsection \ref{ssec:superlinear-maps}) that $\vphi_1^\circ$ is an $R$-superlinear map on the left. Using it, the Equation \eqref{eq:sesquilinear-before-B} becomes


%Since  this new action makes $\mc U\Star$ a simple graded left $R$-supermodule. Also, since we had $\D\sop = \End_{R\sop} (\U\Star)$, we c it follows that $\D\sop$ can be identif
%We, then, have that $\mc U\Star$ is a simple graded left $R$-module and that $\D\sop = \End_R(\mc U\Star)$.

%Since $R$ acts on the left, we will use the convention of writing $R$-superlinear maps on the right. % (see Subsection \ref{ssec:superlinear-maps}).
%By Proposition {\tt ??}, $R$ has only one graded simple supermodule up to isomorphism and shift, \ie, there is an invertible $R$-linear map $\vphi_1: \mc U \to \mc U\Star$ which is homogeneous of some degree $(g_0, \alpha)\in G^\#$.



% Using the notation just introduced, Equation \eqref{eq:sesquilinear-before-B} becomes
% \begin{equation}%\label{eq:sesquilinear-with-vphi1-circ}
%     \vphi_1^\circ (ud) = \vphi_1^\circ (u) \tilde\vphi_0 (d)
% \end{equation}
% or, puting $\vphi_0(d) = (\tilde \vphi_0(d))^\circ$,
% \begin{equation}\label{eq:sesquilinear-with-vphi1-circ}
%     \vphi_1^\circ (ud) = (-1)^{|d|(|\vphi_1|+|u|)}\vphi_0 (d)\vphi_1^\circ (u).
% \end{equation}







% It is important to note that the map $\vphi_1$ is not uniquely determined. For every nonzero homogeneous element $d\in\D$, the map $d\vphi_1: \mc U \to \mc U\Star$ is also an invertible, homogeneous and $R$-superlinear. If we consider $\vphi_1$ fixed, every such map can be obtained this way: if $\vphi_1' : \mc U \to \mc U\Star$ is an invertible homogeneous $R$-superlinear map, then we could take $d := \vphi'\vphi\inv \in \End_R(\mc U) = \D$ and, hence, $\vphi_1' = d \vphi_1$.

% Changing $\vphi_1$ to $\vphi_1'$ also changes the super-anti-automorphism $\vphi_0 (c) = \sign{\vphi_1}{d}\vphi_1\inv d \vphi_1$ to $\vphi_0':= \sign{\delta\vphi_1}{d}\vphi_1\inv\delta\inv d \delta\vphi_1= \sign{\delta}{d} \vphi_0(\delta\inv d \delta)$. In other words, $\vphi_0' = \vphi_0 \circ \operatorname{sInt}_\delta$, where $\operatorname{sInt}_\delta: $

% The choice of the map $\vphi_1$ 

%If $\vphi_1' : \mc U \to \mc U\Star$ is another invertible and homogeneous $R$-superlinear map, then $\vphi'\vphi\inv: \mc U \to \mc U$ is a nonzero homogeneous element of $\D = \End_R(\mc U)$.
%Conversely, for each nonzero homogeneous element $\delta\in\D$, the map $\vphi_1' := \delta\vphi_1: \mc U \to \mc U\Star$ is $R$-superlinear, invertible and homogeneous.
% Changing $\vphi_1$ to $\vphi_1'$ also changes the super-anti-automorphism $\vphi_0(d) = \sign{\vphi_1}{d}\vphi_1\inv d \vphi_1$ to $\vphi_0':= $


% depends on the choice of $\vphi_1$: if we consider $\delta\vphi_1$ instead, then we change $\vphi_0(d) = \vphi_1\inv d \vphi_1$ to $\vphi_0'(d) = \vphi_0(\delta\inv d \delta)$.



\section{Classification of graded-simple superalgebras\\ with superinvolution}

In this section we will introduce parameters that describe the finite dimensional associative superalgebras with superinvolution $(R, \vphi)$ where $R$ is graded simple and, then, give a classification result involving these parameters. 
Throughout this section, we will assume that $\FF$ is an algebraically closed field with $\Char \FF \neq 2$.

Recall from Theorem \ref{thm:vphi-involution-iff-delta-pm-1} that in this case we have that $R \iso \End_\D (\U)$ and that $\vphi$ is determined by a superinvolution $\vphi_0$ on $\D$ and a $\vphi_0$-sesquilinear form on $\U$.

\subsection{Parametrization of $(\D, \vphi_0)$}

Recall that a graded division superalgebra is the same as a graded division algebra if we consider the $G^\#$-grading. 
In particular, the isomorphism class of a finite dimensional graded division superalgebra $\D$ is determined by a pair $(T, \beta)$ where $T \coloneqq \supp \D \subseteq G^\#$ is a finite abelian group and $\beta\from T\times T \to \FF^\times$ is an alternating bicharacter {\tt (see ??)}. 
Instead of writing subscripts for the $G$-grading and superscripts for the canonical $\ZZ_2$-grading, it will be convenient to write $\D = \bigoplus_{t\in T} \D_t$ and recover the parity via the map $p\from T \to \ZZ_2$ which is the restriction of the projection $G^\# = G\times \ZZ_2 \to \ZZ_2$. 
% Sometimes we may want to discuss graded division superalgebras without reference to the groups $G$ or $G^\#$, so it is convenient to say 

{\tt (for the ``see'' part: [EK] $D_4$ and [BK] gradings on classical \\lie algebras)}

Since each component $\D_t$ of $\D$ is one-dimensional, an invertible degree-preserving map $\vphi_0\from \D \to \D$ is completely determined by a map $\eta\from T \to \FF^\times$.

\begin{prop}\label{prop:superpolarization}
    Let $\vphi_0\from \D \to \D$ be the invertible degree-preserving map determined by $\eta\from T \to \FF^\times$  such that $\vphi_0(X_t) = \eta(t) X_t$ for all $t\in T$ and $X_t\in \D_t$. 
    Then $\vphi_0$ is a super-anti-automorphism if, and only if,
    %
    \begin{equation}\label{eq:superpolarization}
        \forall a,b\in T, \quad (-1)^{p(a) p(b)} \beta(a,b) =  \eta(ab) \eta(a)\inv \eta(b)\inv.
    \end{equation}
    %
    Moreover, $\D$ admits a super-anti-automorphism if, and only if, $\beta$ only takes values $\pm 1$.
\end{prop}

\begin{proof}
    For all $a,b \in T$, let $X_a \in \D_a$ and $X_b\in \D_b$. Then:
    %
    \begin{alignat*}{2}
        &&\vphi_0(X_a X_b) &= (-1)^{p(a) p(b)} \vphi_0(X_b) \vphi_0(X_a)\\
        \iff&&\,\, \eta(ab)X_a X_b &= (-1)^{p(a) p(b)} \eta(a) \eta(b) X_b X_a\\
        \iff&&\, \eta(ab)X_a X_b &= (-1)^{p(a) p(b)} \eta(a) \eta(b) \beta(b,a) X_a X_b\\
        \iff&& \eta(ab) &= (-1)^{p(a) p(b)} \eta(a) \eta(b) \beta(b,a)
        \\
        \iff&& (-1)^{p(a) p(b)} \beta(b, a) &=  \eta(ab) \eta(a)\inv \eta(b)\inv.
    \end{alignat*}
    The right-hand side of this last equation does not change if $a$ and $b$ are switched, hence $\beta(b,a) = \beta(a,b)$. 
    
    Since $\beta$ is alternating, $\beta(b, a) = \beta (a, b)\inv$, therefore $\beta(a,b)^2 = 1$, which proves one direction of the ``moreover'' part.
    %from where we conclude that $\beta(a,b) = \pm 1$. 
    The converse follows from the fact that the isomorphism class of $\D\sop$ is determined by $(T, \beta\inv)$, so if $\beta$ takes only values in $\{ \pm 1 \}$, there must be an isomorphism from $\D$ to $\D\sop$, which can be seen as a super-anti-isomorphism on $\D$.
\end{proof}

\begin{cor}\label{cor:odd-cant-have-order-2}
    If $\D$ admits a superinvolution, %$\vphi_0$ is a superinvolution. 
    % $\eta(t) \in \{ \pm 1 \}$ for all $t\in T$. 
    then every odd element in $T$ must have order at least $4$.
\end{cor}

\begin{proof}
    The bicharacter $\beta$ is alternating, so if we put $a = b = t$ in Equation \eqref{eq:superpolarization}, we get
    %
    \begin{equation}\label{eq:eta-t-square}
        \forall t\in T, \quad \eta (t)^2 = (-1)^{p(t)} \eta(t^2).
    \end{equation}
    %
    % Also, since $\vphi_0^2 = \id$, $\eta(t)^2 = 1$ for all $t\in T$.
    
    Now let $t\in T^-$. 
    Every odd power of $t$ is also an odd element, so $t$ cannot have an odd order. 
    By Equation \eqref{eq:eta-t-square}, $\eta (t^2) = - \eta(t)^2 = -1$, hence $t^2 \neq e$.
\end{proof}

With this we can translate our task to the level of abelian groups. 
Instead of considering the graded superalgebra with super-anti-automorphism $(\D, \vphi_0)$, we can focus, instead, on the data $(T, \beta, p, \eta)$, where $T$ is a finite abelian group, $\beta$ is an alternating bicharacter on $T$, $p\from T \to \ZZ_2$ is a group homomorphism and $\eta\from T \to \FF^\times$ satisfies Equation \eqref{eq:superpolarization}. 
Also, the condition of $\vphi_0$ being a superinvolution clearly corresponds to $\eta(t) \in \{ \pm 1 \}$ for all $t\in T$.

The following definitions give us a more compact way to express Equation \eqref{eq:superpolarization}. 
Also, Definition \ref{def:coboundary} will play a broader role in Section \ref{sec:div-grads-on-sinv-simple}. 

\begin{defi}\label{def:coboundary}
    Let $H$ and $K$ be groups and let $f\from H \to K$ be any map. 
    We define $\mathrm{d} f\from H\times H \to K$ to be the map given by $\mathrm{d} f\, (a,b) = f(ab)f(a)\inv f(b)\inv$ for all $a,b \in H$. 
    The maps $H\times H \to K$ of this for are called \emph{$2$-coboundaries}.
\end{defi}

\begin{defi}\label{def:tilde-beta}
    Given a finite dimensional graded-division superalgebra associated to $(T, \beta, p)$, we define the bicharacter $\tilde\beta\from T\times T \to \FF^\times$ by $\tilde\beta (a,b) = (-1)^{p(a) p(b)} \beta(a, b)$, for all $a, b \in T$.
\end{defi}

Hence, Equation \eqref{eq:superpolarization} becomes $\tilde\beta = \mathrm{d}\eta$. 
Note that $\tilde\beta$ is skew-symmetric, \ie, $\tilde\beta(b, a) = \tilde\beta\inv(a, b)$, but $\tilde\beta (t,t) = (-1)^{|t|}$, for all $t\in T$, so $\tilde\beta$ is not, in general, alternating. 

We will now see how to translate the concepts of center and supercenter...

The radicals of of $\beta$ and $\tilde\beta$ are the support of the center and supercenter of $\D$, respectively. 

\begin{defi}
    center and supercenter
\end{defi}

\begin{prop}
    center and supercenter are graded
\end{prop}

We state and prove the following for further reference.

\begin{lemma}
    $\rad \tilde\beta = (\rad \beta)\cap T^+$.
\end{lemma}

\begin{proof}
    Let $t\in T^+$. 
    In this case $\tilde\beta (t, \cdot) = \beta (t, \cdot)$, so
    $\tilde\beta (t, T) = 1$ if, and only if, $\beta (t, T) = 1$. 
    Hence $(\rad \tilde\beta)\cap T^+ = (\rad \beta)\cap T^+$. 
    
    Now let $t \in T^-$. 
    In this case $\tilde \beta (t,t) = (-1)^{|t|} = -1$, so $t \not\in \rad \tilde\beta$. 
    Therefore $\rad \tilde\beta = (\rad \tilde\beta)\cap T^+$, concluding the proof.
\end{proof}

\subsection{Parametrization of $(\U, B)$}

% Let $R \coloneqq \End_\D (\U)$ and let $\vphi$ be a superinvolution on R. 
% From Theorem \ref{thm:vphi-involution-iff-delta-pm-1}, $\vphi$ is determined by a pair $(\vphi_0, B)$, where $\vphi_0$ is a superinvolution on $\D$ and $B\from \U \times \U \to \D$ is a homogeneous $\vphi_0$-sesquilinear form on $\U$ such that $\overline B = \delta B$ with $\delta \in \{ \pm 1 \}$. 

Let $(\D, \vphi_0)$ be a fixed graded-division superalgebra with super-anti-automorphism associated to $(T, \beta, p, \eta)$. 


% In Section ??, we saw that the isomorphism class of $(\D, \vphi_0)$ can be described by $(T, \beta, p, \eta)$. 
Recall that a $G$-graded supermodule $\U$ can be regarded as a $G^\#$-graded module 
% written as a direct sum of its isotypic components % $\U_{gT} = \bigoplus_{h \in gT} \U_h$
and that its isomorphism class is determined by the map $\kappa\from G^\#/T \to \ZZ_{\geq 0}$ with finite support. 
Explicitly, $\kappa (gT) = \dim_\D \U_{gT}$, where $\U_{gT}$ is the isotypic component associated to the coset $gT$ (see Section \ref{U-in-terms-of-GxZZ2}).

% defined by $\kappa (gT) = \dim_\D \U_{gT}$, where $\U_{gT}$ is the isotypic component associated to the coset $gT$ (Subsection \ref{U-in-terms-of-GxZZ2}).

% described by a map $\kappa\from G^\#/T \to \ZZ_{\geq 0}$ with finite support. 
We will now consider a 
% nondegenerate 
homogeneous $\vphi_0$-sesquilinear form $B$ on $\U$, $\deg B = g_0 \in G^\#$.
% Its presence gives us further restrictions on $\kappa$. 
Since $B$ has degree $g_0$ and takes values in $\D$, if $B(\U_{g}, \U_{h}) \neq 0$ for some $g, h \in G^\#$, then $g_0 g h \in T$. 
In terms of isotypic components, this means that, given $\U_{g T}$, there is at most one isotypic component $\U_{hT}$ such that $B(\U_{gT}, \U_{hT}) \neq 0$, namely, $\U_{g_0\inv g\inv T}$. 
% we can only have $B(\U_{g T}, \U_{g' T}) \neq 0$ if $\bar {g'} = \bar g_0\inv \bar g\inv \in G^\#/T$. 
We say that the components $\U_{gT}$ and $\U_{g_0\inv g\inv T}$ are \emph{paired by $B$}.
% Since $B$ is nondegenerate, we have that $\U_{g T}$ and $\U_{g_0\inv g\inv T}$ are in duality via $B$ and, in particular, $\kappa(g T) = \kappa(g_0\inv g \inv T)$. 

% Note that $\U_{g T} = \U_{g_0\inv g\inv T}$ if, and only if, $g_0 g^2 \in T$. 
% In this case, we say that $\U_{gT}$ is a \emph{self-dual component}. 
% Otherwise, we say that $\U_{gT}$ and $\U_{g_0\inv g\inv T}$ form a \emph{pair of dual components}. 

% From now on, we will assume that $\vphi_0$ is a superinvolution, \ie, that $\eta$ takes values in $\pmone$. 

We will now reduce the study of $B$ to the study of $\FF$-bilinear forms. 
Fix a set-theoretic section $\xi\from G^\#/T \to G^\#$ of the natural homomorphism $ G^\# \to G^\#/T$, \ie, $\xi (x) \in x$ for all $x \in G^\#/T$, and fix a nonzero element $X_t \in \D_t$ for all $t\in T$. 
Note that $\U_{\xi(x)} \tensor \D \iso \U_x$ via the map $u \tensor d \mapsto ud$ and, hence, an $\FF$-basis of $\U_{\xi(x)}$ is a graded $\D$-basis for $\U_x$. 
In view of Convention \ref{conv:pick-even-basis}, if $\D$ is odd we choose $\xi$ to take values in $G = G\times \{ \bar 0 \}$.

For a given $x \in G^\#/T$, set $y \coloneqq g_0\inv x\inv \in G^\#/T$ and $t \coloneqq g_0 \xi(x) \xi(y) \in T$. 
Also, set $\V_x \coloneqq \U_x + \U_y$ (so $\V_x = \U_x$ if $x=y$ and $\V_x = \U_x \oplus \U_y$ if $x \neq y$) and $V_x \coloneqq \U_{\xi(x)} + \U_{\xi(y)}$ (so $\V_x \iso V_x \tensor \D$). 
We will denote the restriction of $B$ to $\V_x$ by $B_x$ and define the bilinear map $\tilde{B}_x\from V_x \times V_x \to \FF$ by 
\begin{equation}\label{eq:B_x-tilde}
    \tilde{B}_x (u,v) \coloneqq X_{t}\inv B_x (u,v),
\end{equation}
for all $u,v \in V_x$. 
It is clear that $B$ is nondegenerate if, and only if, $B_x$ is nondegenerate for every $x \in G^\#/T$. 
If this is the case, $\U_x$ and $\U_y$ are dual to each other and, hence, $\kappa(x) = \kappa(y)$. 
% If $x = y$ or, equivalently, $g_0 x^2 = T$, we say that $\U_x$ is a \emph{self-dual component}, otherwise we say that $\U_x$ and $\U_y$ are a \emph{pair of dual components}. 

\begin{lemma}\label{lemma:B_x-nondeg}
    The $\vphi_0$-sesquilinear form $B_x$ is nondegenerate if, and only if, the bilinear form $\tilde{B}_x$ is nondegenerate.
\end{lemma}

\begin{proof}
    Assume $B_x$ is nondegenerate and let $u \in V_x$ be such that $\tilde{B}_x(u,v) = 0$ for all $v \in V_x$. 
    Then $B_x(u, v) = X_{t} \tilde{B}_x(u,v) = 0$ for all $v \in V_x$ and, hence, $B_x(u, vd) = B_x(u, v)d = 0$ for all $d \in \D$. 
    It follows that $B_x(u,v) = 0$ for all $v\in \V_x = V_x \D$ and, therefore, $u = 0$.
    
    Now assume $\tilde{B}_x$ is nondegenerate and let $u \in \V_x$ be such that $B_x (u,v) = 0$ for all $v \in \V_x$.
    Let $v\in V_x$ be homogeneous and write $u = \sum_{g\in G^\#} u_g$ where $u_g \in \U_g$. 
    Then $0 = B_x(\sum_{g\in G^\#} u_g, v) = \sum_{g\in G^\#} B_x(u_g, v)$ and, since the summands have pairwise distinct degrees, $B_x(u_g, v) = 0$ for all $g\in G^\#$. 
    Also, since $\xi(gT)\inv g \in T$, we have that $u_g = \tilde u_g d$ for some homogeneous elements $\tilde u_g \in V_x$ and $0 \neq d \in \D$. 
    Then $0 = B_x(u_g, v) = (-1)^{|d|(|B| + |\tilde u_g|)} \vphi_0(d) B_x(\tilde u_g, v)$, and hence $B_x(\tilde u_g, v) = 0$. 
    It follows that $\tilde{B}_x(\tilde u_g, v) = 0$, for all $v\in V_x$, which implies $\tilde u_g = 0$. 
    Therefore, $u = 0$, concluding the proof.
\end{proof}

We are interested in the case when the superadjunction with respect to $B$ is involutive. 
By Theorem \ref{thm:vphi-involution-iff-delta-pm-1}, this happens if, and only if, $\vphi_0$ is involutive and $\overline B = \delta B$ for some $\delta \in \pmone$. 
So, from now on, we will assume that $\eta$ takes values in $\pmone$. 

\begin{lemma}\label{lemma:B_x-delta}
    Let $\delta \in \pmone$. 
    Then $\overline{B_x} = \delta B_x$ if, and only if, 
    \[
        \tilde{B}_x (v, u) = (-1)^{|u| |v|} \eta(t) \delta \tilde{B}_x (u, v)
    \]
    for all $u, v \in V_x$, where $t \coloneqq g_0 \xi(x) \xi(g_0\inv x\inv)$.
\end{lemma}

\begin{proof}
    Let $u,v \in \V_x$. 
    By definition of $\overline{B_x}$, we have:
    \begin{alignat*}{3}
        \overline{B_x} (u, v) &= \sign{u}{v} \vphi_0\inv( B_x(v, u) )
        &&= \sign{u}{v} \vphi_0\inv( X_t \tilde{B}_x(v, u) )\\
        &= \sign{u}{v} \tilde{B}_x(v, u) \vphi_0\inv(X_t)
        &&= \sign{u}{v} \tilde{B}_x(v, u) \eta(t)\inv X_t,
    \end{alignat*}
    where we have used the fact that $\tilde B_x (v, u) \in \FF$.
    Hence, $\overline{B_x} (u, v) = \delta {B_x} (u, v)$ if, and only if,
    $\sign{u}{v} \tilde{B}_x(v, u) \eta(t)\inv X_t = \delta X_t \tilde{B}_x(u, v)$, and the result follows.
\end{proof}

Recall the identification $M_k (\D) = \M_k(\FF) \tensor \D$ (see Remark \ref{rmk:M(D)=M(FF)-tensor-D}). 
In the next two propositions we consider a component paired to itself and two components paired to one another.

% For convenience, we will also fix elements $0 \neq X_t \in \D_t$ for all $t\in T$.

\begin{prop}\label{prop:self-dual-components}
    Let $\delta \in \pmone$. 
    Suppose $g_0 x^2 = T$,  and  set $t \coloneqq g_0\xi(x)^2 \in T$. 
    Then 
    \begin{equation}\label{eq:mu_x}
        \mu_{x} \coloneqq (-1)^{|\xi(x)|} \eta(t) \delta \in \pmone
    \end{equation}
    % $\mu_{gT} = (-1)^{|g|} \eta(g_0 g^2) \delta \in \pmone$
    does not depend on the choice of the section $\xi\from G^\#/T \to G^\#$. 
    % Further, there is a $\D$-basis on $\U_{gT}$ consisting only of homogeneous elements of degree $g$ such that  that the restriction of $B$ to $\U_{gT}$ is represented by
    % \begin{enumerate}[(i)]
    %     \item $I_k \tensor X_{g_0g^2}$ if 
    % \end{enumerate}
    Moreover, the restriction $B_x$ of $B$ to $\U_x$ is nondegenerate and satisfies $\overline{B_x} = \delta B_x$ if, and only if, there is a $\D$-basis of $\U_{x}$ consisting only of elements of degree $\xi(x)$ such that the matrix representing $B_x$ is given by
    \begin{enumerate}[(i)]
        \item $I_{\kappa(x)} \tensor X_t$ if $\mu_x = +1$;
        \item $J_{\kappa(x)} \tensor X_t$ if $\mu_{x} = -1$, where $\kappa (x)$ is even and $J_{\kappa(x)} \coloneqq \begin{pmatrix}
        0 & I_{\kappa(x)/2}\\
        -I_{\kappa(x)/2} & 0
    \end{pmatrix}$.
    \end{enumerate}
\end{prop}

\begin{proof}
    Let $g \coloneqq \xi(x)$. If $\xi' \from G^\#/T \to G^\#$ is another section, then there is $s \in T$ such that $\xi' (x) = g s$. 
    Hence:
    \begin{align*}
        (-1)^{|\xi' (x)|} \eta(g_0 \xi' (x)^2) &= (-1)^{|gs|} \eta(g_0 g^2 s^2)\\
        &= (-1)^{|g| + |s|} \sign{g_0 g^2}{s^2} \beta(g_0 g^2, s^2)\eta(g_0 g^2) \eta(s^2)\\
        &= (-1)^{|g| + |s|} (-1)^{2 |g_0 g^2| |s|} \beta(g_0 g^2, s)^2 \eta(g_0 g^2) \eta(s^2) \\
        &= (-1)^{|g| + |s|} \eta(g_0 g^2) \eta(s^2) \\ 
        &= (-1)^{|g| + |s|} \eta(g_0 g^2) (-1)^{|s|} \eta (s)^2 = (-1)^{|g|} \eta(g_0 g^2),
    \end{align*}
    where we have used Equation \eqref{eq:superpolarization} twice. 
    
    For the ``moreover'' part, it follows from Lemmas \ref{lemma:B_x-nondeg} and \ref{lemma:B_x-delta} that $B_x$ is nondegenerate and $\overline{B_x} = \delta B_x$ if, and only if, $\tilde B_x$ is nondegenerate and $B_x (u,v) = \mu_x B_x(v, u)$, for all $u,v \in V_x = \U_{\xi(x)}$. 
    Then the result follows from the well-known classification of (skew-)symmetric bilinear forms over an algebraically closed field of characteristic different from $2$ and the fact that an $\FF$-basis for $\U_{\xi(x)}$ is a $\D$-basis for $\U_x$.
\end{proof}

\begin{remark}
    Even though $\mu_{x}$ does not depend on $\xi$, the element $t = g_0\xi(x)^2$ may depend on $\xi$.
\end{remark}

\begin{prop}\label{prop:pair-of-dual-components}
    Let $\delta \in \pmone$. 
    Suppose $g_0 x y = T$ for $x\neq y$ and set $t \coloneqq g_0\xi(x)\xi(y) \in T$. 
    Then the restriction $B_x$ of $B$ to $\U_x \oplus \U_y$ is nondegenerate and satisfies $\overline{B_x} = \delta B_x$ if, and only if, there is a $\D$-basis of $\U_x$ with all elements having degree $\xi(x)$ and a $\D$-basis of $\U_y$ with all elements having degree $\xi(y)$ such that the matrix representing $B_x$ is
    \[
        \begin{pmatrix}
            0 & I_{\kappa(x)}\\
            \sign{\xi(x)}{\xi(y)} \eta(t) \delta I_{\kappa(x)} & 0
        \end{pmatrix} \tensor X_t. 
    \]
\end{prop}

\begin{proof}
    Assume that $B_x$ is nondegenerate. 
    Then by Lemma \ref{lemma:B_x-nondeg}, the bilinear form $\tilde B_x$ on $V_x = \U_{\xi(x)} \oplus \U_{\xi(y)}^*$ is nondegenerate, and hence, the map $\U_{\xi(x)} \to \U_{\xi(y)}$ given by $u \mapsto \tilde B_x (u, \cdot)$  is an isomorphism of vector spaces. 
    Hence, we can fix a basis $\{u_1, \ldots, u_{\kappa(x)} \}$ for $\U_{\xi(x)}$ and take its dual basis $\{v_1, \ldots, v_{\kappa(x)} \}$ for $\U_{\xi(y)}$, \ie, $\tilde B_x (u_i, v_j) = \delta_{ij}$. 
    If we also assume $\overline{B_x} = \delta B_x$, then by Lemma \ref{lemma:B_x-delta}, we have $\tilde B_x (v_i, u_j) = \sign{\xi(x)}{\xi(y)} \eta(t) \delta \delta_{ij}$. 
    This proves the only if part. 
    The converse is clear. 
\end{proof}

\begin{defi}\label{def:parameter-of-(U,B)}
    Let $\U$ be a graded $\D$-module of finite rank and $B$ be a homogeneous nondegenerate $\vphi_0$-sesquilinear form such that $\overline{B_x} = \delta B_x$ for some $\delta \in \pmone$. 
    We say that the triple $(\kappa, g_0, \delta)$ is the \emph{inertia of $(\U, B)$}, where $g_0 = \deg B \in G^\#$ and $\kappa(x) = \dim_\D \U_x$ for all $x \in G^\#/T$. 
\end{defi}

By the considerations above, the quadruple $(\eta, \kappa, g_0, \delta)$ satifies the following: 

\begin{defi}
    Let $\eta\from T \to \pmone$ such that $\mathrm{d}\eta = \tilde\beta$,
    $\kappa\from G^\#/T \to \ZZ_{\geq 0}$, $g_0 \in G^\#$ and $\delta \in \pmone$. 
    We say that the quadruple $(\eta, \kappa, g_0, \delta)$ is \emph{$\D$-admissible} if:
    \begin{enumerate}[(i)]
        \item $\kappa$ has finite support; \label{item:kappa-finite-support}
        \item $\kappa(x) = \kappa(g_0\inv x\inv)$ for all $x \in G^\#/T$; \label{item:kappa-duality}
        \item For any $x\in G^\#/T$, if $g_0 x^2 = T$ and $\mu_x \coloneqq (-1)^{|g|}\eta(g_0g^2)\delta -1$ for $g\in x$ (see Propositon \ref{prop:self-dual-components}), then $\kappa (x)$ is even. \label{item:kappa-parity}
    \end{enumerate}
    The set of all $\D$-admissible quadruples will be denoted by $\mathsf{X}(\D)$.
\end{defi}

Given a triple $(\eta, \kappa, g_0, \delta) \in \mathsf{X} (\D)$, we can construct a pair $(\U, B)$ such that $(\eta, \kappa, g_0, \delta)$ is it inertia. 
To see that, fix a total order $\leq$ on the set $G^\#/T$.
We define $U_x \coloneqq \FF^{\kappa(x)}$, and $\U = \sum_{g \in G^\#} \U_g$ where $\U_x \coloneqq U_x \tensor \D$, for all $x\in G^\#/T$. 
For all $x, y \in G^\#/T$ such that $g_0x y = T$ and $x \leq y$, we let $B_x$ the $\vphi_0$-sesquilinear on $\U_x + \U_y$ represented, relative to the standard basis of $U_x+U_y$, by to the matrices in Proposition \ref{prop:self-dual-components}, if $x=y$, or in Proposition \ref{prop:pair-of-dual-components}, if $x\neq y$. 

\begin{thm}\label{thm:iso-(U,B)}
    Suppose $\FF$ is an algebraically closed field and $\Char \FF \neq 2$. 
    Let $\D$ be a finite dimensional graded-division superalgebra and let $\vphi_0$ be a degree preserving superinvolution on $\D$. 
    % The map assigning a triple $(\kappa, g_0, \delta) \in \mathsf{X} (\D, \vphi_0)$ for ever
    The assignment of inertia to a pair $(\U, B)$ as in Definition \ref{def:parameter-of-(U,B)} gives a bijection between the isomorphism classes of these pairs and the set $\mathsf{X} (\D, \vphi_0)$.
    % Two pairs $(\U, B)$ and $(\U', B')$ are isomorphic if, and only if, they are associated to the same triple in $\mathsf{X} (\D, \vphi_0)$.
\end{thm}

\begin{proof}
    Suppose there is an isomorphism $\psi\from (\U, B) \to (\U', B')$.
    Since, in particular, $\psi$ is an isomorphism of graded $\D$-modules, both $\U$ and $\U'$ correspond to the same map $\kappa\from G^\#/T \to \ZZ_{\geq 0}$. 
    Also, from the fact that $B'(\psi(u), \psi(v)) = B(u, v)$ for all $u, v\in \U$, it is clear that $\deg B' = \deg B$.
    Moreover, if $\overline{B} = \delta B$, then
    \begin{align*}
        \overline{B'} \big(\psi(u), \psi(v) \big) &= \sign{\psi(u)}{\psi(v)} \vphi_0\inv \Big( B'\big( \psi(v) , \psi(u) \big) \Big) \\
        &= \sign{u}{v} \vphi_0\inv \big( B(v, u) \big) 
        = \overline{B} (u, v) \\
        &= \delta B(u, v) = \delta B' \big( \psi(u), \psi(v) \big),
    \end{align*}
    for all $u, v \in \U$. 
    Since $\psi$ is bijective, it follows that $\overline{B'} = \delta B'$. 
    
    Conversely, suppose that $(\U, B)$ and $(\U, B')$ have the same inertia $(\kappa, g_0, \delta)$. 
    To show that $(\U, B)$ and $(\U, B')$ are isomorphic, it suffices to find homogeneous $\D$-bases $\{u_1, \ldots, u_k\}$ of $\U$ and $\{u_1', \ldots, u_k'\}$ of $\U'$ such that $\deg u_i = \deg u_i'$, $1 \leq i \leq k$, and $B$ and $B'$ are represented by the same matrix. 
    Indeed, in this case the $\D$-linear map $\psi\from \U \to \U'$ defined by $\psi(u_i) = u_i'$, $1 \leq i \leq k$, is degree preserving, and $B(u_i, u_j) = B(u_i', u_j')$, $1 \leq i,j \leq k$, implies $B(u, v) = B( \psi(u), \psi(v) )$ for all $u, v\in \U$. 
    The existence of such bases follows from $\dim_\D (\U_x) = \dim_\D (\U_x') = \kappa(x)$, for all $x \in G^\#/T$, and Propositions \ref{prop:self-dual-components} and \ref{prop:pair-of-dual-components}. 
\end{proof}


\subsection{Parametrization of $(R, \vphi)$}

Recall from Theorems \ref{thm:vphi-iff-vphi0-and-B} and \ref{thm:vphi-involution-iff-delta-pm-1} that a finite dimensional graded-simple superalgebra with superinvolution $(R, \vphi)$ is described by $\D$, $\vphi_0$, $\U$ and $B$. 
With the parametrizations of $(\D, \vphi_0)$ and $(\U, B)$ presented above,
this data reduces (up to isomorphism) to $T$, $\beta$, $p$, $\eta$, $\kappa$, $g_0$ and $\delta$. 
We will now classify finite dimensional graded-simple superalgebras with superinvolution in terms of these parameters.

We will use Corollary \ref{cor:iso-with-actions} and express the group actions defined by Equations \eqref{eq:Dx_gr-action}, \eqref{eq:Aut(D)-action} and \eqref{eq:G-action} in terms of the above parameters. 
Let $R \coloneqq \End_\D (\U)$ and $R' \coloneqq \End_{\D'} (\U')$, with superinvolutions $\vphi$ and $\vphi'$, respectively, defined by pairs $(\vphi_0, B)$ and $(\vphi_0', B')$. 
Consider the corresponding parameters $(T, \beta, p, \eta, \kappa, g_0, \delta)$ and $(T', \beta', p', \eta', g_0', \delta', \kappa')$. 
If $(R, \vphi) \iso (R', \vphi')$, then $\D \iso \D'$ and, hence, $T = T'$, $\beta = \beta'$ and $p = p'$. 
For each triple $(T, \beta, p)$, we fix a graded-division superalgebra $\D$ with these parameters, so we may suppose $\D = \D'$. 

\begin{defi}
    We define $\mathsf{X} (\D)$ to be the set of all quadruples $(\eta, \kappa, g_0, \delta)$ where $\eta\from T \to \FF^\times$ is such that $\mathrm{d}\eta = \tilde \beta$ (see Definitions \ref{def:coboundary} and \ref{def:tilde-beta}) and $(\kappa, g_0, \delta)$ is an $\eta$-admissible triple (see Definition \ref{def:parameter-of-(U,B)}). 
    Note that $\mathsf{X} (\D)$ can be identified with the set $\bigsqcup_{\vphi_0} \mathsf {X} (\D, \vphi_0)$. 
\end{defi}

By Corollary \ref{cor:iso-with-actions}, $(R, \vphi) \iso (R', \vphi')$ if, and only if, $(\eta', g_0', \delta', \kappa')$ is in the orbit of $(\eta, \kappa, g_0, \delta)$ under the action of $(\D^\times_{\mathrm{gr}} \rtimes A ) \times G^\#$ determined by its action on the isomorphism classes of $(\U, B)$ (see Lemma \ref{lemma:action-on-(U,B)}). 
Let us compute this action explicitly. 

First, in our case of algebraically closed $\FF$, the $A$-action (defined by Equation \eqref{eq:Aut(D)-action}) is trivial. 
To see that,
fix $\eta$ and suppose $(\kappa, g_0, \delta)$ is assigned to $(\U, B)$. 
Note that $\psi_0 \in A$ must be a scalar operator on each component $\D_t$ of $\D$, hence $\psi_0$ commutes with $\vphi_0$. 
It follows that $\psi_0\inv \circ B$ is $\vphi_0$-sesquilinear, so we can use Theorem \ref{thm:iso-(U,B)} to show that $(\U, B)$ is isomorphic to $\psi_0\cdot (\U, B) = (\U^{\psi_0\inv}, \psi \circ B)$. 
The graded $\D$-modules $\U$ and $\U^{\psi_0\inv}$ have the same $\kappa$, since $\dim_\D \U_x = \dim_\D (\U_x)^{\psi_0\inv}$, for all $x \in G^\#/T$. 
Also, it is clear that $\deg (\psi_0 \circ B) = \deg B$. 
Finally, 
% \begin{align*}
%     \overline{(\psi_0 \circ B)} (u,v) &= \sign{u}{v} (\psi_0\inv \circ \vphi \circ \psi_0)\inv \big( (\psi_0 \circ B)(v, u) \big) \\
%     &= \sign{u}{v} (\psi_0 \circ \vphi\inv \circ \psi_0\inv) \big( (\psi_0 \circ B)(v,u) \big) \\
%     &= \psi_0 \bigg( \sign{u}{v} \vphi\inv \big( B(v,u) \big) \bigg) \\
%     &= \psi_0 \big( \overline B (u,v) \big) = \psi_0 \big( \delta B (u,v) \big) = \delta (\psi_0 \circ B) (u,v),
% \end{align*}
\begin{align*}
    \overline{(\psi_0 \circ B)} (u,v) &= \sign{u}{v} \vphi_0\inv \big( (\psi_0 \circ B)(v, u) \big) \\
    &= \psi_0 \bigg( \sign{u}{v} \vphi_0\inv \big( B(v,u) \big) \bigg) \\
    &= \psi_0 \big( \overline B (u,v) \big) = \psi_0 \big( \delta B (u,v) \big) = \delta (\psi_0 \circ B) (u,v),
\end{align*}
for all $u, v \in \U\even \cup \U\odd$.

Now, let us consider the $\D^\times_{\mathrm{gr}}$-action. 
Let $t\in T$ and $0\neq d \in \D_t$ and let $(\eta', \kappa', g_0', \delta')$ be the parameters corresponding to $d \cdot (\U, B) = (\U, d B)$ (see Equation \eqref{eq:Dx_gr-action}). 
To compute $\eta'$, recall that $dB$ is $(\mathrm{sInt}_d \circ \vphi_0)$-sesquilinear. 
Let $s\in T$ and $c \in \D_s$. 
Then
\begin{align*}
    (\mathrm{sInt}_{d} \circ \vphi_0) (c) &= \mathrm{sInt}_{d} ( \eta(s) c ) = \sign{t}{s} \eta(s) d c d\inv\\
    &= \sign{t}{s} \eta(s) \beta(t,s) c d d\inv = \tilde{\beta} (t,s) \eta(s) c
\end{align*}
and, hence, $\eta' (s) = \tilde{\beta} (t,s) \eta(s)$ for all $s\in T$. 
Since the action by $d$ does not change $\U$, we have $\kappa' = \kappa$. 
Clearly $g_0' = \deg (dB) = t g_0$. 
It remains to compute $\delta'$. 
Using Lemma \ref{lemma:bar-dB}, we have 
\begin{align*}
    \overline{d B} &= (-1)^{|t|} \vphi_0(d) \overline{B} = (-1)^{|t|} \eta(t) d \delta B = (-1)^{|t|} \eta(t) \delta (d B),
\end{align*}
so $\delta' = (-1)^{t} \eta(t) \delta$. 
Note that $(\eta', \kappa', g_0', \delta')$ depends only on $t$, so the $\D^\times_\mathrm{gr}$-action on $\mathsf{X}(\D)$ factors through the action of $T \iso \D^\times_\mathrm{gr}/\FF^\times$.

Finally, we consider the $G^\#$-action. 
Let $g\in G$ and let $(\eta'', \kappa'', g_0'', \delta'')$ be the parameters corresponding to $g \cdot (\U, B) = (\U^{[g]}, B^{[g]})$ (see Equation \eqref{eq:G-action}). 
Since $B^{[g]}$ is $\vphi_0$-sesquilinear, $\eta'' = \eta$. By the definition of $\U^{[g]}$, $\kappa'' = g\cdot \kappa$ where $(g\cdot \kappa) (x) = \kappa(g\inv x)$ for all $x\in G^\#/T$ {\tt (computed before)}. 
As noted in Remark \ref{rmk:deg-B^[g]}, $g_0'' = \deg B^{[g]} = g_0 g^{-2}$. 
Also, for all $u, v\ \in \U\even \cup \U\odd$, and writing $u^{[g]}$ and $v^{[g]}$ for the same elements but considered as elements of $\U^{[g]}$, we compute: 
\begin{align*}
    \overline{B^{[g]}}(u^{[g]},v^{[g]}) &= \sign{u^{[g]}}{v^{[g]}} \vphi_0\inv \big( B^{[g]} (v^{[g]}, u^{[g]}) \big) = (-1)^{(|g| + |u|) (|g| + |v|)} \vphi_0\inv \big( \sign{g}{v} B(v, u) \big) \\
    &= (-1)^{|g| + |g||u| + |g||v| + |u||v|} \sign{g}{v} \vphi_0\inv \big(B(v, u) \big) = (-1)^{|g| + |g||u|} \overline B(u,v) \\
    &= (-1)^{|g|} \sign{g}{u} \delta B(u,v) = (-1)^{|g|} \delta B^{[g]}(u^{[g]},v^{[g]}),
\end{align*}
We conclude that $\delta'' = (-1)^{|g|} \delta$. 

We summarize this discussion in the following:

\begin{defi}
    The group $T\times G^\#$ acts on $\mathsf{X}(\D)$ by 
    \begin{align}
        t \cdot (\eta, \kappa, g_0, \delta) &\coloneqq (\tilde\beta (t, \cdot) \eta, \kappa, t g_0, (-1)^{|t|} \eta(t)\delta)
        \intertext{and}
        g \cdot (\eta, \kappa, g_0, \delta) &\coloneqq (\eta, g\cdot \kappa, g_0 g^{-2}, (-1)^{|g|} \delta),
    \end{align}
    for all $t\in T$, $g\in G^\#$ and $(\eta, \kappa, g_0, \delta) \in \mathsf{X}(\D)$.
\end{defi}

% \begin{equation}
%     t \cdot (\eta, \kappa, g_0, \delta) = (\eta \tilde \beta (t, \cdot), t g_0, (-1)^{|t|} \eta(t)\delta, \kappa).
% \end{equation}


% Finally, the $G^\#$-action is given by
% \begin{equation}
%     g \cdot (\eta, \kappa, g_0, \delta) = (\eta, g_0 g^{-2}, (-1)^{|g|} \delta, g\cdot \kappa),
% \end{equation}
% where $(g \cdot \kappa)(x) \coloneqq \kappa (g\inv x)$ for all $x \in G^\#/T$.

Thus Corollary \ref{cor:iso-with-actions} can be restated as follows:

\begin{thm}\label{thm:iso-(R,vphi)-with-parameters}
    Let $\D$ be a finite dimensional graded-divison superalgebra over an algebraically closed field $\FF$, $\Char \FF \neq 2$, with parameters $(T, \beta, p)$. 
    Let $\vphi_0$ and $\vphi_0'$ be degree preserving superinvolutions on $\D$ and let $(\U, B)$ and $(\U', B')$ be graded right $\D$-supermodules of finite rank with nondegenerate $\delta$-hermitian
    Let $R \coloneqq \End_\D(\U)$ and $R' \coloneqq \End_\D(\U')$
\end{thm}

We will now proceed to give simplifications of this result by fixing $\eta$.